\newHymn
\FirstLine{Puer natus in Bethlehem, alleluia}

\settowidth{\versewidth}{a boy is born in bethlehem alleluia alleluia alleluia alleluia}

\begin{verse}[\versewidth]

\annotinverse{
A Boy is born in Bethlehem,\\
Joy bringing to Jerusalem.
}

\FirstVerse{P}{uer} natus in Béthlehem, allelúia:\\*
Unde gaudet Jerúsalem,\\*
\vin allelúia, allelúia.


\end{verse}
{
%\gresetfirstlineaboveinitial{Ant}{\large A}
\renewcommand\greinitialformat[1]{\normalsize #1}
\includescore{gabc/incordis.tex}
}
\vskip-\baselineskip
\annotinverse{In jubilee of heart, let us adore with one accord,\\
The birth of Christ, Our Lord.}

\begin{verse}[\versewidth]

\annotinverse{He lieth in a manger poor,\\
Whose Kingdom shall for aye endure.}

\flagverse{2} Hic jacet in praesépio, allelúia:\\*
Qui regnat sine término,\\*
\vin allelúia, allelúia.

\annotinverse{The kings of Saba come and bring,
Gold, myrrh and incense to their King.}

\flagverse{3} Reges de Saba véniunt, allelúia,\\*
Aurum, thus, myrrham ófferunt,\\*
\vin allelúia, allelúia.

\annotinverse{One after one, the cot forlorn,\\
Ent'ring they hail their Prince new-born.}

\flagverse{4} Intrántes domum ínvicem, allelúia,\\*
Novum salútant Príncipem,\\*
\vin allelúia, allelúia.

\annotinverse{The serpent's venom knows Him not,\\
Though of our blood His own He got.}

\flagverse{5} Sine serpéntis vúlnere, allelúia,\\*
De nostro venit sánguine,\\*
\vin allelúia, allelúia.

\annotinverse{Made like to us in human kin,\\
Unlike us in respect to sin.}

\flagverse{6} In carne nobis símilis, allelúia,\\*
Peccáto sed dissímilis,\\*
\vin allelúia, allelúia.

\end{verse}

\begin{verse}[\versewidth]

\annotinverse{That like Him He might make us be,\\
And with Himself and God agree.}

\flagverse{7} Ut rédderet nos hómines, allelúia,\\*
Deo et sibi símiles,\\*
\vin allelúia, allelúia.

\annotinverse{To this birth's joy let all accord,\\
And bless forever Christ the Lord.}

\flagverse{8} In hoc natáli gaudio, allelúia:\\*
Benedicámus Dómino,\\*
\vin allelúia, allelúia.

\end{verse}

\begin{verse}[\versewidth]

\annotinverse{And praise the Holy Trinity,\\
Now and to all eternity.}

\flagverse{9} Laudétur sancta Trínitas, allelúia,\\*
Deo dicámus grátias,\\*
\vin allelúia, allelúia.

\end{verse}

\Htrans{the Transalpine Redemptorist Christmas Book}{2010}
