
\smallhead{8th December}

\atitle{Immaculate Conception}

\label{Ep.immac}
\bibleref{Epistle}{Prov.~8:22--35}

The Lord possessed me in the beginning of his ways, before he made any thing
from the beginning.   I was set up from eternity, and of old before the earth
was made.   The depths were not as yet, and I was already conceived. neither
had the fountains of waters as yet sprung out:   The mountains with their huge
bulk had not as yet been established: before the hills I was brought forth:  He
had not yet made the earth, nor the rivers, nor the poles of the world.  When
he prepared the heavens, I was present: when with a certain law and compass he
enclosed the depths:   When he established the sky above, and poised the
fountains of waters:  When he compassed the sea with its bounds, and set a law
to the waters that they should not pass their limits: when be balanced the
foundations of the earth;  I was with him forming all things: and was delighted
every day, playing before him at all times; Playing in the world: and my
delights were to be with the children of men.  Now therefore, ye children, hear
me: Blessed are they that keep my ways.  Hear instruction and be wise, and
refuse it not.   Blessed is the man that heareth me, and that watcheth daily at
my gates, and waiteth at the posts of my doors.   He that shall find me, shall
find life, and shall have salvation from the Lord.


\bibleref{Gospel}{Luke 1:26--28}

At that time, the angel Gabriel was sent from God into a city of
Galilee, called Nazareth,  to a virgin espoused to a man whose name was Joseph,
of the house of David; and the virgin's name was Mary.  And the angel being
come in, said unto her: Hail, full of grace, the Lord is with thee: blessed art
thou among women. 


%\bigskip

\smallhead{21st December}

\atitle{St Thomas}

\bibleref{Epistle}{Eph.~2:19--22}

Brethren: Now therefore you are no more strangers and foreigners: but you
are fellow citizens with the saints and the domestics of God,
Built upon the foundation of the apostles and prophets, Jesus
Christ himself being the chief corner stone:
In whom all the building, being framed together, groweth up into
an holy temple in the Lord.
In whom you also are built together into an habitation of God in
the Spirit.

\bibleref{Gospel}{John~20:24--29}

At that time Thomas, one of the twelve, who is called Didymus, was not
with them when Jesus came.
The other disciples therefore said to him: We have seen the Lord.
But he said to them: Except I shall see in his hands the print of the
nails and put my finger into the place of the nails and put my hand into
his side, I will not believe.
And after eight days, again his disciples were within, and Thomas
with them. Jesus cometh, the doors being shut, and stood in the midst
and said: Peace be to you.
Then he said to Thomas: Put in thy finger hither and see my
hands. And bring hither the hand and put it into my side.  And be not
faithless, but believing.
Thomas answered and said to him: My Lord and my God.
Jesus saith to him: Because thou hast seen me, Thomas, thou hast
believed: blessed are they that have not seen and have believed.

%\bigskip

\smallhead{26th December}

\atitle{St.~Stephen}

\bibleref{Epistle}{Acts 6:8--10; 7:54--59}

In those days: Stephen, full of grace and fortitude, did great wonders and
signs among the people.
Now there arose some, of that which is called the synagogue of the
Libertines and of the Cyrenians and of the Alexandrians and of them that
were of Cilicia and Asia, disputing with Stephen.
And they were not able to resist the wisdom and the spirit that
spoke.
Now hearing these things, they were cut to the heart: and they
gnashed with their teeth at him.
But he, being full of the Holy Ghost, looking up steadfastly to
heaven, saw the glory of God and Jesus standing on the right hand of
God. And he said: Behold, I see the heavens opened and the Son of man
standing on the right hand of God.
And they, crying out with a loud voice, stopped their ears and
with one accord ran violently upon him.
And casting him forth without the city, they stoned him.  And the
witnesses laid down their garments at the feet of a young man, whose
name was Saul.
And they stoned Stephen, invoking and saying: Lord Jesus, receive
my spirit.
And falling on his knees, he cried with a loud voice, saying:
Lord, lay not his sin to their charge: And when he had said this, he
fell asleep in the Lord. % And Saul was consenting to his death.



\bibleref{Gospel}{Matt.~23:34--39}

At that time Jesus said to the scribes and pharisees: Behold I send to you prophets and wise men and scribes:
and some of them you will put to death and crucify: and some you will
scourge in your synagogues and persecute from city to city.
That upon you may come all the just blood that hath been shed
upon the earth, from the blood of Abel the just, even unto the blood of
Zacharias the son of Barachias, whom you killed between the temple and
the altar.
\challnote{That upon you may come, etc... Not that they should suffer more than
their own sins justly deserved; but that the justice of God should now
fall upon them with such a final vengeance, once for all, as might
comprise all the different kinds of judgments and punishments, that had
at any time before been inflicted for the shedding of just blood.}
Amen I say to you, all these things shall come upon this
generation.
Jerusalem, Jerusalem, thou that killest the prophets and stonest
them that are sent unto thee, how often would I have gathered together
thy children, as the hen doth gather her chickens under her wings, and
thou wouldst not?
Behold, your house shall be left to you, desolate.
For I say to you, you shall not see me henceforth till you say:
Blessed is he that cometh in the name of the Lord.


%\bigskip

\smallhead{27th December}

\atitle{St.~John}

\bibleref{Epistle}{Ecclus.~15:1--6}

He that feareth God, will do good: and he that possesseth justice,
shall lay hold on her,
And she will meet him as an honourable mother, and will receive
him as a wife married of a virgin.
With the bread of life and understanding, she shall feed him, and
give him the water of wholesome wisdom to drink: and she shall be made
strong in him, and he shall not be moved.
And she shall hold him fast, and he shall not be confounded: and
she shall exalt him among his neighbours.
And in the midst of the church she shall open his mouth, and shall
fill him with the spirit of wisdom and understanding, and shall clothe
him with a robe of glory.
She shall heap upon him a treasure of joy and gladness, and shall
cause him to inherit an everlasting name.

\bibleref{Gospel}{John 21:19--24}

At that time Jesus said to Peter: Follow me.
Peter turning about, saw that disciple whom Jesus loved
following, who also leaned on his breast at supper and said: Lord, who
is he that shall betray thee?
Him therefore when Peter had seen, he saith to Jesus: Lord, and
what shall this man do?
Jesus saith to him: So I will have him to remain till I come,
what is it to thee? Follow thou me.
This saying therefore went abroad among the brethren, that that
disciple should not die. And Jesus did not say to him: He should not
die; but: So I will have him to remain till I come, what is it to thee?
This is that disciple who giveth testimony of these things and
hath written these things: and we know that his testimony is true.


%\bigskip

\smallhead{28th December}

\atitle{Holy Innocents}

\bibleref{Epistle}{Apoc.~14:1--5}

In those days I beheld a Lamb stood upon mount Sion, and with him an
hundred forty-four thousand, having his name and the name of his Father
written on their foreheads.
And I heard a voice from heaven, as the noise of many waters and
as the voice of great thunder. And the voice which I heard was as the
voice of harpers, harping on their harps.
And they sung as it were a new canticle, before the throne and
before the four living creatures and the ancients: and no man could say
the canticle, but those hundred forty-four thousand who were purchased
from the earth.
These are they who were not defiled with women: for they are
virgins. These follow the Lamb whithersoever he goeth.  These were
purchased from among men, the firstfruits to God and to the Lamb.
And in their mouth there was found no lie: for they are without
spot before the throne of God.


\bibleref{Gospel}{Matt.~2:13--18}

At that time an angel of the Lord appeared
in sleep to Joseph, saying: Arise, and take the child and his mother,
and fly into Egypt: and be there until I shall tell thee. For it will
come to pass that Herod will seek the child to destroy him.
Who arose, and took the child and his mother by night, and retired
into Egypt: and he was there until the death of Herod:
That it might be fulfilled which the Lord spoke by the prophet,
saying: Out of Egypt have I called my son.
Then Herod perceiving that he was deluded by the wise men, was
exceeding angry: and sending killed all the menchildren that were in
Bethlehem, and in all the borders thereof, from two years old and under,
according to the time which he had diligently inquired of the wise men.
Then was fulfilled that which was spoken by Jeremias the prophet,
saying:
A voice in Rama was heard, lamentation and great mourning; Rachel
bewailing her children, and would not be comforted, because they are
not.



\bigskip

\smallhead{29th December}

\atitle{St Thomas Becket}

\bibleref{Epistle}{Heb.~5:1--6}

Brethren, every high priest taken from among men is ordained for men in
the things that appertain to God, that he may offer up gifts and
sacrifices for sins:
Who can have compassion on them that are ignorant and that err:
because he himself also is compassed with infirmity.
And therefore he ought, as for the people, so also for himself, to
offer for sins.
Neither doth any man take the honour to himself, but he that is
called by God, as Aaron was.
So Christ also did not glorify himself, that he might be made a
high priest: but he that said unto him: Thou art my Son: this day have I
begotten thee.
As he saith also in another place: Thou art a priest for ever,
according to the order of Melchisedech.


\bibleref{Gospel}{John 10:11--16}

At that time Jesus said to the Pharisees:
I am the good shepherd. The good shepherd giveth his life for his
sheep.
But the hireling and he that is not the shepherd, whose own the
sheep are not, seeth the wolf coming and leaveth the sheep and flieth:
and the wolf casteth and scattereth the sheep,
And the hireling flieth, because he is a hireling: and he hath no
care for the sheep.
I am the good shepherd: and I know mine, and mine know me.
As the Father knoweth me, and I know the Father: and I lay down
my life for my sheep.
And other sheep I have that are not of this fold: them also I
must bring. And they shall hear my voice: And there shall be one fold
and one shepherd.

 
\bigskip

\smallhead{13th January}

\atitle{Baptism of Our Lord}

\bibleref{Epistle}{Is.~60:1--6}

Arise, be enlightened, O Jerusalem: for thy light is come, and the
glory of the Lord is risen upon thee.
For behold darkness shall cover the earth, and a mist the people:
but the Lord shall arise upon thee, and his glory shall be seen upon
thee.
And the Gentiles shall walk in thy light, and kings in the
brightness of thy rising.
Lift up thy eyes round about, and see: all these are gathered
together, they are come to thee: thy sons shall come from afar, and thy
daughters shall rise up at thy side.
Then shalt thou see, and abound, and thy heart shall wonder and be
enlarged, when the multitude of the sea shall be converted to thee, the
strength of the Gentiles shall come to thee.
The multitude of camels shall cover thee, the dromedaries of
Madian and Epha: all they from Saba shall come, bringing gold and
frankincense: and shewing forth praise to the Lord.

\medskip

\bibleref{Gospel}{John 1:29--34}

At that time John saw Jesus coming to him; and he saith: Behold
the Lamb of God. Behold him who taketh away the sin of the world.
This is he of whom I said: After me there cometh a man, who is
preferred before me: because he was before me.
And I knew him not: but that he may be made manifest in Israel,
therefore am I come baptizing with water.
And John gave testimony, saying: I saw the Spirit coming down, as
a dove from heaven; and he remained upon him.
And I knew him not: but he who sent me to baptize with water said
to me: He upon whom thou shalt see the Spirit descending and remaining
upon him, he it is that baptizeth with the Holy Ghost.
And I saw: and I gave testimony that this is the Son of God.



\bigskip

\smallhead{2nd February}

\atitle{Purification (Candlemas)}

\bibleref{Epistle}{Mal.~3:1--4}

Thus saith the Lord God:
Behold I send my angel, and he shall prepare the way before my
face. And presently the Lord, whom you seek, and the angel of the
testament, whom you desire, shall come to his temple. Behold, he cometh,
saith the Lord of hosts.
\challnote{My angel... Viz., John the Baptist, the messenger of God, and forerunner
of Christ.}
And who shall be able to think of the day of his coming? and who
shall stand to see him? for he is like a refining fire, and like the
fuller's herb:
and he shall sit refining and cleansing the silver, and he shall
purify the sons of Levi, and shall refine them as gold, and as silver,
and they shall offer sacrifices to the Lord in justice.
And the sacrifice of Juda and of Jerusalem shall please the Lord,
as in the days of old, and in the ancient years:
saith the Lord almighty.

%\columnbreak
\medskip

\bibleref{Gospel}{Luke 2:22--32}

At that time,
%And 
after the days of Mary's purification, according to the law of
Moses, were accomplished, they carried him to Jerusalem, to present him
to the Lord:
as it is written in the law of the Lord: Every male opening the
womb shall be called holy to the Lord:
and to offer a sacrifice, according as it is written in the law of
the Lord, a pair of turtledoves or two young pigeons.
And behold there was a man in Jerusalem named Simeon: and this man
was just and devout, waiting for the consolation of Israel. And the Holy
Ghost was in him.
And he had received an answer from the Holy Ghost, that he should
not see death before he had seen the Christ of the Lord.
And he came by the Spirit into the temple. And when his parents
brought in the child Jesus, to do for him according to the custom of the
law,
he also took him into his arms and blessed God and said:
Now thou dost dismiss thy servant, O Lord, according to thy word
in peace;
because my eyes have seen thy salvation,
which thou hast prepared before the face of all peoples:
A light to the revelation of the Gentiles and the glory of thy
people Israel.

\bigskip

\smallhead{24th February}

\atitle{St Matthias}

\bibleref{Epistle}{Acts 1:15--26}

In those days Peter rising up in the midst of the brethren, said
(now the number of persons together was about an hundred and twenty):
Men, brethren, the scripture must needs be fulfilled, which the
Holy Ghost spoke before by the mouth of David concerning Judas, who was
the leader of them that apprehended Jesus:
Who was numbered with us, and had obtained part of this ministry.
And he indeed hath possessed a field of the reward of iniquity,
and being hanged, burst asunder in the midst: and all his bowels gushed
out.
And it became known to all the inhabitants of Jerusalem: so that
the same field was called in their tongue, Haceldama, that is to say,
The field of blood.
For it is written in the book of Psalms: Let their habitation
become desolate, and let there be none to dwell therein. And his
bishopric let another take.
Wherefore of these men who have companied with us, all the time
that the Lord Jesus came in and went out among us,
Beginning from the baptism of John, until the day wherein he was
taken up from us, one of these must be made a witness with us of his
resurrection.
And they appointed two, Joseph, called Barsabas, who was surnamed
Justus, and Matthias.
And praying, they said: Thou, Lord, who knowest the heart of all
men, shew whether of these two thou hast chosen,
To take the place of this ministry and apostleship, from which
Judas hath by transgression fallen, that he might go to his own place.
And they gave them lot, and the lot fell upon Matthias, and he was
numbered with the eleven apostles.

\medskip

\bibleref{Gospel}{Matt.~11:25--30}

At that time Jesus answered and said: I confess to thee, O
Father, Lord of Heaven and earth, because thou hast hid these things
from the wise and prudent, and hast revealed them to little ones.
Yea, Father: for so hath it seemed good in thy sight.
All things are delivered to me by my Father. And no one knoweth
the Son but the Father: neither doth any one know the Father, but the
Son, and he to whom it shall please the Son to reveal him.
Come to me all you that labor and are burdened, and I will
refresh you.
Take up my yoke upon you, and learn of me, because I am meek, and
humble of heart: And you shall find rest to your souls.
For my yoke is sweet and my burden light.



\bigskip
\columnbreak

\smallhead{19th March}

\atitle{Saint Joseph}

\bibleref{Epistle}{Ecclus.~45:1--6}

%Moses was 
Beloved of God, and men: whose memory is in benediction.  He made him
like the saints in glory, and magnified him in the fear of his enemies, and
with his words he made prodigies to cease.  He glorified him in the sight of
kings, and gave him commandments in the sight of his people, and shewed him his
glory.  He sanctified him in his faith, and meekness, and chose him out of all
flesh.  For he heard him, and his voice, and brought him into a cloud.  And he
gave him commandments before his face, and a law of life and instruction.
%, that
%he might teach Jacob his covenant, and Israel his judgments.


\bibleref{Gospel}{Matt.~1:18--21}


%Now the generation of Christ was in this wise. 
When Mary the Mother of Jesus was
espoused to Joseph, before they came together, she was found with child, of the
Holy Ghost.  Whereupon Joseph her husband, being a just man, and not willing
publicly to expose her, was minded to put her away privately.  But while he
thought on these things, behold the Angel of the Lord appeared to him in his
sleep, saying: Joseph, son of David, fear not to take unto thee Mary thy wife,
for that which is conceived in her, is of the Holy Ghost.  And she shall bring
forth a son: and thou shalt call his name Jesus. For he shall save his people
from their sins.


\bigskip

\smallhead{25th March}

\atitle{Annunciation}

\bibleref{Epistle}{Is.~7:10--15}

In those days the Lord spoke to Achaz, saying:
Ask thee a sign of the Lord thy God, either unto the depth of
hell, or unto the height above.
And Achaz said: I will not ask, and I will not tempt the Lord.
And he said: Hear ye therefore, O house of David: Is it a small
thing for you to be grievous to men, that you are grievous to my God
also?
Therefore the Lord himself shall give you a sign. Behold a virgin
shall conceive, and bear a son and his name shall be called Emmanuel.
He shall eat butter and honey, that he may know to refuse the
evil, and to choose the good.


%\columnbreak

\bibleref{Gospel}{Luke 1:26--38}
\label{Go.angelus}

At that time the angel Gabriel was sent from God into a
city of Galilee, called Nazareth,
to a virgin espoused to a man whose name was Joseph, of the house
of David: and the virgin's name was Mary.
And the angel being come in, said unto her: Hail, full of grace,
the Lord is with thee: blessed art thou among women.
Who having heard, was troubled at his saying and thought with
herself what manner of salutation this should be.
And the angel said to her: Fear not, Mary, for thou hast found
grace with God.
Behold thou shalt conceive in thy womb and shalt bring forth a
son: and thou shalt call his name Jesus.
He shall be great and shall be called the Son of the Most High.
And the Lord God shall give unto him the throne of David his father: and
he shall reign in the house of Jacob for ever.
And of his kingdom there shall be no end.
And Mary said to the angel: How shall this be done, because I know
not man?
And the angel answering, said to her: The Holy Ghost shall come
upon thee and the power of the Most High shall overshadow thee. And
therefore also the Holy which shall be born of thee shall be called the
Son of God.
And behold thy cousin Elizabeth, she also hath conceived a son in
her old age: and this is the sixth month with her that is called barren.
Because no word shall be impossible with God.
And Mary said: Behold the handmaid of the Lord: be it done to me
according to thy word. %And the angel departed from her.

\bigskip

\smallhead{25th April}

\atitle{St.~Mark}

\bibleref{Epistle}{Ezech.~1:10--14}
\label{Ep.stmark}

As for the likeness of their faces: there was the face of a
man, and the face of a lion on the right side of all the four: and the
face of an ox, on the left side of all the four: and the face of an
eagle over all the four.
And their faces, and their wings were stretched upward: two wings
of every one were joined, and two covered their bodies:
And every one of them went straight forward: whither the impulse
of the spirit was to go, thither they went: and they turned not when
they went.
And as for the likeness of the living creatures, their appearance
was like that of burning coals of fire, and like the appearance of
lamps. This was the vision running to and fro in the midst of the living
creatures, a bright fire, and lightning going forth from the fire.
And the living creatures ran and returned like flashes of
lightning.


\bibleref{Gospel}{Luke 10:1--9}
\label{Go.stmark}

At that time, the Lord appointed also other seventy-two.
And he sent them two and two before his face into every city and place
whither he himself was to come.
And he said to them: The harvest indeed is great, but the
labourers are few. Pray ye therefore the Lord of the harvest that he
send labourers into his harvest.
Go: Behold I send you as lambs among wolves.
Carry neither purse, nor scrip, nor shoes: and salute no man by
the way.
Into whatever house you enter, first say: Peace be to this house.
And if the son of peace be there, your peace shall rest upon him:
but if not, it shall return to you.
And in the same house, remain, eating and drinking such things as
they have: for the labourer is worthy of his hire.  Remove not from
house to house.
And into what city soever you enter, and they receive you, eat
such things as are set before you.
And heal the sick that are therein and say to them: The kingdom of
God is come nigh unto you.


\bigskip

%\columnbreak

\smallhead{1st May}

\atitle{St.~Joseph the Worker}

\bibleref{Epistle}{Col.~3:14--15,17,23--24}

Brethren: have charity, which is the bond of
perfection,
and let the peace of Christ rejoice in your hearts, wherein also
you are called in one body: and be ye thankful.
%Let the word of Christ dwell in you abundantly: in all wisdom,
%teaching and admonishing one another in psalms, hymns and spiritual
%canticles, singing in grace in your hearts to God.
All whatsoever you do in word or in work, do all in the name of
the Lord Jesus Christ, giving thanks to God and the Father by him.
%Wives, be subject to your husbands, as it behoveth in the Lord.
%Husbands, love your wives and be not bitter towards them.
%Children, obey your parents in all things: for this is well
%pleasing to the Lord.
%Fathers, provoke not your children to indignation, lest they be
%discouraged.
%Servants, obey in all things your masters according to the flesh:
%not serving to the eye, as pleasing men: but in simplicity of heart,
%fearing God.
Whatsoever you do, do it from the heart, as to the Lord, and not
to men:
knowing that you shall receive of the Lord the reward of
inheritance. Serve ye the Lord Christ.



\bibleref{Gospel}{Matt.~13:54--58}

And coming into his own country, he taught them in their
synagogues, so that they wondered and said: How came this man by this
wisdom and miracles?
Is not this the carpenter's son? Is not his mother called Mary,
and his brethren James, and Joseph, and Simon, and Jude:
%His brethren... These were the children of Mary the wife of Cleophas,
%sister to our Blessed Lady, (St. Matt. 27. 56; St.  John 19. 25,) and
%therefore, according to the usual style of the Scripture, they were
%called brethren, that is, near relations to our Saviour.
And his sisters, are they not all with us? Whence therefore hath
he all these things?
And they were scandalized in his regard. But Jesus said to them:
A prophet is not without honour, save in his own country, and in his own
house.
And he wrought not many miracles there, because of their
unbelief.


\bigskip

\smallhead{11th May}

\atitle{Sts.~Philip and James}

\bibleref{Epistle}{Wisdom 5:1--5}

Then shall the just stand with great constancy against those that
have afflicted them, and taken away their labours.
These seeing it, shall be troubled with terrible fear, and shall be
amazed at the suddenness of their unexpected salvation,
Saying within themselves, repenting, and groaning for anguish of
spirit: These are they, whom we had sometime in derision, and for a
parable of reproach.
We fools esteemed their life madness, and their end without honour.
Behold, how they are numbered among the children of God, and their
lot is among the saints.


\bibleref{Gospel}{John 14:1--13}

At that time, Jesus said to His disciples: Let not your heart be troubled. You believe in God: believe also
in me.
In my Father's house there are many mansions. If not, I would have
told you: because I go to prepare a place for you.
And if I shall go and prepare a place for you, I will come again
and will take you to myself: that where I am, you also may be.
And whither I go you know: and the way you know.
Thomas saith to him: Lord, we know not whither thou goest.  And
how can we know the way?
Jesus saith to him: I am the way, and the truth, and the life. No
man cometh to the Father, but by me.
If you had known me, you would without doubt have known my Father
also: and from henceforth you shall know him. And you have seen him.
Philip saith to him: Lord, shew us the Father; and it is enough
for us.
Jesus saith to him: Have I been so long a time with you and have
you not known me? Philip, he that seeth me seeth the Father also. How
sayest thou: Shew us the Father?
Do you not believe that I am in the Father and the Father in me?
The words that I speak to you, I speak not of myself.  But the Father
who abideth in me, he doth the works.
Believe you not that I am in the Father and the Father in me?
Otherwise believe for the very works' sake. Amen, amen, I say to
you, he that believeth in me, the works that I do, he also shall do: and
greater than these shall he do.
Because I go to the Father: and whatsoever you shall ask the
Father in my name, that will I do.


\bigskip

\smallhead{31st May}

\atitle{Queenship of Mary}

\bibleref{Epistle}{Ecclus.~24:5--11,30--31}

I came out of the mouth of the most High, the firstborn before all
creatures:
I dwelt in the highest places, and my throne is in a pillar of a
cloud.
And have stood in all the earth: and in every people,
And in every nation I have had the chief rule:
And by my power I have trodden under my feet the hearts of all
the high and low.
He that hearkeneth to me, shall not be confounded: and they that
work by me, shall not sin.
They that explain me shall have life everlasting.



\bibleref{Gospel}{Luke 1:26--33}

At that time: the angel Gabriel was sent from God into a
city of Galilee, called Nazareth,
To a virgin espoused to a man whose name was Joseph, of the house
of David: and the virgin's name was Mary.
And the angel being come in, said unto her: Hail, full of grace,
the Lord is with thee: blessed art thou among women.
Who having heard, was troubled at his saying and thought with
herself what manner of salutation this should be.
And the angel said to her: Fear not, Mary, for thou hast found
grace with God.
Behold thou shalt conceive in thy womb and shalt bring forth a
son: and thou shalt call his name Jesus.
He shall be great and shall be called the Son of the Most High.
And the Lord God shall give unto him the throne of David his father: and
he shall reign in the house of Jacob for ever.
And of his kingdom there shall be no end.



\bigskip

\smallhead{24th June}

\atitle{Nativity of St.~John the Baptist}

\bibleref{Epistle}{Is.~49:1--3,5,6,7}

Give ear, ye islands, and hearken, ye people from afar. The Lord
hath called me from the womb, from the bowels of my mother he hath been
mindful of my name.
And he hath made my mouth like a sharp sword: in the shadow of his
hand he hath protected me, and hath made me as a chosen arrow: in his
quiver he hath hidden me.
And he said to me: Thou art my servant Israel, for in thee will I
glory.
%And I said: I have laboured in vain, I have spent my strength
%without cause and in vain: therefore my judgment is with the Lord, and
%my work with my God.
And now saith the Lord, that formed me from the womb to be his
servant, %that I may bring back Jacob unto him, and Israel will not be
%gathered together: and I am glorified in the eyes of the Lord, and my
%God is made my strength.
%And he said: It is a small thing that thou shouldst be my servant
%to raise up the tribes of Jacob, and to convert the dregs of Israel.
Behold, I have given thee to be the light of the Gentiles, that thou
mayst be my salvation even to the farthest part of the earth.
%Thus saith the Lord the redeemer of Israel, his Holy One, to the
%soul that is despised, to the nation that is abhorred, to the servant of
%rulers: 
Kings shall see, and princes shall rise up, and adore for the
Lord's sake, because he is faithful, and for the Holy One of Israel, who
hath chosen thee.

%\columnbreak

\bibleref{Gospel}{Luke 1:57--68}

Elizabeth's full time of being delivered was come: and she
brought forth a son.
And her neighbors and kinsfolks heard that the Lord had shewed his
great mercy towards her: and they congratulated with her.
And it came to pass that on the eighth day they came to circumcise
the child: and they called him by his father's name Zachary.
And his mother answering, said: Not so. But he shall be called
John.
And they said to her: There is none of thy kindred that is called
by this name.
And they made signs to his father, how he would have him called.
And demanding a writing table, he wrote, saying: John is his name.
And they all wondered.
And immediately his mouth was opened and his tongue loosed: and he
spoke, blessing God.
And fear came upon all their neighbours: and all these things were
noised abroad over all the hill country of Judea.
And all they that had heard them laid them up in their heart,
saying: What an one, think ye, shall this child be? For the hand of the
Lord was with him.
And Zachary his father was filled with the Holy Ghost. And he
prophesied, saying:
Blessed be the Lord God of Israel: because he hath visited and
wrought the redemption of his people.



%\bigskip


\smallhead{29th June}

\atitle{Saints Peter and Paul}

\bibleref{Epistle}{Acts 12:1--11}

In those days, Herod the king stretched forth his hands, to
afflict some of the church.
And he killed James, the brother of John, with the sword.
And seeing that it pleased the Jews, he proceeded to take up Peter
also. Now it was in the days of the Azymes.
\challnote{Azymes\ldots\ The festival of the unleavened bread, or the pasch, which
answers to our Easter.}
And when he had apprehended him, he cast him into prison,
delivering him to four files of soldiers, to be kept, intending, after
the pasch, to bring him forth to the people.
Peter therefore was kept in prison. But prayer was made without
ceasing by the church unto God for him.
And when Herod would have brought him forth, the same night, Peter
was sleeping between two soldiers, bound with two chains: and the
keepers before the door kept the prison.
And behold an angel of the Lord stood by him and a light shined in
the room. And he, striking Peter on the side, raised him up, saying:
Arise quickly. And the chains fell off from his hands.
And the angel said to him: Gird thyself and put on thy sandals.
And he did so. And he said to him: Cast thy garment about thee and
follow me.
And going out, he followed him. And he knew not that it was true
which was done by the angel: but thought he saw a vision.
And passing through the first and the second ward, they came to
the iron gate that leadeth to the city which of itself opened to them.
And going out, they passed on through one street. And immediately the
angel departed from him.
And Peter coming to himself, said: Now I know in very deed that
the Lord hath sent his angel and hath delivered me out of the hand of
Herod and from all the expectation of the people of the Jews.

%%\columnbreak
\medskip

\bibleref{Gospel}{Matt.~16:13--19}

At that time, Jesus came into the quarters of Cesarea Philippi: and he
asked his disciples, saying: Whom do men say that the Son of man is?
But they said: Some John the Baptist, and other some Elias, and
others Jeremias, or one of the prophets.
Jesus saith to them: But whom do you say that I am?
Simon Peter answered and said: Thou art Christ, the Son of the
living God.
And Jesus answering said to him: Blessed art thou, Simon
Bar-Jona: because flesh and blood hath not revealed it to thee, but my
Father who is in heaven.
And I say to thee: That thou art Peter; and upon this rock I will
build my church, and the gates of hell shall not prevail against it.
\challnote{Thou art Peter, etc\ldots\ As St. Peter, by divine revelation, here made a
solemn profession of his faith of the divinity of Christ; so in
recompense of this faith and profession, our Lord here declares to him
the dignity to which he is pleased to raise him: viz., that he to whom
he had already given the name of Peter, signifying a rock, St.~John 1.~42, 
should be a rock indeed, of invincible strength, for the support of
the building of the church; in which building he should be, next to
Christ himself, the chief foundation stone, in quality of chief pastor,
ruler, and governor; and should have accordingly all fulness of
ecclesiastical power, signified by the keys of the kingdom of heaven.
Upon this rock, etc\ldots\ The words of Christ to Peter, spoken in the
vulgar language of the Jews which our Lord made use of, were the same as
if he had said in English, Thou art a Rock, and upon this rock I will
build my church. So that, by the plain course of the words, Peter is
here declared to be the rock, upon which the church was to be built:
Christ himself being both the principal foundation and founder of the
same.  Where also note, that Christ, by building his house, that is, his
church, upon a rock, has thereby secured it against all storms and
floods, like the wise builder, St. Matt. 7. 24, 25.  The gates of hell,
etc\ldots\ That is, the powers of darkness, and whatever Satan can do,
either by himself, or his agents. For as the church is here likened to a
house, or fortress, built on a rock; so the adverse powers are likened
to a contrary house or fortress, the gates of which, that is, the whole
strength, and all the efforts it can make, will never be able to prevail
over the city or church of Christ. By this promise we are fully assured,
that neither idolatry, heresy, nor any pernicious error whatsoever shall
at any time prevail over the church of Christ.}
And I will give to thee the keys of the kingdom of heaven.  And
whatsoever thou shalt bind upon earth, it shall be bound also in heaven:
and whatsoever thou shalt loose on earth, it shall be loosed also in
heaven.
\challnote{Loose on earth\ldots\ The loosing the bands of temporal punishments due to
sins, is called an indulgence; the power of which is here granted.}


%%\columnbreak


\bigskip

\smallhead{1st July}

\atitle{Precious Blood}

\bibleref{Epistle}{Heb.~9:11--15}

Brethren: Christ, being come an high Priest of the good things to come,
by a greater and more perfect tabernacle, not made with hand, that is,
not of this creation:
Neither by the blood of goats or of calves, but by his own blood,
entered once into the Holies, having obtained eternal redemption.
%Eternal redemption... By that one sacrifice of his blood, once offered
%on the cross, Christ our Lord paid and exhibited, once for all, the
%general price and ransom of all mankind: which no other priest could do.
For if the blood of goats and of oxen, and the ashes of an heifer,
being sprinkled, sanctify such as are defiled, to the cleansing of the
flesh:
How much more shall the blood of Christ, who by the Holy Ghost
offered himself unspotted unto God, cleanse our conscience from dead
works, to serve the living God?
And therefore he is the mediator of the new testament: that by
means of his death for the redemption of those transgressions which were
under the former testament, they that are called may receive the promise
of eternal inheritance, in Christ Jesus our Lord.

%\bigskip
\medskip

\bibleref{Gospel}{John 19:30--35}

At that time, Jesus, when he had taken the vinegar, said: It is
consummated. And bowing his head, he gave up the ghost.
Then the Jews (because it was the parasceve), that the bodies
might not remain upon the cross on the sabbath day (for that was a great
sabbath day), besought Pilate that their legs might be broken: and that
they might be taken away.
The soldiers therefore came: and they broke the legs of the
first, and of the other that was crucified with him.
But after they were come to Jesus, when they saw that he was
already dead, they did not break his legs.
But one of the soldiers with a spear opened his side: and
immediately there came out blood and water.
And he that saw it hath given testimony: and his testimony is
true. 

\bigskip

\smallhead{2nd July}

\atitle{Visitation}

\bibleref{Epistle}{Cant.~2:8--14}

Behold he cometh leaping upon the
mountains, skipping over the hills.
\challnote{The voice of my beloved: that is, the preaching of the gospel
surmounting difficulties figuratively here expressed by mountains and
little hills.}
My beloved is like a roe, or a young hart. Behold he standeth
behind our wall, looking through the windows, looking through the
lattices.
Behold my beloved speaketh to me: Arise, make haste, my love, my
dove, my beautiful one, and come.
For winter is now past, the rain is over and gone.
The flowers have appeared in our land, the time of pruning is
come: the voice of the turtle is heard in our land:
The fig tree hath put forth her green figs: the vines in flower
yield their sweet smell. Arise, my love, my beautiful one, and come:
My dove in the clefts of the rock, in the hollow places of the
wall, shew me thy face, let thy voice sound in my ears: for thy voice is
sweet, and thy face comely.

\medskip

\bibleref{Gospel}{Luke 1:37--47}

%Because no word shall be impossible with God.
%And Mary said: Behold the handmaid of the Lord: be it done to me
%according to thy word. And the angel departed from her.
At that time Mary rising up, went into the hill country with
haste into a city of Juda.
And she entered into the house of Zachary and saluted Elizabeth.
And it came to pass that when Elizabeth heard the salutation of
Mary, the infant leaped in her womb. And Elizabeth was filled with the
Holy Ghost.
And she cried out with a loud voice and said: Blessed art thou
among women and blessed is the fruit of thy womb.
And whence is this to me that the mother of my Lord should come to
me?
For behold as soon as the voice of thy salutation sounded in my
ears, the infant in my womb leaped for joy.
And blessed art thou that hast believed, because those things
shall be accomplished that were spoken to thee by the Lord.
And Mary said: My soul doth magnify the Lord.
And my spirit hath rejoiced in God my Saviour.


\bigskip

\smallhead{25th July}

\atitle{St.~James}

\bibleref{Epistle}{1 Cor.~4:9--15}

Brethren, I think that God hath set forth us apostles, the last, as it
were men appointed to death. We are made a spectacle to the world and to
angels and to men.
We are fools for Christs sake, but you are wise in Christ: we are
weak, but you are strong: you are honourable, but we without honour.
Even unto this hour we both hunger and thirst and are naked and
are buffeted and have no fixed abode.
And we labour, working with our own hands. We are reviled: and we
bless. We are persecuted: and we suffer it.
We are blasphemed: and we entreat. We are made as the refuse of
this world, the offscouring of all, even until now.
I write not these things to confound you: but I admonish you as my
dearest children.
For if you have ten thousand instructors in Christ, yet not many
fathers. For in Christ Jesus, by the gospel, I have begotten you.

\medskip

\bibleref{Gospel}{Matt.~20:20--23}

At that time the mother of the sons of Zebedee came to Jesus with her sons,
adoring and asking something of him.
Who said to her: What wilt thou? She saith to him: say that these
my two sons may sit, the one on thy right hand, and the other on thy
left, in thy kingdom.
And Jesus answering, said: You know not what you ask. Can you
drink the chalice that I shall drink? They say to him: We can.
He saith to them: My chalice indeed you shall drink; but to sit
on my right or left hand is not mine to give to you, but to them for
whom it is prepared by my Father.


\bigskip

\smallhead{26th July}

\atitle{St.~Anne}

\bibleref{Epistle}{Prov.~31:10--31}

Who shall find a valiant woman? far, and from the uttermost
coasts is the price of her.
The heart of her husband trusteth in her, and he shall have no
need of spoils.
She will render him good, and not evil all the days of her life.
She hath sought wool and flax, and hath wrought by the counsel of
her hands.
She is like the merchant's ship, she bringeth her bread from
afar.
And she hath risen in the night, and given a prey to her
household, and victuals to her maidens.
She hath considered a field, and bought it: with the fruit of her
hands she hath planted a vineyard.
She hath girded her loins with strength, and hath strengthened
her arm.
She hath tasted, and seen that her traffic is good: her lamp
shall not be put out in the night.
She hath put out her hand to strong things, and her fingers have
taken hold of the spindle.
She hath opened her hand to the needy, and stretched out her
hands to the poor.
She shall not fear for her house in the cold of snow: for all her
domestics are clothed with double garments.
She hath made for herself clothing of tapestry: fine linen, and
purple, is her covering.
Her husband is honourable in the gates, when he sitteth among the
senators of the land.
She made fine linen, and sold it, and delivered a girdle to the
Chanaanite.
\challnote{The Chanaanite... The merchant, for Chanaanite, in Hebrew, signifies a
merchant.}
Strength and beauty are her clothing, and she shall laugh in the
latter day.
She hath opened her mouth to wisdom, and the law of clemency is
on her tongue.
She hath looked well on the paths of her house, and hath not
eaten her bread idle.
Her children rose up, and called her blessed: her husband, and he
praised her.
Many daughters have gathered together riches: thou hast surpassed
them all.
Favour is deceitful, and beauty is vain: the woman that feareth
the Lord, she shall be praised.
Give her of the fruit of her hands: and let her works praise her
in the gates.

\medskip

\bibleref{Gospel}{Matt.~13:44--52}

At that time, Jesus spoke to his disciples this parable:
The kingdom of heaven is like unto a treasure hidden in a field.
Which a man having found, hid it, and for joy thereof goeth, and selleth
all that he hath, and buyeth that field.
Again the kingdom of heaven is like to a merchant seeking good
pearls.
Who when he had found one pearl of great price, went his way, and
sold all that he had, and bought it.
Again the kingdom of heaven is like to a net cast into the sea,
and gathering together of all kinds of fishes.
Which, when it was filled, they drew out, and sitting by the
shore, they chose out the good into vessels, but the bad they cast
forth.
So shall it be at the end of the world. The angels shall go out,
and shall separate the wicked from among the just.
And shall cast them into the furnace of fire: there shall be
weeping and gnashing of teeth.
Have ye understood all these things? They say to him: Yes.
He said unto them: Therefore every scribe instructed in the
kingdom of heaven, is like to a man that is a householder, who bringeth
forth out of his treasure new things and old.


\bigskip

\columnbreak

\smallhead{6th August}

\atitle{Transfiguration}

\bibleref{Epistle}{2 Peter 1:16--19}

Dearly beloved:
We have not followed artificial fables, when we made known to you
the power and presence of our Lord Jesus Christ: but we were
eyewitnesses of his greatness.
For he received from God the Father honour and glory, this voice
coming down to him from the excellent glory: This is my beloved Son, in
whom I am well pleased. Hear ye him.
And this voice, we heard brought from heaven, when we were with
him in the holy mount.
And we have the more firm prophetical word: whereunto you do well
to attend, as to a light that shineth in a dark place, until the day
dawn and the day star arise in your hearts.


\bibleref{Gospel}{Matt.~17:1--9}

At that time Jesus took Peter and James, and John his brother,
and bringeth them up into a high mountain apart: And he was transfigured before
them. And his face did shine as the sun: and his garments became white as snow.
And behold there appeared to them Moses and Elias talking with him.  And Peter
answering, said to Jesus: Lord, it is good for us to be here: if thou wilt, let
us make here three tabernacles, one for thee, and one for Moses, and one for
Elias.  And as he was yet speaking, behold a bright cloud overshadowed them.
And lo a voice out of the cloud, saying: This is my beloved Son, in whom I am
well pleased: hear ye him.  And the disciples hearing fell upon their face, and
were very much afraid.  And Jesus came and touched them: and said to them:
Arise, and fear not.  And they lifting up their eyes, saw no one, but only
Jesus.  And as they came down from the mountain, Jesus charged them, saying:
Tell the vision to no man, till the Son of man be risen from the dead.

\bigskip

\smallhead{10th August}

\atitle{St.~Lawrence}

\bibleref{Epistle}{2 Cor.~9:6--10}

Brethren: He who soweth sparingly shall also reap sparingly:
and he who soweth in blessings shall also reap blessings.
Every one as he hath determined in his heart, not with sadness or
of necessity: for God loveth a cheerful giver.
And God is able to make all grace abound in you: that ye always,
having all sufficiently in all things, may abound to every good work,
As it is written: He hath dispersed abroad, he hath given to the
poor: his justice remaineth for ever.
And he that ministereth seed to the sower will both give you bread
to eat and will multiply your seed and increase the growth of the fruits
of your justice.


\bibleref{Gospel}{John 12:24--26}

At that time, Jesus said to his disciples:
Amen, amen, I say to you, unless the grain of wheat falling into
the ground die,
Itself remaineth alone. But if it die it bringeth forth much
fruit. He that loveth his life shall lose it and he that hateth his life
in this world keepeth it unto life eternal.
If any man minister to me, let him follow me: and where I am,
there also shall my minister be. If any man minister to me, him will my
Father honour.



\bigskip
\columnbreak

\smallhead{15th August}

\atitle{Assumption of the Blessed Virgin}

\bibleref{Epistle}{Judith 13:22--25,15:10}%{Ecclus.~24:11--13,15--20}
\label{Ep.assump}

The Lord hath
blessed thee by his power, because by thee he hath brought our enemies
to nought.
%And Ozias the prince of the people of Israel, said to her:
Blessed art thou, O daughter, by the Lord the most high God, above all
women upon the earth.
Blessed be the Lord who made heaven and earth, who hath directed
thee to the cutting off the head of the prince of our enemies.
Because he hath so magnified thy name this day, that thy praise
shall not depart out of the mouth of men who shall be mindful of the
power of the Lord for ever, for that thou hast not spared thy life, by
reason of the distress and tribulation of thy people, but hast prevented
our ruin in the presence of our God.
Thou art the glory of Jerusalem, thou art the joy of
Israel, thou art the honour of our people:



\bibleref{Gospel}{Luke 1:41--50}%{Luke 10:38--42}

At that time, Elizabeth was filled with the
Holy Ghost.
And she cried out with a loud voice and said: Blessed art thou
among women and blessed is the fruit of thy womb.
And whence is this to me that the mother of my Lord should come to
me?
For behold as soon as the voice of thy salutation sounded in my
ears, the infant in my womb leaped for joy.
And blessed art thou that hast believed, because those things
shall be accomplished that were spoken to thee by the Lord.
And Mary said: My soul doth magnify the Lord.
And my spirit hath rejoiced in God my Saviour.
Because he hath regarded the humility of his handmaid: for behold
from henceforth all generations shall call me blessed.
\challnote{Shall call me blessed\ldots\ These words are a prediction of that honour
which the church in all ages should pay to the Blessed Virgin. Let
Protestants examine whether they are any way concerned in this prophecy.}
Because he that is mighty hath done great things to me: and holy
is his name.
And his mercy is from generation unto generations, to them that
fear him.

\bigskip

\smallhead{16th August}

\atitle{St.~Joachim}

\bibleref{Epistle}{Ecclus.~31:8--11}

Blessed is the man that is found without blemish: and that
hath not gone after gold, nor put his trust in money nor in treasures.
Who is he, and we will praise him? for he hath done wonderful
things in his life.
Who hath been tried thereby, and made perfect, he shall have
glory everlasting. He that could have transgressed, and hath not
transgressed: and could do evil things, and hath not done them:
Therefore are his goods established in the Lord, and all the
church of the saints shall declare his alms.


\bibleref{Gospel}{Matt.~1:1--6}
\label{Go.joachim}

The book of the generation of Jesus Christ, the son of David, the
son of Abraham:
Abraham begot Isaac. And Isaac begot Jacob. And Jacob begot Judas
and his brethren.
And Judas begot Phares and Zara of Thamar. And Phares begot Esron.
And Esron begot Aram.
And Aram begot Aminadab. And Aminadab begot Naasson. And Naasson
begot Salmon.
And Salmon begot Booz of Rahab. And Booz begot Obed of Ruth.  And
Obed begot Jesse.
And Jesse begot David the king. And David the king begot Solomon,
of her that had been the wife of Urias.
And Solomon begot Roboam. And Roboam begot Abia. And Abia begot
Asa.
And Asa begot Josaphat. And Josaphat begot Joram. And Joram begot
Ozias.
And Ozias begot Joatham. And Joatham begot Achaz. And Achaz begot
Ezechias.
And Ezechias begot Manasses. And Manasses begot Amon. And Amon
begot Josias.
And Josias begot Jechonias and his brethren in the transmigration
of Babylon.
And after the transmigration of Babylon, Jechonias begot
Salathiel. And Salathiel begot Zorobabel.
And Zorobabel begot Abiud. And Abiud begot Eliacim. And Eliacim
begot Azor.
And Azor begot Sadoc. And Sadoc begot Achim. And Achim begot
Eliud.
And Eliud begot Eleazar. And Eleazar begot Mathan. And Mathan
begot Jacob.
And Jacob begot Joseph the husband of Mary, of whom was born
Jesus, who is called Christ.



\bigskip

\smallhead{22nd August}

\atitle{Immaculate Heart of Mary}

\bibleref{Epistle}{Ecclus.~24:23--31}
\label{Ep.immacheart}

As the vine I have brought forth a pleasant odour: and my flowers
are the fruit of honour and riches.
I am the mother of fair love, and of fear, and of knowledge, and
of holy hope.
In me is all grace of the way and of the truth, in me is all hope
of life and of virtue.
Come over to me, all ye that desire me, and be filled with my
fruits.
For my spirit is sweet above honey, and my inheritance above
honey and the honeycomb.
My memory is unto everlasting generations.
They that eat me, shall yet hunger: and they that drink me, shall
yet thirst.
He that hearkeneth to me, shall not be confounded: and they that
work by me, shall not sin.
They that explain me shall have life everlasting.


\bibleref{Gospel}{John 19:25--27} 
\label{Go.stabant}

At that time there stood by the cross of Jesus, his mother and his
mother's sister, Mary of Cleophas, and Mary Magdalen.
When Jesus therefore had seen his mother and the disciple
standing whom he loved, he saith to his mother: Woman, behold thy son.
After that, he saith to the disciple: Behold thy mother.  And
from that hour, the disciple took her to his own.


\bigskip

\smallhead{24th August}

\atitle{St.~Bartholomew}

\bibleref{Epistle}{1 Cor.~12:27--31}

Brethren, you are the body of Christ and members of member.
And God indeed hath set some in the church; first apostles,
secondly prophets, thirdly doctors: after that miracles: then the graces
of healings, helps, governments, kinds of tongues, interpretations of
speeches.
Are all apostles? Are all prophets? Are all doctors?
Are all workers of miracles? Have all the grace of healing?  Do
all speak with tongues? Do all interpret?
But be zealous for the better gifts. And I shew unto you yet a
more excellent way.


\bibleref{Gospel}{Luke 6:12--19}

At that time, Jesus went out into a
mountain to pray: and he passed the whole night in the prayer of God.
And when day was come, he called unto him his disciples: and he
chose twelve of them (whom also he named apostles):
Simon, whom he surnamed Peter, and Andrew his brother, James and
John, Philip and Bartholomew,
Matthew and Thomas, James the son of Alpheus, and Simon who is
called Zelotes,
And Jude the brother of James, and Judas Iscariot, who was the
traitor.
And coming down with them, he stood in a plain place: and the
company of his disciples and a very great multitude of people from all
Judea and Jerusalem and the sea coast, both of Tyre and Sidon,
Who were come to hear him and to be healed of their diseases. And
they that were troubled with unclean spirits were cured.
And all the multitude sought to touch him: for virtue went out
from him and healed all.


\bigskip

\smallhead{8th September}

\atitle{Nativity of Mary}

\bibleref{Epistle}{Prov.~8:22--35}

As on 8th December, Immaculate Conception, page \pageref{Ep.immac}.

\emph{The Lord possessed me in the beginning of his ways\ldots} 

\bibleref{Gospel}{Matt.~1:1--6}

As on 16 August, St.~Joachim, page \pageref{Go.joachim}.

\emph{The book of the generation of Jesus Christ\ldots}

\bigskip

\smallhead{14th September}

\atitle{Exaltation of the Holy Cross}


\bibleref{Epistle}{Phil.~2:5-11}


Brethren, let this mind be in you, which was also in Christ Jesus: Who being in the
form of God, thought it not robbery to be equal with God: But emptied himself,
taking the form of a servant, being made in the likeness of men, and in habit
found as a man.
\challnote{Emptied himself, exinanivit\ldots\ made himself as of no account.}  He humbled
himself, becoming obedient unto death, even to the death of the cross.  For
which cause, God also hath exalted him and hath given him a name which is above
all names: That in the name of Jesus every knee should bow, of those that are
in heaven, on earth, and under the earth: And that every tongue should confess
that the Lord Jesus Christ is in the glory of God the Father.


\bibleref{Gospel}{John 12:31--36}

At that time: Jesus said to the multitudes of the Jews:
Now is the judgment of the world: now shall the prince of this
world be cast out.
And I, if I be lifted up from the earth, will draw all things to
myself.
(Now this he said, signifying what death he should die.)
The multitude answered him: We have heard out of the law that
Christ abideth for ever. And how sayest thou: The Son of man must be
lifted up? Who is this Son of man?
Jesus therefore said to them: Yet a little while, the light is
among you. Walk whilst you have the light, and the darkness overtake you
not. And he that walketh in darkness knoweth not whither be goeth.
Whilst you have the light, believe in the light, that you may be
the children of light. %These things Jesus spoke: and he went away and
%hid himself from them.


\bigskip

\smallhead{15th September}

\atitle{Seven Sorrows of Mary}

\bibleref{Epistle}{Judith 13:22--25}

As on 15th August, the Assumption of Our Lady, page \pageref{Ep.assump}

\emph{The Lord hath
blessed thee by his power\ldots}

\bibleref{Gospel}{John 19:25--27}

As on 22nd August, Immaculate Heart of Mary, page \pageref{Go.stabant}.

\emph{At that time there stood by the cross of Jesus\ldots}

\bigskip

\smallhead{21st September}

\atitle{St.~Matthew}

\bibleref{Epistle}{Ezech.~1:10--14}

As on 25th April, St.~Mark, page \pageref{Ep.stmark}.

\emph{As for the likeness of their faces\ldots}

\bibleref{Gospel}{Matt.~9:9--13}

At that time, Jesus saw a man sitting in the
custom house, named Matthew; and he saith to him: Follow me. And he
arose up and followed him.
And it came to pass as he was sitting at meat in the house, behold
many publicans and sinners came, and sat down with Jesus and his
disciples.
And the Pharisees seeing it, said to his disciples: Why doth your
master eat with publicans and sinners?
But Jesus hearing it, said: They that are in health need not a
physician, but they that are ill.
Go then and learn what this meaneth, I will have mercy and not
sacrifice. For I am not come to call the just, but sinners.



%\bigskip

\smallhead{29th September}

\atitle{St.~Michael Archangel}

\bibleref{Epistle}{Apoc.~1:1--5}


In those days: God signified the things which must shortly come to pass,
sending by his angel to his servant John,
%The things which must shortly come... and again it is said, ver. 3, The
%time is at hand... This can not be meant of all the things prophesied in
%the Apocalypse, where mention is made also of the day of judgment, and
%of the glory of heaven at the end of the world. That some things were to
%come to pass shortly, is evident, by what is said to the Seven Churches,
%chap. 2 and 3, Or that the persecutions foretold should begin shortly.
%Or that these words signified, that all time is short, and that from the
%coming of Christ, we are now in the last age or last hour. See 1 John
%2.18.
who hath given testimony to the word of God and the testimony of
Jesus Christ, what things soever he hath seen.
Blessed is he that readeth and heareth the words of this prophecy:
and keepeth those things which are written in it. For the time is at
hand.
John to the seven churches which are in Asia. Grace be unto you and
peace, from him that is and that was and that is to come: and from the
seven spirits which are before his throne:
And from Jesus Christ, who is the faithful witness, the first
begotten of the dead and the prince of the kings of the earth, who hath
loved us and washed us from our sins in his own blood,


\bibleref{Gospel}{Matt.~18:1--10}

At that time the disciples came to Jesus, saying: Who, thinkest
thou, is the greater in the kingdom of heaven?
And Jesus, calling unto him a little child, set him in the midst
of them.
And said: amen I say to you, unless you be converted, and become
as little children, you shall not enter into the kingdom of heaven.
Whosoever therefore shall humble himself as this little child, he
is the greater in the kingdom of heaven.
And he that shall receive one such little child in my name,
receiveth me.
But he that shall scandalize one of these little ones that believe
in me, it were better for him that a millstone should be hanged about
his neck, and that he should be drowned in the depth of the sea.
%Shall scandalize... That is, shall put a stumblingblock in their way,
%and cause them to fall into sin.
Woe to the world because of scandals. For it must needs be that
scandals come: but nevertheless woe to that man by whom the scandal
cometh.
%It must needs be, etc... Viz., considering the wickedness and corruption
%of the world.
And if thy hand, or thy foot, scandalize thee, cut it off, and
cast it from thee. It is better for thee to go into life maimed or lame,
than having two hands or two feet, to be cast into everlasting fire.
%Scandalize thee... That is, cause thee to offend.
And if thy eye scandalize thee, pluck it out, and cast it from
thee. It is better for thee having one eye to enter into life, than
having two eyes to be cast into hell fire.
See that you despise not one of these little ones: for I say to
you, that their angels in heaven always see the face of my Father who is
in heaven.

\bigskip

\smallhead{7th October}

\atitle{Our Lady of the Rosary}

\bibleref{Epistle}{Prov.~8:22--24,32--35}

The Lord possessed me in the beginning of his ways, before he made any thing
from the beginning.   I was set up from eternity, and of old before the earth
was made.   The depths were not as yet, and I was already conceived. Now therefore, ye children, hear
me: Blessed are they that keep my ways.  Hear instruction and be wise, and
refuse it not.   Blessed is the man that heareth me, and that watcheth daily at
my gates, and waiteth at the posts of my doors.   He that shall find me, shall
find life, and shall have salvation from the Lord.


\bibleref{Gospel}{Luke 1:26--38}

As on 25th March, Annunciation, page \pageref{Go.angelus}.

\emph{At that time the angel Gabriel was sent from God\ldots}

\bigskip

\smallhead{11th October}

\atitle{Maternity of Mary}

\bibleref{Epistle}{Ecclus.~24:23--31}

As on 22nd August, Immaculate Heart of Mary, page \pageref{Ep.immacheart}.

\emph{As the vine I have brought forth a pleasant odour\ldots}

\bibleref{Gospel}{Luke 2:43--51}

At that time: when they returned, the
child Jesus remained in Jerusalem. And his parents knew it not.  And thinking
that he was in the company, they came a day's journey and sought him among
their kinsfolks and acquaintance.  And not finding him, they returned into
Jerusalem, seeking him.  And it came to pass, that, after three days, they
found him in the temple, sitting in the midst of the doctors, hearing them and
asking them questions.  And all that heard him were astonished at his wisdom
and his answers.  And seeing him, they wondered. And his mother said to him:
Son, why hast thou done so to us? Behold thy father and I have sought thee
sorrowing.  And he said to them: How is it that you sought me? Did you not know
that I must be about my father's business?  And they understood not the word
that he spoke unto them.  And he went down with them and came to Nazareth and
was subject to them. 

\bigskip

\smallhead{18th October}

\atitle{St.~Luke}

\bibleref{Epistle}{2 Cor.~8:16--24}

Brethren, I give thanks to God, who hath given the same carefulness for you
in the heart of Titus.
For indeed he accepted the exhortation: but, being more careful,
of his own will he went unto you.
We have sent also with him the brother whose praise is in the
gospel through all the churches.
And not that only: but he was also ordained by the churches
companion of our travels, for this grace, which is administered by us,
to the glory of the Lord and our determined will:
Avoiding this, lest any man should blame us in this abundance
which is administered by us.
For we forecast what may be good, not only before God but also
before men.
And we have sent with them our brother also, whom we have often
proved diligent in many things, but now much more diligent: with much
confidence in you,
Either for Titus, who is my companion and fellow labourer towards
you, or our brethren, the apostles of the churches, the glory of Christ.
Wherefore shew ye to them, in the sight of the churches, the
evidence of your charity and of our boasting on your behalf.


\bibleref{Gospel}{Luke 10:1--9}

As on 25th April, St.~Mark, page \pageref{Go.stmark}

\emph{At that time, the Lord appointed also other seventy-two\ldots}

\bigskip

\smallhead{28th October}

\atitle{Sts.~Simon and Jude}

\bibleref{Epistle}{Eph.~4:7--13}

But to every one of us is given grace, according to the measure of
the giving of Christ.
Wherefore he saith: Ascending on high, he led captivity captive: he
gave gifts to men.
Now that he ascended, what is it, but because he also descended
first into the lower parts of the earth?
He that descended is the same also that ascended above all the
heavens: that he might fill all things.
And he gave some apostles, and some prophets, and other some
evangelists, and other some pastors and doctors:
\challnote{Gave some apostles--Until we all meet, etc... Here it is plainly
expressed, that Christ has left in his church a perpetual succession of
orthodox pastors and teachers, to preserve the faithful in unity and
truth.}
For the perfecting of the saints, for the word of the ministry,
for the edifying of the body of Christ:
Until we all meet into the unity of faith and of the knowledge of
the Son of God, unto a perfect man, unto the measure of the age of the
fulness of Christ:

\bigskip

\bibleref{Gospel}{John 15:17--25}

These things I command you, that you love one another.
If the world hate you, know ye that it hath hated me before you.
If you had been of the world, the world would love its own: but
because you are not of the world, but I have chosen you out of the
world, therefore the world hateth you.
Remember my word that I said to you: The servant is not greater
than his master. If they have persecuted me, they will also persecute
you. If they have kept my word, they will keep yours also.
But all these things they will do to you for my name's sake:
because they know not him that sent me.
If I had not come and spoken to them, they would not have sin:
but now they have no excuse for their sin.
He that hateth me hateth my Father also.
If I had not done among them the works that no other man hath
done, they would not have sin: but now they have both seen and hated
both me and my Father.
But that the word may be fulfilled which is written in their law:
they hated me without cause.


\bigskip

\smallhead{Last Sunday of October}

\atitle{Christ the King}

\bibleref{Epistle}{Col.~1:12--20}

Brethren, giving thanks to God the Father, who hath made us worthy to be
partakers of the lot of the saints in light:
Who hath delivered us from the power of darkness and hath
translated us into the kingdom of the Son of his love,
in whom we have redemption through his blood, the remission of
sins:
Who is the image of the invisible God, the firstborn of every
creature:
\challnote{The firstborn\ldots\ That is, first begotten; as the Evangelist declares,
the only begotten of his Father: hence, St. Chrisostom explains
firstborn, not first created, as he was not created at all, but born of
his Father before all ages; that is, coeval with the Father and with the
Holy Ghost.}
For in him were all things created in heaven and on earth, visible
and invisible, whether thrones, or dominations, or principalities, or
powers. All things were created by him and in him.
And he is before all: and by him all things consist.
And he is the head of the body, the church: who is the beginning,
the firstborn from the dead, that in all things he may hold the primacy:
Because in him, it hath well pleased the Father that all fulness
should dwell:
And through him to reconcile all things unto himself, making peace
through the blood of his cross, both as to the things that are on earth
and the things that are in heaven, in Christ Jesus our Lord.

\bigskip

\bibleref{Gospel}{John 18:33--37}

At that time, Pilate % therefore went into the hall again and called Jesus and
said to Jesus: Art thou the king of the Jews?
Jesus answered: Sayest thou this thing of thyself, or have others
told it thee of me?
Pilate answered: Am I a Jew? Thy own nation and the chief priests
have delivered thee up to me. What hast thou done?
Jesus answered: My kingdom is not of this world. If my kingdom
were of this world, my servants would certainly strive that I should not
be delivered to the Jews: but now my kingdom is not from hence.
Pilate therefore said to him: Art thou a king then? Jesus
answered: Thou sayest that I am a king. For this was I born, and for
this came I into the world; that I should give testimony to the truth.
Every one that is of the truth heareth my voice.


\bigskip

%\columnbreak

\smallhead{1st November}

\atitle{All Saints}

\bibleref{Epistle}{Apoc.~7:2--12}

In those days, behold, I, John, saw another angel ascending from the rising of the sun,
having the sign of the living God. And he cried with a loud voice to the
four angels to whom it was given to hurt the earth and the sea,
saying: Hurt not the earth nor the sea nor the trees, till we sign
the servants of our God in their foreheads.
And I heard the number of them that were signed. An hundred forty-
four thousand were signed, of every tribe of the children of Israel.
Of the tribe of Juda, twelve thousand signed: Of the tribe of
Ruben, twelve thousand signed: Of the tribe of Gad, twelve thousand
signed:
Of the tribe of Aser, twelve thousand signed: Of the tribe of
Nephthali, twelve thousand signed: Of the tribe of Manasses, twelve
thousand signed:
Of the tribe of Simeon, twelve thousand signed: Of the tribe of
Levi, twelve thousand signed: Of the tribe of Issachar, twelve thousand
signed:
Of the tribe of Zabulon, twelve thousand signed: Of the tribe of
Joseph, twelve thousand signed: Of the tribe of Benjamin, twelve
thousand signed.
After this, I saw a great multitude, which no man could number, of
all nations and tribes and peoples and tongues, standing before the
throne and in sight of the Lamb, clothed with white robes, and palms in
their hands.
And they cried with a loud voice, saying: Salvation to our God,
who sitteth upon the throne and to the Lamb.
And all the angels stood round about the throne and the ancients
and the four living creatures. And they fell down before the throne upon
their faces and adored God,
saying: Amen. Benediction and glory and wisdom and thanksgiving,
honour and power and strength, to our God, for ever and ever. Amen.


\bibleref{Gospel}{Matt.~5:1--12}

At that time, Jesus, seeing the multitudes, went up into a mountain, and when he
was sat down, his disciples came unto him.
And opening his mouth he taught them, saying:
Blessed are the poor in spirit: for theirs is the kingdom of
heaven.
\challnote{The poor in spirit\ldots\ That is, the humble; and they whose spirit is not
set upon riches.}
Blessed are the meek: for they shall possess the land.
Blessed are they that mourn: for they shall be comforted.
Blessed are they that hunger and thirst after justice: for they
shall have their fill.
Blessed are the merciful: for they shall obtain mercy.
Blessed are the clean of heart: they shall see God.
Blessed are the peacemakers: for they shall be called the children
of God.
Blessed are they that suffer persecution for justice' sake: for
theirs is the kingdom of heaven.
Blessed are ye when they shall revile you, and persecute you, and
speak all that is evil against you, untruly, for my sake:
Be glad and rejoice for your reward is very great in heaven. For
so they persecuted the prophets that were before you.


%\bigskip

\smallhead{2nd November}

\atitle{All Souls}

\heading{First Mass}

\bibleref{Epistle}{1 Cor.~15:51--57}

Brethren: Behold, I tell you a mystery. We shall all indeed rise again: but
we shall not all be changed.
In a moment, in the twinkling of an eye, at the last trumpet: for
the trumpet shall sound and the dead shall rise again incorruptible. And
we shall be changed.
For this corruptible must put on incorruption: and this mortal
must put on immortality.
And when this mortal hath put on immortality, then shall come to
pass the saying that is written: Death is swallowed up in victory.
O death, where is thy victory? O death, where is thy sting?
Now the sting of death is sin: and the power of sin is the law.
But thanks be to God, who hath given us the victory through our
Lord Jesus Christ.



\bibleref{Gospel}{John 5:25--29}

At that time Jesus said to the multitudes of the Jews:
Amen, amen, I say unto you, that the hour cometh, and now is, when
the dead shall hear the voice of the Son of God: and they that hear
shall live.
For as the Father hath life in himself, so he hath given to the
Son also to have life in himself.
And he hath given him power to do judgment, because he is the Son
of man.
Wonder not at this: for the hour cometh wherein all that are in
the graves shall hear the voice of the Son of God.
And they that have done good things shall come forth unto the
resurrection of life: but they that have done evil, unto the
resurrection of judgment.


\heading{Second Mass}

\bibleref{Epistle}{2 Mac.~12:43--46}

In those days: The most valiant man Judas, making a gathering, sent twelve thousand drachmas of silver
to Jerusalem for sacrifice to be offered for the sins of the dead,
thinking well and religiously concerning the resurrection.
(For if he had not hoped that they that were slain should rise
again, it would have seemed superfluous and vain to pray for the dead,)
And because he considered that they who had fallen asleep with
godliness, had great grace laid up for them.
%With godliness... Judas hoped that these men who died fighting for the
%cause of God and religion, might find mercy: either because they might
%be excused from mortal sin by ignorance; or might have repented of their
%sin, at least at their death.
It is therefore a holy and wholesome thought to pray for the
dead, that they may be loosed from sins.


\bibleref{Gospel}{John 6:37--40}

At that time Jesus said to the multitudes of the Jews:
All that the Father giveth to me shall come to me: and him that
cometh to me, I will not cast out.
Because I came down from heaven, not to do my own will but the
will of him that sent me.
Now this is the will of the Father who sent me: that of all that
he hath given me, I should lose nothing; but should raise it up again in
the last day.
And this is the will of my Father that sent me: that every one who
seeth the Son and believeth in him may have life everlasting. And I will
raise him up in the last day.


\heading{Third Mass}

%\smallhead{Also Daily Mass for the Dead}

\bibleref{Epistle}{Apoc.~14:13}


At that time Jesus said to the multitudes of the Jews:
And I heard a voice from heaven, saying to me: Write: Blessed are
the dead who die in the Lord. From henceforth now, saith the Spirit,
that they may rest from their labours. For their works follow them.



\bibleref{Gospel}{John 6:51--55}

At that time Jesus said to the multitudes of the Jews:
I am the living bread which came down from heaven.
If any man eat of this bread, he shall live for ever: and the
bread that I will give is my flesh, for the life of the world.
The Jews therefore strove among themselves, saying: How can this
man give us his flesh to eat?
Then Jesus said to them: Amen, amen, I say unto you: except you
eat the flesh of the Son of man and drink his blood, you shall not have
life in you.
%Except you eat and drink, etc... To receive the body and blood of
%Christ, is a divine precept, insinuated in this text; which the faithful
%fulfil, though they receive but in one kind; because in one kind they
%receive both body and blood, which cannot be separated from each other.
%Hence, life eternal is here promised to the worthy receiving, though but
%in one kind.  Ver. 52. If any man eat of this bread, he shall live for
%ever; and the bread that I will give, is my flesh for the life of the
%world. Ver. 58. He that eateth me, the same also shall live by me. Ver.
%59. He that eateth this bread, shall liver for ever.
He that eateth my flesh and drinketh my blood hath everlasting
life: and I will raise him up in the last day.

\bigskip

\smallhead{9th November}

\atitle{Dedication of St.~Saviour's}

\bibleref{Epistle}{Apoc.~21:2--5}

In those days
I, John, saw the holy city, the new Jerusalem, coming down out
of heaven from God, prepared as a bride adorned for her husband.
And I heard a great voice from the throne, saying: Behold the
tabernacle of God with men: and he will dwell with them.  And they shall
be his people: and God himself with them shall be their God.
And God shall wipe away all tears from their eyes: and death shall
be no more. Nor mourning, nor crying, nor sorrow shall be any more, for
the former things are passed away.
And he that sat on the throne, said: Behold, I make all things
new. %And he said to me: Write. For these words are most faithful and
%true.

\medskip

\bibleref{Gospel}{Luke 19:1--10}

At that time Jesus,
entering in, walked through Jericho.
And behold, there was a man named Zacheus, who was the chief of
the publicans: and he was rich.
And he sought to see Jesus who he was: and he could not for the
crowd, because he was low of stature.
And running before, he climbed up into a sycamore tree, that he
might see him: for he was to pass that way.
And when Jesus was come to the place, looking up, he saw him and
said to him: Zacheus, make haste and come down: for this day I must
abide in thy house.
And he made haste and came down and received him with joy.
And when all saw it, they murmured, saying, that he was gone to be
a guest with a man that was a sinner.
But Zacheus standing, said to the Lord: Behold, Lord, the half of
my goods I give to the poor; and if I have wronged any man of any thing,
I restore him fourfold.
Jesus said to him: This day is salvation come to this house,
because he also is a son of Abraham.
For the Son of man is come to seek and to save that which was
lost.


%\bigskip


\bigskip

\smallhead{30th November}

\atitle{St.~Andrew}

\bibleref{Epistle}{Rom.~10:10--18}

For, with the heart, we believe unto justice: but, with the
mouth, confession is made unto salvation.
For the scripture saith: Whosoever believeth in him shall not be
confounded.
For there is no distinction of the Jew and the Greek: for the
same is Lord over all, rich unto all that call upon him.
For whosoever shall call upon the name of the Lord shall be
saved.
How then shall they call on him in whom they have not believed?
Or how shall they believe him of whom they have not heard? And how shall
they hear without a preacher?
And how shall they preach unless they be sent, as it is written:
How beautiful are the feet of them that preach the gospel of peace, of
them that bring glad tidings of good things?
\challnote{Unless they be sent... Here is an evident proof against all new
teachers, who have all usurped to themselves the ministry without any
lawful mission, derived by succession from the apostles, to whom Christ
said, John 20.21, As my Father hath sent me, I also send you.}
But all do not obey the gospel. For Isaias saith: Lord, who hath
believed our report?
Faith then cometh by hearing; and hearing by the word of Christ.
But I say: Have they not heard? Yes, verily: Their sound hath
gone forth into all the earth: and their words unto the ends of the
whole world.

\goodbreak

\bibleref{Gospel}{Matt.~4:18--22}

And Jesus walking by the sea of Galilee, saw two brethren, Simon
who is called Peter, and Andrew his brother, casting a net into the sea
(for they were fishers).
And he saith to them: Come ye after me, and I will make you to be
fishers of men.
And they immediately leaving their nets, followed him.
And going on from thence, he saw other two brethren, James the son
of Zebedee, and John his brother, in a ship with Zebedee their father,
mending their nets: and he called them.
And they forthwith left their nets and father, and followed him.


