\documentclass[a5paper,11pt,twoside]{memoir}
\usepackage[british,latin]{babel}
\usepackage{lettrine}
\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
\setsansfont{Calluna Sans}
\setmainfont{EB Garamond}
\newfontfamily{\semibf}{Calluna-Semibold}
\newfontfamily{\anavio}{Anavio}
\newfontface{\vectis}{Vectis_Bold_OT}
\newfontfamily{\libertine}{Linux Libertine O}
\newfontface{\versicles}{Versiculum}
\newfontface{\cruci}{Juuji}
%\usepackage{mparhack}
%\usepackage{verse}
\usepackage{nopageno}
\usepackage{parallel}
%\usepackage{multicol}
%\usepackage{fncylab}
%\usepackage{hanging}
\usepackage{graphicx}
\usepackage{gregoriotex}
%\usepackage{libgreek}
%\usepackage{scrpage2}
%\settrimmedsize{9in}{6in}{*}
%\setlength{\trimtop}{0pt}
%\setlength{\trimedge}{0pt}
%\addtolength{\trimedge}{-\paperwidth}
\settypeblocksize{170mm}{115mm}{*} % Was 101mm in a5
\setulmargins{*}{*}{1.618}
\setlrmargins{*}{*}{1}
\setheadfoot{\onelineskip}{2\onelineskip}
\setheaderspaces{*}{.8\onelineskip}{*}
\checkandfixthelayout

\input conf-hymns.tex

\setgrefactor{18}

\setsecnumdepth{chapter}

\setsecheadstyle{\LARGE\scshape\centering}
\setsubsecheadstyle{\Large\scshape\centering}
\setsubsubsecheadstyle{\large\scshape\centering}

\def\greinitialformat#1{%
{\fontsize{24}{24}\vectis #1}}


\def\gretranslationformat#1{%
{\fontsize{8}{8}\selectfont #1}%
}

\begin{document}

\pagestyle{empty}

\section{Prayer before choir practice}

%\rubrics{Indulgence of 3 years and 300 days.}

\rubrics{Oratio Ante Scholam Musicae}

\gresetfirstannotation{Ant.}
\gresetsecondannotation{5.}
%\gresetfirstlineaboveinitial{Ant.\\5.}{Ant.\\5.}
%\gresetsecondlineaboveinitial{5.}{5.}
\includescore{kyriale/repleatur.tex}

\bigskip

[Let my mouth be filled with thy praise, in order that I be able to sing;
my lips will rejoice for as long as I sing unto thee.]

\bigskip


\begin{Parallel}{\gcolwidth}{\gcolwidth}
\latin{\Vbar Laudábo Dóminum in vita mea.}
\vern{I will give praise unto the Lord of my life.}
\latin{\Rbar Psallam Deo meo quámdiu ero.}
\vern{I will sing psalms unto God all the days of my life.}
\latin{Orémus.}
\vern{Let us pray.}
\latin{Súscipe, quaésumus, Dómine,\\
sacrifícium labiórum nostrórum: \dag\ \\
et intercedéntibus sanctis tuis\\
Gregório atque Caecília, tua nobis\\
pietáte concéde; ut, quam\\
offérimus laudem peregrinántes in\\
terris, * hanc tibi perpétuo\\
concinére mereámur in caelis.\\
Per Christum Dóminum nostrum. \\
\Rbar Amen.}
\vern{Accept, we beseech thee, O Lord,\\
the sacrifice (homage) of our lips,\\
and through the intercession of thy\\
saints Gregory and Caecilia, grant\\
unto us thy mercy; that through\\
these offerings of praise during our\\
earthly pilgrimage, * we may be\\
found worthy to sing your praises\\
eternally in heaven.
Through\\
Christ our Lord. \Rbar Amen.}
\end{Parallel}


\end{document}

