\section{Prayers after Low Mass}

\label{HailMary}

\begin{Parallel}{\gcolwidth}{\gcolwidth}
{\emph{To be said thrice---}\par}
\firstlatin{A}{ve}{ María, grátia plena, Dóminus tecum, benedícta tu in muliéribus et benedíctus fructis ventris tui, Jesus.}
\firstvern{H}{ail}{ Mary, full of grace, the Lord is with thee.  Blessed art thou among women and blessed is the fruit of thy womb, Jesus.}
\latin{Sancta María, Mater Dei, ora pro nobis peccatóribus, nunc et in hora mortis nostrae. Amen. }
\vern{Holy Mary, Mother of God, pray for us, sinners, now and at the hour of our death.  Amen.}

\smallskip

\label{HailHolyQueen}
\firstlatin{S}{alve}{ Regína, Mater misericórdi\ae , vita, dulcédo, et spes nostra, salve. Ad te clamámus, éxsules
fílii Hev\ae . Ad te suspirámus geméntes et flentes in hac lacrimárum valle. Eia ergo, Advocáta nostra, illos
tuos misericórdes óculos ad nos convérte. Et Jesum, benedíctum fructum ventris tui, nobis, post hoc
exsílium, osténde.}
\firstvern{H}{ail!}{ holy Queen, Mother of Mercy; hail, our life, our
sweetness, and our hope! To thee do we cry, poor
banished children of Eve; to thee do we send up our
sighs, mourning and weeping in this valley of tears. Turn,
then, most gracious advocate, thine eyes of mercy
towards us; and after this our exile, show unto us the
blessed fruit of thy womb, Jesus.}
\latin{O clemens, o pia, o dulcis Virgo María.}
\vern{O clement, O loving, O sweet Virgin Mary.}

\bigskip

\latin{\Vbar Ora pro nobis, sancta Dei Géni\-trix.}
\vern{\Vbar Pray for us O holy Mother of God}
\latin{\Rbar Ut digni efficiámur promissiónibus Christi.}
\vern{\Rbar That we may be made worthy of the promises of Christ.}

\smallskip

\latin{Orémus.}
\vern{Let us pray.}
\firstlatin{D}{eus}{ refúgium nostrum et virtus, pópulum ad te clamántem propítius réspice; et intercedénte gloriósa et immaculáta Vírgine Dei Genitríce María, cum beáto Josepho ejus Sponso, ac beátis Apóstolis tuis Petro et Paulo, et ómnibus Sanctis, quas pro conversióne peccatórum, pro libertáte et exaltatióne sanct\ae\ Matris Ecclési\ae , preces effúndimus, miséricors et benígnus exáudi. Per eúmdem Christum Dóminum nostrum.}
\firstvern{O}{ God,}{ our refuge and our strength, mercifully look
down on Thy people who cry to Thee; and through
the intercession of the glorious and Immaculate Virgin
Mary, Mother of God, of St.~Joseph her Spouse, of Thy
blessed Apostles Peter and Paul, and of all the Saints,
in mercy and goodness hear our prayers for the conversion 
of sinners, and for the liberty and exaltation of our
Holy Mother the Church. Through the same Christ our
Lord.}
\latin{\Rbar Amen.}
\vern{\Rbar Amen.}

%\newpage
\smallskip

\firstlatin{S}{ancte}{ Míchael Archángele, defénde nos in pr\ae lio. Contra nequítiam et insídias diáboli esto pr\ae sídium. Imperet illi Deus, súpplices deprecámur. Tuque princeps milítiae c\ae léstis, Sátanam aliósque spíritus malígnos, qui ad perditiónem animárum pervagántur in mundo divína virtúte in inférnum detrúde.}
\firstvern{B}{lessed}{ Michael, Archangel, defend us in the hour of
conflict; be our safeguard against the wickedness
and snares of the devil---may God restrain him, we
humbly pray:---and do thou, O Prince of the heavenly
host, by the power of God thrust Satan down to hell,
and, with him, the other wicked spirits who wander
through the world for the ruin of souls.}
%Michael, Archangel, defend us in the day of battle, be our
%safeguard against the wickedness and snares of the devil.  May God rebuke him, we
%humbly pray : and do thou,  Prince of the heavenly host, by the power
%of God thrust down to
%hell Satan, and all wicked spirits who wander through the world for the
%ruin of souls.
\latin{\Rbar Amen.}
\vern{\Rbar Amen.}

\smallskip

% commented text from the Small Missal published in Sydney by E J Dwyer
% new text from the page scanned by Fr Rehak
\textit{Then is recited thrice---}
\latin{\Vbar Cor Jesu sacratíssimum.}
\vern{\Vbar Most Sacred Heart of Jesus.}
\latin{\Rbar Miserére nobis.}
\vern{\Rbar Have mercy on us.}
\end{Parallel}


