\section{Prayers after Low Mass}

\label{HailMary}

{\emph{To be said thrice---}\par}
\lettrine{H}{ail} Mary, full of grace, the Lord is with thee.  Blessed art thou among women and blessed is the fruit of thy womb, Jesus.

Holy Mary, Mother of God, pray for us, sinners, now and at the hour of our death.  Amen.

\smallskip

\label{HailHolyQueen}
\lettrine{H}{ail!} holy Queen, Mother of Mercy; hail, our life, our
sweetness, and our hope! To thee do we cry, poor
banished children of Eve; to thee do we send up our
sighs, mourning and weeping in this valley of tears. Turn,
then, most gracious advocate, thine eyes of mercy
towards us; and after this our exile, show unto us the
blessed fruit of thy womb, Jesus.

O clement, O loving, O sweet Virgin Mary.

\bigskip

\Vbar Pray for us O holy Mother of God

\Rbar That we may be made worthy of the promises of Christ.

\smallskip

Let us pray.

\lettrine{O}{ God,} our refuge and our strength, mercifully look
down on Thy people who cry to Thee; and through
the intercession of the glorious and Immaculate Virgin
Mary, Mother of God, of St.~Joseph her Spouse, of Thy
blessed Apostles Peter and Paul, and of all the Saints,
in mercy and goodness hear our prayers for the conversion 
of sinners, and for the liberty and exaltation of our
Holy Mother the Church. Through the same Christ our
Lord.

\Rbar Amen.

%\newpage
\smallskip

\lettrine{B}{lessed} Michael, Archangel, defend us in the hour of
conflict; be our safeguard against the wickedness
and snares of the devil---may God restrain him, we
humbly pray:---and do thou, O Prince of the heavenly
host, by the power of God thrust Satan down to hell,
and, with him, the other wicked spirits who wander
through the world for the ruin of souls.

\Rbar Amen.

\smallskip

\textit{Then is recited thrice---}

\Vbar Most Sacred Heart of Jesus.

\Rbar Have mercy on us.


