
\smallhead{8th December}

\atitle{Immaculate Conception}

\bibleref{Epistle}{Prov.~8: 22--35}

The Lord possessed me in the beginning of his ways, before he made any thing
from the beginning.   I was set up from eternity, and of old before the earth
was made.   The depths were not as yet, and I was already conceived. neither
had the fountains of waters as yet sprung out:   The mountains with their huge
bulk had not as yet been established: before the hills I was brought forth:  He
had not yet made the earth, nor the rivers, nor the poles of the world.  When
he prepared the heavens, I was present: when with a certain law and compass he
enclosed the depths:   When he established the sky above, and poised the
fountains of waters:  When he compassed the sea with its bounds, and set a law
to the waters that they should not pass their limits: when be balanced the
foundations of the earth;  I was with him forming all things: and was delighted
every day, playing before him at all times; Playing in the world: and my
delights were to be with the children of men.  Now therefore, ye children, hear
me: Blessed are they that keep my ways.  Hear instruction and be wise, and
refuse it not.   Blessed is the man that heareth me, and that watcheth daily at
my gates, and waiteth at the posts of my doors.   He that shall find me, shall
find life, and shall have salvation from the Lord.


\bibleref{Gospel}{Luke 1: 26--28}

At that time, the angel Gabriel was sent from God into a city of
Galilee, called Nazareth,  to a virgin espoused to a man whose name was Joseph,
of the house of David; and the virgin's name was Mary.  And the angel being
come in, said unto her: Hail, full of grace, the Lord is with thee: blessed art
thou among women. 



\bigskip

\smallhead{21st December}

\atitle{St.\ Thomas, Apostle}

\bibleref{Epistle}{Ephesians 2: 19--22}

\bibleref{Gospel}{John 20: 24--29}

\bigskip

\smallhead{26th December}

\atitle{St.\ Stephen, protomartyr}

\bibleref{Epistle}{Acts 6: 8--10; 7, 54--60}

\biblref{Gospel}{Matthew 23: 34--39}

\bigskip

\smallhead{27th December}

\atitle{St John, Apostle}

\bibleref{Epistle}{Ecclesiasticus 15: 1--6}

\bibleref{Gospel}{John 21: 19--24}

\bigskip

\smallhead{28th December}

\atitle{The Holy Innocents}

\bibleref{Epistle}{Apocalypse 14: 1--5}

\bibleref{Gospel}{Matthew 2: 13--18}

\bigskip


\smallhead{29th December}

\atitle{St.~Thomas of Canterbury}

\bibleref{Epistle}{Hebrews 5: 1--6}

\bibleref{Gospel}{John 10: 11--16}

\bigskip


\smallhead{13th January}


\atitle{The Baptism of Our Lord}

\bibleref{Epistle}{Isaias 60: 1--6}

\bibleref{Gospel}{John 1: 29--34}

\bigskip


\smallhead{2nd February}

\atitle{Purification}

\bibleref{Epistle}{Mal.~3: 1--4}

Thus saith the Lord God:
Behold I send my angel, and he shall prepare the way before my
face. And presently the Lord, whom you seek, and the angel of the
testament, whom you desire, shall come to his temple. Behold, he cometh,
saith the Lord of hosts.
\challnote{My angel... Viz., John the Baptist, the messenger of God, and forerunner
of Christ.}
And who shall be able to think of the day of his coming? and who
shall stand to see him? for he is like a refining fire, and like the
fuller's herb:
and he shall sit refining and cleansing the silver, and he shall
purify the sons of Levi, and shall refine them as gold, and as silver,
and they shall offer sacrifices to the Lord in justice.
And the sacrifice of Juda and of Jerusalem shall please the Lord,
as in the days of old, and in the ancient years:
saith the Lord almighty.

\columnbreak

\bibleref{Gospel}{Luke 2: 22--32}

At that time,
%And 
after the days of Mary's purification, according to the law of
Moses, were accomplished, they carried him to Jerusalem, to present him
to the Lord:
as it is written in the law of the Lord: Every male opening the
womb shall be called holy to the Lord:
and to offer a sacrifice, according as it is written in the law of
the Lord, a pair of turtledoves or two young pigeons.
And behold there was a man in Jerusalem named Simeon: and this man
was just and devout, waiting for the consolation of Israel. And the Holy
Ghost was in him.
And he had received an answer from the Holy Ghost, that he should
not see death before he had seen the Christ of the Lord.
And he came by the Spirit into the temple. And when his parents
brought in the child Jesus, to do for him according to the custom of the
law,
he also took him into his arms and blessed God and said:
Now thou dost dismiss thy servant, O Lord, according to thy word
in peace;
because my eyes have seen thy salvation,
which thou hast prepared before the face of all peoples:
A light to the revelation of the Gentiles and the glory of thy
people Israel.

%\bigskip

\smallhead{19th March}

\atitle{Saint Joseph}

\bibleref{Epistle}{Ecclus.~45: 1--6}

%Moses was 
Beloved of God, and men: whose memory is in benediction.  He made him
like the saints in glory, and magnified him in the fear of his enemies, and
with his words he made prodigies to cease.  He glorified him in the sight of
kings, and gave him commandments in the sight of his people, and shewed him his
glory.  He sanctified him in his faith, and meekness, and chose him out of all
flesh.  For he heard him, and his voice, and brought him into a cloud.  And he
gave him commandments before his face, and a law of life and instruction.
%, that
%he might teach Jacob his covenant, and Israel his judgments.


\bibleref{Gospel}{Matt.~1: 18--21}


%Now the generation of Christ was in this wise. 
When Mary the Mother of Jesus was
espoused to Joseph, before they came together, she was found with child, of the
Holy Ghost.  Whereupon Joseph her husband, being a just man, and not willing
publicly to expose her, was minded to put her away privately.  But while he
thought on these things, behold the Angel of the Lord appeared to him in his
sleep, saying: Joseph, son of David, fear not to take unto thee Mary thy wife,
for that which is conceived in her, is of the Holy Ghost.  And she shall bring
forth a son: and thou shalt call his name Jesus. For he shall save his people
from their sins.


\bigskip

\smallhead{25th March}

\atitle{Annunciation}

\bibleref{Epistle}{Is.~7: 10--15}

In those days the Lord spoke to Achaz, saying:
Ask thee a sign of the Lord thy God, either unto the depth of
hell, or unto the height above.
And Achaz said: I will not ask, and I will not tempt the Lord.
And he said: Hear ye therefore, O house of David: Is it a small
thing for you to be grievous to men, that you are grievous to my God
also?
Therefore the Lord himself shall give you a sign. Behold a virgin
shall conceive, and bear a son and his name shall be called Emmanuel.
He shall eat butter and honey, that he may know to refuse the
evil, and to choose the good.


\columnbreak

\bibleref{Gospel}{Luke 1: 26--38}

At that time the angel Gabriel was sent from God into a
city of Galilee, called Nazareth,
to a virgin espoused to a man whose name was Joseph, of the house
of David: and the virgin's name was Mary.
And the angel being come in, said unto her: Hail, full of grace,
the Lord is with thee: blessed art thou among women.
Who having heard, was troubled at his saying and thought with
herself what manner of salutation this should be.
And the angel said to her: Fear not, Mary, for thou hast found
grace with God.
Behold thou shalt conceive in thy womb and shalt bring forth a
son: and thou shalt call his name Jesus.
He shall be great and shall be called the Son of the Most High.
And the Lord God shall give unto him the throne of David his father: and
he shall reign in the house of Jacob for ever.
And of his kingdom there shall be no end.
And Mary said to the angel: How shall this be done, because I know
not man?
And the angel answering, said to her: The Holy Ghost shall come
upon thee and the power of the Most High shall overshadow thee. And
therefore also the Holy which shall be born of thee shall be called the
Son of God.
And behold thy cousin Elizabeth, she also hath conceived a son in
her old age: and this is the sixth month with her that is called barren.
Because no word shall be impossible with God.
And Mary said: Behold the handmaid of the Lord: be it done to me
according to thy word. %And the angel departed from her.


\bigskip

~

\bigskip

\columnbreak

\smallhead{1st May}

\atitle{St.~Joseph the Worker}

\bibleref{Epistle}{Col.~3: 14--15,17,23--24}

Brethren: have charity, which is the bond of
perfection,
and let the peace of Christ rejoice in your hearts, wherein also
you are called in one body: and be ye thankful.
%Let the word of Christ dwell in you abundantly: in all wisdom,
%teaching and admonishing one another in psalms, hymns and spiritual
%canticles, singing in grace in your hearts to God.
All whatsoever you do in word or in work, do all in the name of
the Lord Jesus Christ, giving thanks to God and the Father by him.
%Wives, be subject to your husbands, as it behoveth in the Lord.
%Husbands, love your wives and be not bitter towards them.
%Children, obey your parents in all things: for this is well
%pleasing to the Lord.
%Fathers, provoke not your children to indignation, lest they be
%discouraged.
%Servants, obey in all things your masters according to the flesh:
%not serving to the eye, as pleasing men: but in simplicity of heart,
%fearing God.
Whatsoever you do, do it from the heart, as to the Lord, and not
to men:
knowing that you shall receive of the Lord the reward of
inheritance. Serve ye the Lord Christ.



\bibleref{Gospel}{Matt.~13: 54--58}

And coming into his own country, he taught them in their
synagogues, so that they wondered and said: How came this man by this
wisdom and miracles?
Is not this the carpenter's son? Is not his mother called Mary,
and his brethren James, and Joseph, and Simon, and Jude:
%His brethren... These were the children of Mary the wife of Cleophas,
%sister to our Blessed Lady, (St. Matt. 27. 56; St.  John 19. 25,) and
%therefore, according to the usual style of the Scripture, they were
%called brethren, that is, near relations to our Saviour.
And his sisters, are they not all with us? Whence therefore hath
he all these things?
And they were scandalized in his regard. But Jesus said to them:
A prophet is not without honour, save in his own country, and in his own
house.
And he wrought not many miracles there, because of their
unbelief.




%\bigskip

\smallhead{24th June}

\atitle{Nativity of St.~John the Baptist}

\bibleref{Epistle}{Is.~49: 1--3,5,6,7}

Give ear, ye islands, and hearken, ye people from afar. The Lord
hath called me from the womb, from the bowels of my mother he hath been
mindful of my name.
And he hath made my mouth like a sharp sword: in the shadow of his
hand he hath protected me, and hath made me as a chosen arrow: in his
quiver he hath hidden me.
And he said to me: Thou art my servant Israel, for in thee will I
glory.
%And I said: I have laboured in vain, I have spent my strength
%without cause and in vain: therefore my judgment is with the Lord, and
%my work with my God.
And now saith the Lord, that formed me from the womb to be his
servant, %that I may bring back Jacob unto him, and Israel will not be
%gathered together: and I am glorified in the eyes of the Lord, and my
%God is made my strength.
%And he said: It is a small thing that thou shouldst be my servant
%to raise up the tribes of Jacob, and to convert the dregs of Israel.
Behold, I have given thee to be the light of the Gentiles, that thou
mayst be my salvation even to the farthest part of the earth.
%Thus saith the Lord the redeemer of Israel, his Holy One, to the
%soul that is despised, to the nation that is abhorred, to the servant of
%rulers: 
Kings shall see, and princes shall rise up, and adore for the
Lord's sake, because he is faithful, and for the Holy One of Israel, who
hath chosen thee.



\bibleref{Gospel}{Luke 1: 57--68}

Elizabeth's full time of being delivered was come: and she
brought forth a son.
And her neighbors and kinsfolks heard that the Lord had shewed his
great mercy towards her: and they congratulated with her.
And it came to pass that on the eighth day they came to circumcise
the child: and they called him by his father's name Zachary.
And his mother answering, said: Not so. But he shall be called
John.
And they said to her: There is none of thy kindred that is called
by this name.
And they made signs to his father, how he would have him called.
And demanding a writing table, he wrote, saying: John is his name.
And they all wondered.
And immediately his mouth was opened and his tongue loosed: and he
spoke, blessing God.
And fear came upon all their neighbours: and all these things were
noised abroad over all the hill country of Judea.
And all they that had heard them laid them up in their heart,
saying: What an one, think ye, shall this child be? For the hand of the
Lord was with him.
And Zachary his father was filled with the Holy Ghost. And he
prophesied, saying:
Blessed be the Lord God of Israel: because he hath visited and
wrought the redemption of his people.



%\bigskip


\smallhead{29th June}

\atitle{Saints Peter and Paul}

\bibleref{Epistle}{Acts 12: 1--11}

In those days, Herod the king stretched forth his hands, to
afflict some of the church.
And he killed James, the brother of John, with the sword.
And seeing that it pleased the Jews, he proceeded to take up Peter
also. Now it was in the days of the Azymes.
\challnote{Azymes\ldots\ The festival of the unleavened bread, or the pasch, which
answers to our Easter.}
And when he had apprehended him, he cast him into prison,
delivering him to four files of soldiers, to be kept, intending, after
the pasch, to bring him forth to the people.
Peter therefore was kept in prison. But prayer was made without
ceasing by the church unto God for him.
And when Herod would have brought him forth, the same night, Peter
was sleeping between two soldiers, bound with two chains: and the
keepers before the door kept the prison.
And behold an angel of the Lord stood by him and a light shined in
the room. And he, striking Peter on the side, raised him up, saying:
Arise quickly. And the chains fell off from his hands.
And the angel said to him: Gird thyself and put on thy sandals.
And he did so. And he said to him: Cast thy garment about thee and
follow me.
And going out, he followed him. And he knew not that it was true
which was done by the angel: but thought he saw a vision.
And passing through the first and the second ward, they came to
the iron gate that leadeth to the city which of itself opened to them.
And going out, they passed on through one street. And immediately the
angel departed from him.
And Peter coming to himself, said: Now I know in very deed that
the Lord hath sent his angel and hath delivered me out of the hand of
Herod and from all the expectation of the people of the Jews.

%\columnbreak

\bibleref{Gospel}{Matt.~16: 13--19}

At that time, Jesus came into the quarters of Cesarea Philippi: and he
asked his disciples, saying: Whom do men say that the Son of man is?
But they said: Some John the Baptist, and other some Elias, and
others Jeremias, or one of the prophets.
Jesus saith to them: But whom do you say that I am?
Simon Peter answered and said: Thou art Christ, the Son of the
living God.
And Jesus answering said to him: Blessed art thou, Simon
Bar-Jona: because flesh and blood hath not revealed it to thee, but my
Father who is in heaven.
And I say to thee: That thou art Peter; and upon this rock I will
build my church, and the gates of hell shall not prevail against it.
\challnote{Thou art Peter, etc\ldots\ As St. Peter, by divine revelation, here made a
solemn profession of his faith of the divinity of Christ; so in
recompense of this faith and profession, our Lord here declares to him
the dignity to which he is pleased to raise him: viz., that he to whom
he had already given the name of Peter, signifying a rock, St. John 1.
42, should be a rock indeed, of invincible strength, for the support of
the building of the church; in which building he should be, next to
Christ himself, the chief foundation stone, in quality of chief pastor,
ruler, and governor; and should have accordingly all fulness of
ecclesiastical power, signified by the keys of the kingdom of heaven.
Upon this rock, etc\ldots\ The words of Christ to Peter, spoken in the
vulgar language of the Jews which our Lord made use of, were the same as
if he had said in English, Thou art a Rock, and upon this rock I will
build my church. So that, by the plain course of the words, Peter is
here declared to be the rock, upon which the church was to be built:
Christ himself being both the principal foundation and founder of the
same.  Where also note, that Christ, by building his house, that is, his
church, upon a rock, has thereby secured it against all storms and
floods, like the wise builder, St. Matt. 7. 24, 25.  The gates of hell,
etc\ldots\ That is, the powers of darkness, and whatever Satan can do,
either by himself, or his agents. For as the church is here likened to a
house, or fortress, built on a rock; so the adverse powers are likened
to a contrary house or fortress, the gates of which, that is, the whole
strength, and all the efforts it can make, will never be able to prevail
over the city or church of Christ. By this promise we are fully assured,
that neither idolatry, heresy, nor any pernicious error whatsoever shall
at any time prevail over the church of Christ.}
And I will give to thee the keys of the kingdom of heaven.  And
whatsoever thou shalt bind upon earth, it shall be bound also in heaven:
and whatsoever thou shalt loose on earth, it shall be loosed also in
heaven.
\challnote{Loose on earth\ldots\ The loosing the bands of temporal punishments due to
sins, is called an indulgence; the power of which is here granted.}


%\columnbreak


%\bigskip

\smallhead{1st July}

\atitle{Precious Blood}

\bibleref{Epistle}{Heb.~9: 11--15}

Brethren: Christ, being come an high Priest of the good things to come,
by a greater and more perfect tabernacle, not made with hand, that is,
not of this creation:
Neither by the blood of goats or of calves, but by his own blood,
entered once into the Holies, having obtained eternal redemption.
%Eternal redemption... By that one sacrifice of his blood, once offered
%on the cross, Christ our Lord paid and exhibited, once for all, the
%general price and ransom of all mankind: which no other priest could do.
For if the blood of goats and of oxen, and the ashes of an heifer,
being sprinkled, sanctify such as are defiled, to the cleansing of the
flesh:
How much more shall the blood of Christ, who by the Holy Ghost
offered himself unspotted unto God, cleanse our conscience from dead
works, to serve the living God?
And therefore he is the mediator of the new testament: that by
means of his death for the redemption of those transgressions which were
under the former testament, they that are called may receive the promise
of eternal inheritance, in Christ Jesus our Lord.

\bigskip

\bibleref{Gospel}{John 19: 30--35}

At that time, Jesus, when he had taken the vinegar, said: It is
consummated. And bowing his head, he gave up the ghost.
Then the Jews (because it was the parasceve), that the bodies
might not remain upon the cross on the sabbath day (for that was a great
sabbath day), besought Pilate that their legs might be broken: and that
they might be taken away.
The soldiers therefore came: and they broke the legs of the
first, and of the other that was crucified with him.
But after they were come to Jesus, when they saw that he was
already dead, they did not break his legs.
But one of the soldiers with a spear opened his side: and
immediately there came out blood and water.
And he that saw it hath given testimony: and his testimony is
true. 

\bigskip

~

\columnbreak

\smallhead{6th August}

\atitle{Transfiguration}

\bibleref{Epistle}{2 Peter 1: 16--19}

Dearly beloved:
We have not followed artificial fables, when we made known to you
the power and presence of our Lord Jesus Christ: but we were
eyewitnesses of his greatness.
For he received from God the Father honour and glory, this voice
coming down to him from the excellent glory: This is my beloved Son, in
whom I am well pleased. Hear ye him.
And this voice, we heard brought from heaven, when we were with
him in the holy mount.
And we have the more firm prophetical word: whereunto you do well
to attend, as to a light that shineth in a dark place, until the day
dawn and the day star arise in your hearts.


\bibleref{Gospel}{Matt.~17: 1--9}

At that time Jesus took Peter and James, and John his brother,
and bringeth them up into a high mountain apart: And he was transfigured before
them. And his face did shine as the sun: and his garments became white as snow.
And behold there appeared to them Moses and Elias talking with him.  And Peter
answering, said to Jesus: Lord, it is good for us to be here: if thou wilt, let
us make here three tabernacles, one for thee, and one for Moses, and one for
Elias.  And as he was yet speaking, behold a bright cloud overshadowed them.
And lo a voice out of the cloud, saying: This is my beloved Son, in whom I am
well pleased: hear ye him.  And the disciples hearing fell upon their face, and
were very much afraid.  And Jesus came and touched them: and said to them:
Arise, and fear not.  And they lifting up their eyes, saw no one, but only
Jesus.  And as they came down from the mountain, Jesus charged them, saying:
Tell the vision to no man, till the Son of man be risen from the dead.

%\bigskip

\smallhead{15th August}

\atitle{Assumption of the Blessed Virgin}

\bibleref{Epistle}{Judith 13: 22--25,15: 10}%{Ecclus.~24: 11--13,15--20}


The Lord hath
blessed thee by his power, because by thee he hath brought our enemies
to nought.
%And Ozias the prince of the people of Israel, said to her:
Blessed art thou, O daughter, by the Lord the most high God, above all
women upon the earth.
Blessed be the Lord who made heaven and earth, who hath directed
thee to the cutting off the head of the prince of our enemies.
Because he hath so magnified thy name this day, that thy praise
shall not depart out of the mouth of men who shall be mindful of the
power of the Lord for ever, for that thou hast not spared thy life, by
reason of the distress and tribulation of thy people, but hast prevented
our ruin in the presence of our God.
Thou art the glory of Jerusalem, thou art the joy of
Israel, thou art the honour of our people:



\bibleref{Gospel}{Luke 1: 41--50}%{Luke 10: 38--42}

At that time, Elizabeth was filled with the
Holy Ghost.
And she cried out with a loud voice and said: Blessed art thou
among women and blessed is the fruit of thy womb.
And whence is this to me that the mother of my Lord should come to
me?
For behold as soon as the voice of thy salutation sounded in my
ears, the infant in my womb leaped for joy.
And blessed art thou that hast believed, because those things
shall be accomplished that were spoken to thee by the Lord.
And Mary said: My soul doth magnify the Lord.
And my spirit hath rejoiced in God my Saviour.
Because he hath regarded the humility of his handmaid: for behold
from henceforth all generations shall call me blessed.
\challnote{Shall call me blessed\ldots\ These words are a prediction of that honour
which the church in all ages should pay to the Blessed Virgin. Let
Protestants examine whether they are any way concerned in this prophecy.}
Because he that is mighty hath done great things to me: and holy
is his name.
And his mercy is from generation unto generations, to them that
fear him.


%\bigskip

\smallhead{14th September}

\atitle{Exaltation of the Holy Cross}


\bibleref{Epistle}{Phil.~2: 5-11}


Brethren, let this mind be in you, which was also in Christ Jesus: Who being in the
form of God, thought it not robbery to be equal with God: But emptied himself,
taking the form of a servant, being made in the likeness of men, and in habit
found as a man.
\challnote{Emptied himself, exinanivit\ldots\ made himself as of no account.}  He humbled
himself, becoming obedient unto death, even to the death of the cross.  For
which cause, God also hath exalted him and hath given him a name which is above
all names: That in the name of Jesus every knee should bow, of those that are
in heaven, on earth, and under the earth: And that every tongue should confess
that the Lord Jesus Christ is in the glory of God the Father.


\bibleref{Gospel}{John 12: 31--36}

At that time: Jesus said to the multitudes of the Jews:
Now is the judgment of the world: now shall the prince of this
world be cast out.
And I, if I be lifted up from the earth, will draw all things to
myself.
(Now this he said, signifying what death he should die.)
The multitude answered him: We have heard out of the law that
Christ abideth for ever. And how sayest thou: The Son of man must be
lifted up? Who is this Son of man?
Jesus therefore said to them: Yet a little while, the light is
among you. Walk whilst you have the light, and the darkness overtake you
not. And he that walketh in darkness knoweth not whither be goeth.
Whilst you have the light, believe in the light, that you may be
the children of light. %These things Jesus spoke: and he went away and
%hid himself from them.



%\bigskip

\smallhead{29th September}

\atitle{St.~Michael Archangel}

\bibleref{Epistle}{Apoc.~1: 1--5}


In those days: God signified the things which must shortly come to pass,
sending by his angel to his servant John,
%The things which must shortly come... and again it is said, ver. 3, The
%time is at hand... This can not be meant of all the things prophesied in
%the Apocalypse, where mention is made also of the day of judgment, and
%of the glory of heaven at the end of the world. That some things were to
%come to pass shortly, is evident, by what is said to the Seven Churches,
%chap. 2 and 3, Or that the persecutions foretold should begin shortly.
%Or that these words signified, that all time is short, and that from the
%coming of Christ, we are now in the last age or last hour. See 1 John
%2.18.
who hath given testimony to the word of God and the testimony of
Jesus Christ, what things soever he hath seen.
Blessed is he that readeth and heareth the words of this prophecy:
and keepeth those things which are written in it. For the time is at
hand.
John to the seven churches which are in Asia. Grace be unto you and
peace, from him that is and that was and that is to come: and from the
seven spirits which are before his throne:
And from Jesus Christ, who is the faithful witness, the first
begotten of the dead and the prince of the kings of the earth, who hath
loved us and washed us from our sins in his own blood,


\bibleref{Gospel}{Matt.~18: 1--10}

At that time the disciples came to Jesus, saying: Who, thinkest
thou, is the greater in the kingdom of heaven?
And Jesus, calling unto him a little child, set him in the midst
of them.
And said: amen I say to you, unless you be converted, and become
as little children, you shall not enter into the kingdom of heaven.
Whosoever therefore shall humble himself as this little child, he
is the greater in the kingdom of heaven.
And he that shall receive one such little child in my name,
receiveth me.
But he that shall scandalize one of these little ones that believe
in me, it were better for him that a millstone should be hanged about
his neck, and that he should be drowned in the depth of the sea.
%Shall scandalize... That is, shall put a stumblingblock in their way,
%and cause them to fall into sin.
Woe to the world because of scandals. For it must needs be that
scandals come: but nevertheless woe to that man by whom the scandal
cometh.
%It must needs be, etc... Viz., considering the wickedness and corruption
%of the world.
And if thy hand, or thy foot, scandalize thee, cut it off, and
cast it from thee. It is better for thee to go into life maimed or lame,
than having two hands or two feet, to be cast into everlasting fire.
%Scandalize thee... That is, cause thee to offend.
And if thy eye scandalize thee, pluck it out, and cast it from
thee. It is better for thee having one eye to enter into life, than
having two eyes to be cast into hell fire.
See that you despise not one of these little ones: for I say to
you, that their angels in heaven always see the face of my Father who is
in heaven.


%\bigskip

\smallhead{Last Sunday of October}

\atitle{Christ the King}

\bibleref{Epistle}{Col.~1: 12--20}

Brethren, giving thanks to God the Father, who hath made us worthy to be
partakers of the lot of the saints in light:
Who hath delivered us from the power of darkness and hath
translated us into the kingdom of the Son of his love,
in whom we have redemption through his blood, the remission of
sins:
Who is the image of the invisible God, the firstborn of every
creature:
\challnote{The firstborn\ldots\ That is, first begotten; as the Evangelist declares,
the only begotten of his Father: hence, St. Chrisostom explains
firstborn, not first created, as he was not created at all, but born of
his Father before all ages; that is, coeval with the Father and with the
Holy Ghost.}
For in him were all things created in heaven and on earth, visible
and invisible, whether thrones, or dominations, or principalities, or
powers. All things were created by him and in him.
And he is before all: and by him all things consist.
And he is the head of the body, the church: who is the beginning,
the firstborn from the dead, that in all things he may hold the primacy:
Because in him, it hath well pleased the Father that all fulness
should dwell:
And through him to reconcile all things unto himself, making peace
through the blood of his cross, both as to the things that are on earth
and the things that are in heaven, in Christ Jesus our Lord.

\bigskip

\bibleref{Gospel}{John 18: 33--37}

At that time, Pilate % therefore went into the hall again and called Jesus and
said to Jesus: Art thou the king of the Jews?
Jesus answered: Sayest thou this thing of thyself, or have others
told it thee of me?
Pilate answered: Am I a Jew? Thy own nation and the chief priests
have delivered thee up to me. What hast thou done?
Jesus answered: My kingdom is not of this world. If my kingdom
were of this world, my servants would certainly strive that I should not
be delivered to the Jews: but now my kingdom is not from hence.
Pilate therefore said to him: Art thou a king then? Jesus
answered: Thou sayest that I am a king. For this was I born, and for
this came I into the world; that I should give testimony to the truth.
Every one that is of the truth heareth my voice.


\bigskip

~

\columnbreak

\smallhead{1st November}

\atitle{All Saints}

\bibleref{Epistle}{Apoc.~7: 2--12}

In those days, behold, I, John, saw another angel ascending from the rising of the sun,
having the sign of the living God. And he cried with a loud voice to the
four angels to whom it was given to hurt the earth and the sea,
saying: Hurt not the earth nor the sea nor the trees, till we sign
the servants of our God in their foreheads.
And I heard the number of them that were signed. An hundred forty-
four thousand were signed, of every tribe of the children of Israel.
Of the tribe of Juda, twelve thousand signed: Of the tribe of
Ruben, twelve thousand signed: Of the tribe of Gad, twelve thousand
signed:
Of the tribe of Aser, twelve thousand signed: Of the tribe of
Nephthali, twelve thousand signed: Of the tribe of Manasses, twelve
thousand signed:
Of the tribe of Simeon, twelve thousand signed: Of the tribe of
Levi, twelve thousand signed: Of the tribe of Issachar, twelve thousand
signed:
Of the tribe of Zabulon, twelve thousand signed: Of the tribe of
Joseph, twelve thousand signed: Of the tribe of Benjamin, twelve
thousand signed.
After this, I saw a great multitude, which no man could number, of
all nations and tribes and peoples and tongues, standing before the
throne and in sight of the Lamb, clothed with white robes, and palms in
their hands.
And they cried with a loud voice, saying: Salvation to our God,
who sitteth upon the throne and to the Lamb.
And all the angels stood round about the throne and the ancients
and the four living creatures. And they fell down before the throne upon
their faces and adored God,
saying: Amen. Benediction and glory and wisdom and thanksgiving,
honour and power and strength, to our God, for ever and ever. Amen.


\bibleref{Gospel}{Matt.~5: 1--12}

At that time, Jesus, seeing the multitudes, went up into a mountain, and when he
was sat down, his disciples came unto him.
And opening his mouth he taught them, saying:
Blessed are the poor in spirit: for theirs is the kingdom of
heaven.
\challnote{The poor in spirit\ldots\ That is, the humble; and they whose spirit is not
set upon riches.}
Blessed are the meek: for they shall possess the land.
Blessed are they that mourn: for they shall be comforted.
Blessed are they that hunger and thirst after justice: for they
shall have their fill.
Blessed are the merciful: for they shall obtain mercy.
Blessed are the clean of heart: they shall see God.
Blessed are the peacemakers: for they shall be called the children
of God.
Blessed are they that suffer persecution for justice' sake: for
theirs is the kingdom of heaven.
Blessed are ye when they shall revile you, and persecute you, and
speak all that is evil against you, untruly, for my sake:
Be glad and rejoice for your reward is very great in heaven. For
so they persecuted the prophets that were before you.


%\bigskip

\smallhead{2nd November}

\atitle{All Souls}

\heading{First Mass}

\bibleref{Epistle}{1 Cor.~15: 51--57}

Brethren: Behold, I tell you a mystery. We shall all indeed rise again: but
we shall not all be changed.
In a moment, in the twinkling of an eye, at the last trumpet: for
the trumpet shall sound and the dead shall rise again incorruptible. And
we shall be changed.
For this corruptible must put on incorruption: and this mortal
must put on immortality.
And when this mortal hath put on immortality, then shall come to
pass the saying that is written: Death is swallowed up in victory.
O death, where is thy victory? O death, where is thy sting?
Now the sting of death is sin: and the power of sin is the law.
But thanks be to God, who hath given us the victory through our
Lord Jesus Christ.



\bibleref{Gospel}{John 5: 25--29}

At that time Jesus said to the multitudes of the Jews:
Amen, amen, I say unto you, that the hour cometh, and now is, when
the dead shall hear the voice of the Son of God: and they that hear
shall live.
For as the Father hath life in himself, so he hath given to the
Son also to have life in himself.
And he hath given him power to do judgment, because he is the Son
of man.
Wonder not at this: for the hour cometh wherein all that are in
the graves shall hear the voice of the Son of God.
And they that have done good things shall come forth unto the
resurrection of life: but they that have done evil, unto the
resurrection of judgment.


\heading{Second Mass}

\bibleref{Epistle}{2 Mac.~12: 43--46}

In those days: The most valiant man Judas, making a gathering, sent twelve thousand drachmas of silver
to Jerusalem for sacrifice to be offered for the sins of the dead,
thinking well and religiously concerning the resurrection.
(For if he had not hoped that they that were slain should rise
again, it would have seemed superfluous and vain to pray for the dead,)
And because he considered that they who had fallen asleep with
godliness, had great grace laid up for them.
%With godliness... Judas hoped that these men who died fighting for the
%cause of God and religion, might find mercy: either because they might
%be excused from mortal sin by ignorance; or might have repented of their
%sin, at least at their death.
It is therefore a holy and wholesome thought to pray for the
dead, that they may be loosed from sins.


\bibleref{Gospel}{John 6: 37--40}

At that time Jesus said to the multitudes of the Jews:
All that the Father giveth to me shall come to me: and him that
cometh to me, I will not cast out.
Because I came down from heaven, not to do my own will but the
will of him that sent me.
Now this is the will of the Father who sent me: that of all that
he hath given me, I should lose nothing; but should raise it up again in
the last day.
And this is the will of my Father that sent me: that every one who
seeth the Son and believeth in him may have life everlasting. And I will
raise him up in the last day.


\heading{Third Mass}

%\smallhead{Also Daily Mass for the Dead}

\bibleref{Epistle}{Apoc.~14: 13}


At that time Jesus said to the multitudes of the Jews:
And I heard a voice from heaven, saying to me: Write: Blessed are
the dead who die in the Lord. From henceforth now, saith the Spirit,
that they may rest from their labours. For their works follow them.



\bibleref{Gospel}{John 6: 51--55}

At that time Jesus said to the multitudes of the Jews:
I am the living bread which came down from heaven.
If any man eat of this bread, he shall live for ever: and the
bread that I will give is my flesh, for the life of the world.
The Jews therefore strove among themselves, saying: How can this
man give us his flesh to eat?
Then Jesus said to them: Amen, amen, I say unto you: except you
eat the flesh of the Son of man and drink his blood, you shall not have
life in you.
%Except you eat and drink, etc... To receive the body and blood of
%Christ, is a divine precept, insinuated in this text; which the faithful
%fulfil, though they receive but in one kind; because in one kind they
%receive both body and blood, which cannot be separated from each other.
%Hence, life eternal is here promised to the worthy receiving, though but
%in one kind.  Ver. 52. If any man eat of this bread, he shall live for
%ever; and the bread that I will give, is my flesh for the life of the
%world. Ver. 58. He that eateth me, the same also shall live by me. Ver.
%59. He that eateth this bread, shall liver for ever.
He that eateth my flesh and drinketh my blood hath everlasting
life: and I will raise him up in the last day.

%\bigskip

\smallhead{9th November}

\atitle{Dedication of St.~Saviour's}

\bibleref{Epistle}{Apoc.~21: 2--5}

In those days
I, John, saw the holy city, the new Jerusalem, coming down out
of heaven from God, prepared as a bride adorned for her husband.
And I heard a great voice from the throne, saying: Behold the
tabernacle of God with men: and he will dwell with them.  And they shall
be his people: and God himself with them shall be their God.
And God shall wipe away all tears from their eyes: and death shall
be no more. Nor mourning, nor crying, nor sorrow shall be any more, for
the former things are passed away.
And he that sat on the throne, said: Behold, I make all things
new. %And he said to me: Write. For these words are most faithful and
%true.


\bibleref{Gospel}{Luke 19: 1--10}

At that time Jesus,
entering in, walked through Jericho.
And behold, there was a man named Zacheus, who was the chief of
the publicans: and he was rich.
And he sought to see Jesus who he was: and he could not for the
crowd, because he was low of stature.
And running before, he climbed up into a sycamore tree, that he
might see him: for he was to pass that way.
And when Jesus was come to the place, looking up, he saw him and
said to him: Zacheus, make haste and come down: for this day I must
abide in thy house.
And he made haste and came down and received him with joy.
And when all saw it, they murmured, saying, that he was gone to be
a guest with a man that was a sinner.
But Zacheus standing, said to the Lord: Behold, Lord, the half of
my goods I give to the poor; and if I have wronged any man of any thing,
I restore him fourfold.
Jesus said to him: This day is salvation come to this house,
because he also is a son of Abraham.
For the Son of man is come to seek and to save that which was
lost.


%\bigskip



