\sectionmark{Advent}

\atitle{1st Sunday of Advent}

\bibleref{Epistle}{Rom.~13:11--14}

Brethren, knowing the season, that it is now the hour for us to
rise from sleep. For now our salvation is nearer than when we believed.
The night is passed and the day is at hand. Let us, therefore
cast off the works of darkness and put on the armour of light.
Let us walk honestly, as in the day: not in rioting and
drunkenness, not in chambering and impurities, not in contention and
envy.
But put ye on the Lord Jesus Christ: and make not provision for
the flesh in its concupiscences.

\medskip

\bibleref{Gospel}{Luke 21:25--33}

At that time Jesus said to his disciples: There shall be signs in the sun, and in the moon, and in the stars; and
upon the earth distress of nations, by reason of the confusion of the roaring
of the sea and of the waves;  Men withering away for fear, and expectation of
what shall come upon the whole world. For the powers of heaven shall be
moved;  And then they shall see the Son of man coming in a cloud, with great
power and majesty.  But when these things begin to come to pass, look up, and
lift up your heads, because your redemption is at hand.  And he spoke to them
in a similitude. See the fig tree, and all the trees:  When they now shoot
forth their fruit, you know that summer is nigh;  So you also, when you shall
see these things come to pass, know that the kingdom of God is at hand.  Amen,
I say to you, this generation shall not pass away, till all things be
fulfilled.  Heaven and earth shall pass away, but my words shall not pass away.


\bigskip

\atitle{2nd Sunday of Advent}

\bibleref{Epistle}{Rom.~15:4--13}

Brethren, for what things soever were written, were written for our learning: that
through patience and the comfort of the scriptures, we might have hope.  Now
the God of patience and of comfort grant you to be of one mind one towards
another, according to Jesus Christ:  That with one mind, and with one mouth,
you may glorify God and the Father of our Lord Jesus Christ.   Wherefore
receive one another, as Christ also hath received you unto the honour of God.  
For I say that Christ Jesus was minister of the circumcision\challnote{Minister
of the circumcision: That is, executed his office and ministry towards the
Jews, the people of the circumcision.} for the truth of God, to confirm the
promises made unto the fathers.  But that the Gentiles are to glorify God for
his mercy, as it is written: Therefore will I confess to thee, O Lord, among
the Gentiles, and will sing to thy name.  And again he saith: Rejoice, ye
Gentiles, with his people.   And again: Praise the Lord, all ye Gentiles; and
magnify him, all ye people. And again Isaias saith: There shall be a root of
Jesse; and he that shall rise up to rule the Gentiles, in him the Gentiles
shall hope.  Now the God of hope fill you with all joy and peace in believing;
that you may abound in hope, and in the power of the Holy Ghost. 

\medskip

\bibleref{Gospel}{Matt.~11:2--10}

At that time, when John had heard in prison the works of Christ: sending two of his
disciples he said to him:   Art thou he that art to come, or look we for
another?   And Jesus making answer said to them: Go and relate to John what you
have heard and seen.   The blind see, the lame walk, the lepers are cleansed,
the deaf hear, the dead rise again, the poor have the gospel preached to them.
 And blessed is he that shall not be scandalized in me.\challnote{Scandalized
in me: That is, who shall not take occasion of scandal or offence from my
humility, and the disgraceful death of the cross which I shall endure.}  And
when they went their way, Jesus began to say to the multitudes concerning John:
What went you out into the desert to see? a reed shaken with the wind?   But
what went you out to see? a man clothed in soft garments?  Behold they that are
clothed in soft garments, are in the houses of kings.   But what went you out
to see? a prophet? yea I tell you, and more than a prophet.   For this is he of
whom it is written: Behold I send my angel before thy face, who shall prepare
thy way before thee.

\bigskip

%\columnbreak

\atitle{3rd Sunday of Advent}

\bibleref{Epistle}{Phil.~4:4--7}

Brethren, rejoice in the Lord always; again, I say, rejoice.  Let your modesty be known
to all men. The Lord is nigh.   Be nothing solicitous; but in every thing, by
prayer and supplication, with thanksgiving, let your petitions be made known to
God.  And the peace of God, which surpasseth all understanding, keep your
hearts and minds in Christ Jesus.

%\columnbreak
\medskip

\bibleref{Gospel}{John 1:19--28}

At that time, % And this is the testimony of John, 
the Jews sent from Jerusalem priests
and Levites to John, to ask him: Who art thou?  And he confessed, and did not
deny: and he confessed: I am not the Christ.   And they asked him: What then?
Art thou Elias? And he said: I am not. Art thou the prophet? And he answered:
No.  They said therefore unto him: Who art thou, that we may give an answer to
them that sent us? What sayest thou of thyself?  He said: I am the voice of one
crying out in the wilderness, make straight the way of the Lord, as said the
prophet Isaias.  And they that were sent, were of the Pharisees.  And they
asked him, and said to him: Why then dost thou baptize, if thou be not Christ,
nor Elias, nor the prophet?   John answered them, saying: I baptize with water;
but there hath stood one in the midst of you, whom you know not.  The same is
he that shall come after me, who is preferred before me: the latchet of whose
shoe I am not worthy to loose.  These things were done in Bethania, beyond the
Jordan, where John was baptizing. 

\bigskip

%\columnbreak

\atitle{4th Sunday of Advent}

\bibleref{Epistle}{1 Cor.~4:1--5}

Brethren, let a man so account of us as of the ministers of Christ, and the dispensers of
the mysteries of God.  Here now it is required among the dispensers, that a man
be found faithful.  But to me it is a very small thing to be judged by you, or
by man's day; but neither do I judge my own self.  For I am not conscious to
myself of any thing, yet am I not hereby justified; but he that judgeth me, is
the Lord.  Therefore judge not before the time; until the Lord come, who both
will bring to light the hidden things of darkness, and will make manifest the
counsels of the hearts; and then shall every man have praise from God.

\medskip

\bibleref{Gospel}{Luke 3:1--6}

Now in the fifteenth year of the reign of Tiberius Caesar, Pontius Pilate being
governor of Judea, and Herod being tetrarch of Galilee, and Philip his brother
tetrarch of Iturea, and the country of Trachonitis, and Lysanias tetrarch of
Abilina; Under the high priests Annas and Caiphas; the word of the Lord was
made unto John, the son of Zachary, in the desert.  And he came into all the
country about the Jordan, preaching the baptism of penance for the remission of
sins; As it was written in the book of the sayings of Isaias the prophet: A
voice of one crying in the wilderness: Prepare ye the way of the Lord, make
straight his paths. Every valley shall be filled; and every mountain and hill
shall be brought low; and the crooked shall be made straight; and the rough
ways plain;  And all flesh shall see the salvation of God.

%\columnbreak

\bigskip

\sectionmark{Christmas}

%\atitle{Christmas (1st Mass)}

%\heading{}
\atitle{Christmas}
\heading{\textbf{First Mass:} At Midnight}

\bibleref{Epistle}{Titus 2:11--15}

Dearly-beloved: The grace of God our Saviour hath appeared to all men: Instructing us,
that, denying ungodliness and worldly desires, we should live soberly and
justly and godly in this world, looking for the blessed hope and coming of the
glory of the great God and our Saviour Jesus Christ.  Who gave himself for us,
that he might redeem us from all iniquity and might cleanse to himself a people
acceptable, a pursuer of good works.  These things speak and exhort: in Christ Jesus our Lord.
% and rebuke
%with all authority.  Let no man despise thee.

\medskip

\bibleref{Gospel}{Luke 2:1--14}

At that time, there went out a decree from Caesar
Augustus that the whole world should be enrolled.  This enrolling was first
made by Cyrinus, the governor of Syria.  And all went to be enrolled, every one
into his own city.  And Joseph also went up from Galilee, out of the city of
Nazareth, into Judea, to the city of David, which is called Bethlehem: because
he was of the house and family of David.  To be enrolled with Mary his espoused
wife, who was with child.  And it came to pass that when they were there, her
days were accomplished that she should be delivered.  And she brought forth her
first born\challnote{Her firstborn\ldots\ The meaning is, not that she had
afterward any other child; but it is a way of speech among the Hebrews, to call
them also the firstborn, who are the only children. See annotation Matt.~1:25.}
son and wrapped him up in swaddling clothes and laid him in a manger: because
there was no room for them in the inn.  And there were in the same country
shepherds watching and keeping the night watches over their flock.  And behold
an angel of the Lord stood by them and the brightness of God shone round about
them: and they feared with a great fear.  And the angel said to them: Fear not;
for, behold, I bring you good tidings of great joy that shall be to all the
people: For, this day is born to you a Saviour, who is Christ the Lord, in the
city of David.  And this shall be a sign unto you. You shall find the infant
wrapped in swaddling clothes and laid in a manger.  And suddenly there was with
the angel a multitude of the heavenly army, praising God and saying: Glory to
God in the highest: and on earth peace to men of good will.

\bigskip

%\atitle{Christmas (2nd Mass)}
%\atitle[Christmas (2nd Mass)]{Christmas\break(2nd Mass)}

%\heading{}
%\atitle{Christmas}
\heading{\textbf{Second Mass:} At Dawn}

\bibleref{Epistle}{Titus 3:4--7}

Dearly-beloved: the goodness and kindness of God our Saviour appeared: Not by the
works of justice which we have done, but according to his mercy, he saved us,
by the laver of regeneration and renovation of the Holy Ghost.  Whom he hath
poured forth upon us abundantly, through Jesus Christ our Saviour: That, being
justified by his grace, we may be heirs according to hope of life everlasting.


\bibleref{Gospel}{Luke 2:15--20}

At that time, the
shepherds said one to another: Let us go over to Bethlehem and let us see this
word that is come to pass, which the Lord hath shewed to us.  And they came
with haste: and they found Mary and Joseph, and the infant lying in the manger.
And seeing, they understood of the word that had been spoken to them concerning
this child.  And all that heard wondered: and at those things that were told
them by the shepherds.  But Mary kept all these words, pondering them in her
heart.  And the shepherds returned, glorifying and praising God for all the
things they had heard and seen, as it was told unto them.


%\atitle{Christmas}

%\heading{}
%\columnbreak

\heading{\textbf{Third Mass:}\break During the Day}

\bibleref{Epistle}{Heb.~1:1--12}

God, who, at sundry times and in divers manners, spoke in times past to the
fathers by the prophets, last of all, in these days, hath spoken to us by his
Son, whom he hath appointed heir of all things, by whom also he made the world.
Who being the brightness of his glory and the figure\challnote{The
figure\ldots\  that is, the express image, and most perfect resemblance.} of
his substance and upholding all things by the word of his power, making
purgation\challnote{Making purgation\ldots\  That is, having purged away our
sins by his passion.} of sins, sitteth on the right hand of the majesty on
high: Being made so much better than the angels as he hath inherited a more
excellent name than they.  For to which of the angels hath he said at any time:
Thou art my Son, to-day have I begotten thee? And again: I will be to him a
Father, and he shall be to me a Son?  And again, when he bringeth in the first
begotten into the world, he saith: And let all the angels of God adore him.
And to the angels indeed he saith: He that maketh his angels spirits and his
ministers a flame of fire.  But to the Son: Thy throne, O God, is for ever and
ever: a sceptre of justice is the sceptre of thy kingdom.  Thou hast loved
justice and hated iniquity: therefore God, thy God, hath anointed thee with the
oil of gladness above thy fellows.  And: Thou in the beginning, O Lord, didst
found the earth: and the works of thy hands are the heavens.  They shall
perish: but thou shalt continue: and they shall all grow old as a garment.  And
as a vesture shalt thou change them, and they shalt be changed. But thou art
the selfsame: and thy years shall not fail.  But to which of the angels said he
at any time: Sit on my right hand, until I make thy enemies thy footstool?

%\columnbreak

\bibleref{Gospel}{John 1:1--14}

In the beginning was the Word: and the Word was with God: and the Word was God.
The same was in the beginning with God.  All things were made by him: and
without him was made nothing that was made.  In him was life: and the life was
the light of men.  And the light shineth in darkness: and the darkness did not
comprehend it.  There was a man sent from God, whose name was John.  This man
came for a witness, to give testimony of the light, that all men might believe
through him.  He was not the light, but was to give testimony of the light.
That was the true light, which enlighteneth every man that cometh into this
world.  He was in the world: and the world was made by him: and the world knew
him not.  He came unto his own: and his own received him not.  But as many as
received him, he gave them power to be made the sons of God, to them that
believe in his name.  Who are born, not of blood, nor of the will of the flesh,
nor of the will of man, but of God.  And the Word was made flesh and dwelt
among us (and we saw his glory, the glory as it were of the only begotten of
the Father), full of grace and truth.



%\bigskip

\atitle{Sunday within the Octave of Christmas}

\bibleref{Epistle}{Gal.~4:1--7}

Brethren, as long as the heir is a child, he differeth nothing from a servant, though he
be lord of all, but is under tutors and governors until the time appointed by
the father.  So we also, when we were children, were serving under the elements
of the world.  \challnote{Under the elements, etc\ldots\  That is, under the
first rudiments of religion, in which the carnal Jews were trained up; or under
those corporeal creatures, used in their manifold rites, sacrifices, and
sacraments.} But when the fulness of the time was come, God sent his Son, made
of a woman, made under the law: That he might redeem them who were under the
law: that we might receive the adoption of sons.  And because you are sons, God
hath sent the Spirit of his Son into your hearts, crying: Abba, Father.
Therefore, now he is not a servant, but a son. And if a son, an heir also
through God.


\bibleref{Gospel}{Luke 2:33--40}

At that time, Joseph and Mary the Mother of Jesus were wondering at those things which were spoken
concerning him.  And Simeon blessed them and said to Mary his mother: Behold
this child is set for the fall and for the resurrection of many in Israel and
for a sign which shall be contradicted.  \challnote{For the fall, etc\ldots\
Christ came for the salvation of all men; but here Simeon prophesies what would
come to pass, that many through their own wilful blindness and obstinacy would
not believe in Christ, nor receive his doctrine, which therefore would be ruin
to them: but to others a resurrection, by their believing in him, and obeying
his commandments.} And thy own soul a sword shall pierce, that, out of many
hearts thoughts may be revealed.  And there was one Anna, a prophetess, the
daughter of Phanuel, of the tribe of Aser. She was far advanced in years and
had lived with her husband seven years from her virginity.  And she was a widow
until fourscore and four years: who departed not from the temple, by fastings
and prayers serving night and day.  Now she, at the same hour, coming in,
confessed to the Lord: and spoke of him to all that looked for the redemption
of Israel.  And after they had performed all things according to the law of the
Lord, they returned into Galilee, to their city Nazareth.  And the child grew
and waxed strong, full of wisdom: and the grace of God was in him.



%\bigskip
\columnbreak

\smallhead{1st January}

\atitle{Octave-day of the Nativity}

\bibleref{Epistle}{Titus 2:11--15}

Dearly-beloved: The grace of God our Saviour hath appeared to all men: Instructing us,
that, denying ungodliness and worldly desires, we should live soberly and
justly and godly in this world, looking for the blessed hope and coming of the
glory of the great God and our Saviour Jesus Christ.  Who gave himself for us,
that he might redeem us from all iniquity and might cleanse to himself a people
acceptable, a pursuer of good works.  These things speak and exhort: in Christ Jesus our Lord.


\bibleref{Gospel}{Luke 2.:21} 

At that time, after eight days were accomplished, that the
child should be circumcised, his name was called \textsc{Jesus}, which was
called by the angel before he was conceived in the womb.



%\bigskip

\smallhead{Sunday after the Octave \break or 2nd January}

\atitle{The Holy Name}

\bibleref{Epistle}{Acts 4:8--12}

In those days Peter, filled with the Holy Ghost, said to them: Ye princes of the people
and ancients, hear.  If we this day are examined concerning the good deed done
to the infirm man, by what means he hath been made whole: Be it known to you
all and to all the people of Israel, that by the name of our Lord Jesus Christ
of Nazareth, whom you crucified, whom God hath raised from the dead, even by
him, this man standeth here before you, whole.  This is the stone which was
rejected by you the builders, which is become the head of the corner.  Neither
is there salvation in any other. For there is no other name under heaven given
to men, whereby we must be saved.


\bibleref{Gospel}{Luke 2:21}

At that time, after eight days were accomplished, that the child should be circumcised,
his name was called \textsc{Jesus}, which was called by the angel before he was
conceived in the womb.

%\bigskip

\smallhead{6th January}

\sectionmark{Epiphany}

\atitle{Epiphany}

\bibleref{Epistle}{Is.~60:1--6}

Arise, be enlightened, O Jerusalem: for thy light is come, and the glory of the
Lord is risen upon thee.  For behold darkness shall cover the earth, and a mist
the people: but the Lord shall arise upon thee, and his glory shall be seen
upon thee.  And the Gentiles shall walk in thy light, and kings in the
brightness of thy rising.  Lift up thy eyes round about, and see: all these are
gathered together, they are come to thee: thy sons shall come from afar, and
thy daughters shall rise up at thy side.  Then shalt thou see, and abound, and
thy heart shall wonder and be enlarged, when the multitude of the sea shall be
converted to thee, the strength of the Gentiles shall come to thee.  The
multitude of camels shall cover thee, the dromedaries of Madian and Epha: all
they from Saba shall come, bringing gold and frankincense: and shewing forth
praise to the Lord.


\bibleref{Gospel}{Matt.~2:1--12}

When Jesus was born in Bethlehem of Juda, in the days of king Herod,
behold, there came wise men from the East to Jerusalem, saying: Where is he
that is born king of the Jews? For we have seen his star in the East, and are
come to adore him.  And king Herod hearing this, was troubled, and all
Jerusalem with him.  And assembling together all the chief priests and the
scribes of the people, he inquired of them where Christ should be born.  But
they said to him: In Bethlehem of Juda. For so it is written by the prophet:
And thou Bethlehem the land of Juda art not the least among the princes of
Juda: for out of thee shall come forth the captain that shall rule my people
Israel.  Then Herod, privately calling the wise men learned diligently of them
the time of the star which appeared to them; And sending them into Bethlehem,
said: Go and diligently inquire after the child, and when you have found him,
bring me word again, that I also may come and adore him.  Who having heard the
king, went their way; and behold the star which they had seen in the East, went
before them, until it came and stood over where the child was.  And seeing the
star they rejoiced with exceeding great joy.  And entering into the house, they
found the child with Mary his mother, and falling down they adored him: and
opening their treasures, they offered him gifts; gold, frankincense, and myrrh.
And having received an answer in sleep that they should not return to Herod,
they went back another way into their country.


%\bigskip

\atitle{The Holy Family}

\bibleref{Epistle}{Col.~3:12--17}

Brethren, put ye on therefore, as the elect of God, holy and beloved, the bowels of
mercy, benignity, humility, modesty, patience: Bearing with one another and
forgiving one another, if any have a complaint against another. Even as the
Lord hath forgiven you, so do you also.  But above all these things have
charity, which is the bond of perfection.  And let the peace of Christ rejoice
in your hearts, wherein also you are called in one body: and be ye thankful.
Let the word of Christ dwell in you abundantly: in all wisdom, teaching and
admonishing one another in psalms, hymns and spiritual canticles, singing in
grace in your hearts to God.  All whatsoever you do in word or in work, do all
in the name of the Lord Jesus Christ, giving thanks to God and the Father by
him.


\bibleref{Gospel}{Luke 2:42--52}

When Jesus was twelve years old, they going up into Jerusalem, according to
the custom of the feast, and having fulfilled the days, when they returned, the
child Jesus remained in Jerusalem. And his parents knew it not.  And thinking
that he was in the company, they came a day's journey and sought him among
their kinsfolks and acquaintance.  And not finding him, they returned into
Jerusalem, seeking him.  And it came to pass, that, after three days, they
found him in the temple, sitting in the midst of the doctors, hearing them and
asking them questions.  And all that heard him were astonished at his wisdom
and his answers.  And seeing him, they wondered. And his mother said to him:
Son, why hast thou done so to us? Behold thy father and I have sought thee
sorrowing.  And he said to them: How is it that you sought me? Did you not know
that I must be about my father's business?  And they understood not the word
that he spoke unto them.  And he went down with them and came to Nazareth and
was subject to them. And his mother kept all these words in her heart.  And
Jesus advanced in wisdom and age and grace with God and men.



%\bigskip

\atitle{2nd Sunday\break after Epiphany}

\bibleref{Epistle}{Rom.~12:6--16}

Brethren, having different gifts, according to the grace that is given us, either
prophecy, to be used according to the rule of faith; or ministry, in
ministering; or he that teacheth, in doctrine; he that exhorteth, in exhorting;
he that giveth, with simplicity; he that ruleth, with carefulness; he that
sheweth mercy, with cheerfulness.  Let love be without dissimulation. Hating
that which is evil, cleaving to that which is good, loving one another with the
charity of brotherhood: with honour preventing one another.  In carefulness not
slothful. In spirit fervent. Serving the Lord.  Rejoicing in hope. Patient in
tribulation. Instant in prayer.  Communicating to the necessities of the
saints. Pursuing hospitality.  Bless them that persecute you: bless, and curse
not.  Rejoice with them that rejoice: weep with them that weep.  Being of one
mind one towards another. Not minding high things, but consenting to the
humble.% Be not wise in your own conceits.


\bibleref{Gospel}{John 2:1--11}

At that time, there was a marriage in Cana of Galilee: and the mother of
Jesus was there.  And Jesus also was invited, and his disciples, to the
marriage.  And the wine failing, the mother of Jesus saith to him: They have no
wine.  And Jesus saith to her: Woman, what is that to me and to thee? My hour
is not yet come.  \challnote{What is that to me, etc\ldots\  These words of our
Saviour, spoken to his mother, have been understood by some commentators as
harsh, they not considering the next following verse: Whatsoever he shall say
to you, do ye, which plainly shows that his mother knew of the miracle that he
was to perform, and that it was at her request he wrought it; besides the
manner of speaking the words as to the tone, and the countenance shown at the
same time, which could only be known to those who were present, or from what
had followed: for words indicating anger in one tone of voice, would be
understood quite the reverse in another.} His mother saith to the waiters:
Whatsoever he shall say to you, do ye.  Now there were set there six waterpots
of stone, according to the manner of the purifying of the Jews, containing two
or three measures apiece.  Jesus saith to them: Fill the waterpots with water.
And they filled them up to the brim.  And Jesus saith to them: Draw out now and
carry to the chief steward of the feast. And they carried it.  And when the
chief steward had tasted the water made wine and knew not whence it was, but
the waiters knew who had drawn the water: the chief steward calleth the
bridegroom, and saith to him: Every man at first setteth forth good wine, and
when men have well drunk, then that which is worse.  But thou hast kept the
good wine until now.  This beginning of miracles did Jesus in Cana of Galilee
and manifested his glory. And his disciples believed in him.



%\bigskip

\atitle{3rd Sunday \break after Epiphany}

\bibleref{Epistle}{Rom.~12:16--21}

Brethren, %Being of one mind one towards another. Not minding high things, but consenting
%to the humble. 
be not wise in your own conceits.  To no man rendering evil for
evil. Providing good things, not only in the sight of God but also in the sight
of all men.  If it be possible, as much as is in you, have peace with all men.
Revenge not yourselves, my dearly beloved; but give place unto wrath, for it is
written: Revenge is mine, I will repay, saith the Lord.  But if the enemy be
hungry, give him to eat; if he thirst, give him to drink. For, doing this, thou
shalt heap coals of fire upon his head.  Be not overcome by evil: but overcome
evil by good.



\bibleref{Gospel}{Matt.~8:1--13}

At that time, when Jesus was come down from the mountain, great multitudes followed him: And
behold a leper came and adored him, saying: Lord, if thou wilt, thou canst make
me clean.  And Jesus stretching forth his hand, touched him, saying: I will, be
thou made clean. And forthwith his leprosy was cleansed.  And Jesus saith to
him: See thou tell no man: but go, shew thyself to the priest, and offer the
gift which Moses commanded, for a testimony unto them.  

And when he had entered
into Capharnaum, there came to him a centurion, beseeching him, and saying,
Lord, my servant lieth at home sick of the palsy, and is grievously tormented.
And Jesus saith to him: I will come and heal him.  And the centurion, making
answer, said: Lord, I am not worthy that thou shouldst enter under my roof; but
only say the word, and my servant shall be healed.  For I also am a man subject
to authority, having under me soldiers; and I say to this, Go, and he goeth,
and to another, Come, and he cometh, and to my servant, Do this, and he doeth
it.  And Jesus hearing this, marvelled; and said to them that followed him.
Amen I say to you, I have not found so great faith in Israel.  And I say to you
that many shall come from the east and the west, and shall sit down with
Abraham, and Isaac and Jacob in the kingdom of heaven: But the children of the
kingdom shall be cast out into the exterior darkness: there shall be weeping
and gnashing of teeth.  And Jesus said to the centurion: Go, and as thou hast
believed, so be it done to thee. And the servant was healed at the same hour.


\bigskip

%\columnbreak

\atitle{4th Sunday \break after Epiphany}

\bibleref{Epistle}{Rom.~13:8--10}

Brethren, owe no man any thing, but to love one another. For he that loveth his neighbour
hath fulfilled the law.  For: Thou shalt not commit adultery: Thou shalt not
kill: Thou shalt not steal: Thou shalt not bear false witness: Thou shalt not
covet. And if there be any other commandment, it is comprised in this word:
Thou shalt love thy neighbour as thyself.  The love of our neighbour worketh no
evil. Love therefore is the fulfilling of the law.

%\medskip

\bibleref{Gospel}{Matt.~8:23--27}

At that time, when Jesus entered into the boat, his disciples followed him: And behold a
great tempest arose in the sea, so that the boat was covered with waves, but he
was asleep.  And they came to him, and awaked him, saying: Lord, save us, we
perish.  And Jesus saith to them: Why are you fearful, O ye of little faith?
Then rising up, he commanded the winds, and the sea, and there came a great
calm.  But the men wondered, saying: What manner of man is this, for the winds
and the sea obey him?


%\bigskip

\atitle{5th Sunday \break after Epiphany}

\bibleref{Epistle}{Col.~3:12--17}

Brethren, put ye on therefore, as the elect of God, holy and beloved, the bowels of
mercy, benignity, humility, modesty, patience: Bearing with one another and
forgiving one another, if any have a complaint against another. Even as the
Lord hath forgiven you, so do you also.  But above all these things have
charity, which is the bond of perfection.  And let the peace of Christ rejoice
in your hearts, wherein also you are called in one body: and be ye thankful.
Let the word of Christ dwell in you abundantly: in all wisdom, teaching and
admonishing one another in psalms, hymns and spiritual canticles, singing in
grace in your hearts to God.  All whatsoever you do in word or in work, do all
in the name of the Lord Jesus Christ, giving thanks to God and the Father by
him.

%\medskip

\bibleref{Gospel}{Matt.~13:24--30}

At that time, Jesus spoke this parable to the multitudes: The kingdom of heaven is likened
to a man that sowed good seed in his field.  But while men were asleep, his
enemy came and oversowed cockle among the wheat and went his way.  And when the
blade was sprung up, and had brought forth fruit, then appeared also the
cockle.  And the servants of the good man of the house coming said to him.
Sir, didst thou not sow good seed in thy field? Whence then hath it cockle?
And he said to them: An enemy hath done this. And the servants said to him:
Wilt thou that we go and gather it up?  And he said: No, lest perhaps gathering
up the cockle, you root up the wheat also together with it.  Suffer both to
grow until the harvest, and in the time of the harvest I will say to the
reapers: Gather up first the cockle, and bind it into bundles to burn, but the
wheat gather ye into my barn.

%\bigskip

%\columnbreak

\atitle{6th Sunday \break after Epiphany}

\bibleref{Epistle}{1 Thess.~1:2--10}

%Grace be to you and peace. 
Brethren, we give thanks to God always for you all: making a
remembrance of you in our prayers without ceasing, being mindful of the work of
your faith and labour and charity: and of the enduring of the hope of our Lord
Jesus Christ before God and our Father.  Knowing, brethren, beloved of God,
your election: For our gospel hath not been unto you in word only, but in power
also: and in the Holy Ghost and in much fulness, as you know what manner of men
we have been among you for your sakes.  And you became followers of us and of
the Lord: receiving the word in much tribulation, with joy of the Holy Ghost:
So that you were made a pattern to all that believe in Macedonia and in Achaia.
For from you was spread abroad the word of the Lord not only in Macedonia and
in Achaia but also in every place: your faith which is towards God, is gone
forth, so that we need not to speak any thing.  For they themselves relate of
us, what manner of entering in we had unto you: and how you turned to God from
idols to serve the living and true God.  And to wait for his Son from heaven
(whom he raised up from the dead), Jesus, who hath delivered us from the wrath
to come.


\bibleref{Gospel}{Matt.~13:31--35}

At that time, Jesus spoke to the multitudes this parable: % Another parable he proposed unto them, saying: 
The kingdom of heaven is like to
a grain of mustard seed, which a man took and sowed in his field.  Which is the
least indeed of all seeds; but when it is grown up, it is greater than all
herbs, and becometh a tree, so that the birds of the air come, and dwell in the
branches thereof.  Another parable he spoke to them: The kingdom of heaven is
like to leaven, which a woman took and hid in three measures of meal, until the
whole was leavened.  All these things Jesus spoke in parables to the
multitudes: and without parables he did not speak to them.  That it might be
fulfilled which was spoken by the prophet, saying: I will open my mouth in
parables, I will utter things hidden from the foundation of the world.

\sectionmark{Septuagesima}

\atitle{Septuagesima Sunday}

\bibleref{Epistle}{1 Cor.~9:24--10:5}

Brethren, know you not that they that run in the race, all run indeed, but one receiveth
the prize. So run that you may obtain.  And every one that striveth for the
mastery refraineth himself from all things. And they indeed that they may
receive a corruptible crown: but we an incorruptible one.  I therefore so run,
not as at an uncertainty: I so fight, not as one beating the air.  But I
chastise my body and bring it into subjection: lest perhaps, when I have
preached to others, I myself should become a castaway.  \challnote{I chastise,
etc\ldots\ Here St. Paul shews the necessity of self-denial and mortification,
to subdue the flesh, and its inordinate desires.} For I would not have you
ignorant, brethren, that our fathers were all under the cloud: and all passed
through the sea.  And all in Moses were baptized, in the cloud and in the sea:
\challnote{In Moses\ldots\ Under the conduct of Moses, they received baptism in
figure, by passing under the cloud, and through the sea; and they partook of
the body and blood of Christ in figure, by eating of the manna, (called here a
spiritual food because it was a figure of the true bread which comes down from
heaven,) and drinking the water, miraculously brought out of the rock, called
here a spiritual rock, because it was also a figure of Christ.} And did all eat
the same spiritual food: And all drank the same spiritual drink: (And they
drank of the spiritual rock that followed them: and the rock was Christ.) But
with most of them God was not well pleased: for they were overthrown in the
desert.

%\columnbreak

\bibleref{Gospel}{Matt.~20:1--16}

At that time Jesus spoke to his disciples this parable:
The kingdom of heaven is like to an householder, who went out early in the
morning to hire labourers into his vineyard.  And having agreed with the
labourers for a penny a day, he sent them into his vineyard.  And going out
about the third hour, he saw others standing in the marketplace idle.  And he
said to them: Go you also into my vineyard, and I will give you what shall be
just.  And they went their way. And again he went out about the sixth and the
ninth hour, and did in like manner.  But about the eleventh hour he went out
and found others standing, and he saith to them: Why stand you here all the day
idle?  They say to him: Because no man hath hired us. He saith to them: Go ye
also into my vineyard.  And when evening was come, the lord of the vineyard
saith to his steward: Call the labourers and pay them their hire, beginning
from the last even to the first.  When therefore they were come that came about
the eleventh hour, they received every man a penny.  But when the first also
came, they thought that they should receive more: And they also received every
man a penny.  And receiving it they murmured against the master of the house,
saying: These last have worked but one hour and thou hast made them equal to
us, that have borne the burden of the day and the heats.  But he answering said
to one of them: friend, I do thee no wrong: didst thou not agree with me for a
penny?  Take what is thine, and go thy way: I will also give to this last even
as to thee.  Or, is it not lawful for me to do what I will? Is thy eye evil,
because I am good?  \challnote{What I will\ldots\ Viz., with my own, and in
matters that depend on my own bounty.} So shall the last be first and the first
last. For many are called but few chosen.


%\bigskip

\atitle{Sexagesima Sunday}

\bibleref{Epistle}{2 Cor.~11:19--12:9}

Brethren, you gladly suffer the foolish: whereas yourselves are wise.  For you suffer
if a man bring you into bondage, if a man devour you, if a man take from you,
if a man be lifted up, if a man strike you on the face.  I seek according to
dishonour, as if we had been weak in this part. Wherein if any man dare (I
speak foolishly), I dare also.  They are Hebrews: so am I. They are Israelites:
so am I.  They are the seed of Abraham: so am I.  They are the ministers of
Christ (I speak as one less wise): I am more; in many more labours, in prisons
more frequently, in stripes above measure, in deaths often.  Of the Jews five
times did I receive forty stripes save one.  Thrice was I beaten with rods:
once I was stoned: thrice I suffered shipwreck: a night and a day I was in the
depth of the sea.  In journeying often, in perils of waters, in perils of
robbers, in perils from my own nation, in perils from the Gentiles, in perils
in the city, in perils in the wilderness, in perils in the sea, in perils from
false brethren: In labour and painfulness, in much watchings, in hunger and
thirst, in fastings often, in cold and nakedness: Besides those things which
are without: my daily instance, the solicitude for all the churches.
\challnote{My daily instance\ldots\ The labours that come in, and press upon me
every day.} Who is weak, and I am not weak? Who is scandalized, and I am not on
fire?  If I must needs glory, I will glory of the things that concern my
infirmity.  The God and Father of our Lord Jesus Christ, who is blessed for
ever, knoweth that I lie not.  At Damascus, the governor of the nation under
Aretas the king, guarded the city of the Damascenes, to apprehend me.  And
through a window in a basket was I let down by the wall: and so escaped his
hands.  If I must glory (it is not expedient indeed) but I will come to visions
and revelations of the Lord.  I know a man in Christ: above fourteen years ago
(whether in the body, I know not, or out of the body, I know not: God knoweth),
such a one caught up to the third heaven.  And I know such a man (whether in
the body, or out of the body, I know not: God knoweth): That he was caught up
into paradise and heard secret words which it is not granted to man to utter.
For such an one I will glory: but for myself I will glory nothing but in my
infirmities.  For though I should have a mind to glory, I shall not be foolish:
for I will say the truth. But I forbear, lest any man should think of me above
that which he seeth in me, or any thing he heareth from me.  And lest the
greatness of the revelations should exalt me, there was given me a sting of my
flesh, an angel of Satan, to buffet me.  For which thing, thrice I besought the
Lord that it might depart from me.  And he said to me: My grace is sufficient
for thee: for power is made perfect in infirmity. Gladly therefore will I glory
in my infirmities, that the power of Christ may dwell in me.  \challnote{Power
is made perfect\ldots\ The strength and power of God more perfectly shines
forth in our weakness and infirmity; as the more weak we are of ourselves, the
more illustrious is his grace in supporting us, and giving us the victory under
all trials and conflicts.}


\bibleref{Gospel}{Luke 8:4--15}

At that time, when a very great multitude was gathered together and hastened out of the
cities, unto Jesus, he spoke by a similitude.  The sower went out to sow his
seed. And as he sowed, some fell by the way side. And it was trodden down: and
the fowls of the air devoured it.  And other some fell upon a rock. And as soon
as it was sprung up, it withered away, because it had no moisture.  And other
some fell among thorns. And the thorns growing up with it, choked it.  And
other some fell upon good ground and, being sprung up, yielded fruit a
hundredfold. Saying these things, he cried out: He that hath ears to hear, let
him hear.  And his disciples asked him what this parable might be.  To whom he
said: To you it is given to know the mystery of the kingdom of God; but to the
rest in parables, that seeing they may not see and hearing may not understand.
\challnote{Seeing they may not see\ldots\ See the annotation, Mark 4. 12.} Now
the parable is this: The seed is the word of God.  And they by the way side are
they that hear: then the devil cometh and taketh the word out of their heart,
lest believing they should be saved.  Now they upon the rock are they who when
they hear receive the word with joy: and these have no roots: for they believe
for a while and in time of temptation they fall away.  And that which fell
among thorns are they who have heard and, going their way, are choked with the
cares and riches and pleasures of this life and yield no fruit.  But that on
the good ground are they who in a good and perfect heart, hearing the word,
keep it and bring forth fruit in patience.



%\bigskip

\atitle{Quinquagesima Sunday}

\bibleref{Epistle}{1 Cor.~13:1--13}

Brethren, if I speak with the tongues of men and of angels, and have not charity, I am
become as sounding brass, or a tinkling cymbal.  And if I should have prophecy
and should know all mysteries and all knowledge, and if I should have all
faith, so that I could remove mountains, and have not charity, I am nothing.
And if I should distribute all my goods to feed the poor, and if I should
deliver my body to be burned, and have not charity, it profiteth me nothing.
Charity is patient, is kind: charity envieth not, dealeth not perversely, is
not puffed up, is not ambitious, seeketh not her own, is not provoked to anger,
thinketh no evil: Rejoiceth not in iniquity, but rejoiceth with the truth:
Beareth all things, believeth all things, hopeth all things, endureth all
things.  Charity never falleth away: whether prophecies shall be made void or
tongues shall cease or knowledge shall be destroyed.  For we know in part: and
we prophesy in part.  But when that which is perfect is come, that which is in
part shall be done away.  When I was a child, I spoke as a child, I understood
as a child, I thought as a child. But, when I became a man, I put away the
things of a child.  We see now through a glass in a dark manner: but then face
to face. Now I know in part: but then I shall know even as I am known.  And now
there remain faith, hope, and charity, these three: but the greatest of these
is charity.


\bibleref{Gospel}{Luke 18:31--43}


At that time Jesus took unto him the twelve and said to them: Behold, we go up to
Jerusalem; and all things shall be accomplished which were written by the
prophets concerning the Son of man.  For he shall be delivered to the Gentiles
and shall be mocked and scourged and spit upon.  And after they have scourged
him, they will put him to death. And the third day he shall rise again.  And
they understood none of these things, and this word was hid from them: and they
understood not the things that were said.  Now it came to pass, when he drew
nigh to Jericho, that a certain blind man sat by the way side, begging.  And
when he heard the multitude passing by, he asked what this meant.  And they
told him that Jesus of Nazareth was passing by.  And he cried out, saying:
Jesus, Son of David, have mercy on me.  And they that went before rebuked him,
that he should hold his peace: but he cried out much more: Son of David, have
mercy on me.  And Jesus standing, commanded him to be brought unto him.  And
when he was come near, he asked him, saying; What wilt thou that I do to thee?
But he said: Lord, that I may see.  And Jesus said to him: Receive thy sight:
thy faith hath made thee whole.  And immediately he saw and followed him,
glorifying God.  And all the people, when they saw it, gave praise to God.

\sectionmark{Lent}

\bigskip

\atitle{1st Sunday of Lent}

\bibleref{Epistle}{2 Cor.~6:1--10}

Brethren, we exhort you that you receive not the grace of God in vain.
For he saith: In an accepted time have I heard thee and in the day of salvation
have I helped thee. Behold, now is the acceptable time: behold, now is the day
of salvation.  Giving no offence to any man, that our ministry be not blamed.
But in all things let us exhibit ourselves as the ministers of God, in much
patience, in tribulation, in necessities, in distresses, in stripes, in
prisons, in seditions, in labours, in watchings, in fastings, in chastity, in
knowledge, in longsuffering, in sweetness, in the Holy Ghost, in charity
unfeigned, in the word of truth, in the power of God: by the armour of justice
on the right hand and on the left: By honour and dishonour: by evil report and
good report: as deceivers and yet true: as unknown and yet known: As dying and
behold we live: as chastised and not killed: As sorrowful, yet always
rejoicing: as needy, yet enriching many: as having nothing and possessing all
things.


\bibleref{Gospel}{Matt.~4:1--11}


At that time, Jesus was led by the spirit into the desert, to be tempted by the devil.
And when he had fasted forty days and forty nights, afterwards he was hungry.
And the tempter coming said to him: If thou be the Son of God, command that
these stones be made bread.  Who answered and said: It is written, Not in bread
alone doth man live, but in every word that proceedeth from the mouth of God.
Then the devil took him up into the holy city, and set him upon the pinnacle of
the temple, and said to him: If thou be the Son of God, cast thyself down, for
it is written: That he hath given his angels charge over thee, and in their
hands shall they bear thee up, lest perhaps thou dash thy foot against a stone.
Jesus said to him: It is written again: Thou shalt not tempt the Lord thy God.
Again the devil took him up into a very high mountain, and shewed him all the
kingdoms of the world, and the glory of them, \challnote{Shewed him, etc\ldots\
That is, pointed out to him where each kingdom lay; and set forth in words what
was most glorious and admirable in each of them. Or also set before his eyes,
as it were in a large map, a lively representation of all those kingdoms.} And
said to him: All these will I give thee, if falling down thou wilt adore me.
Then Jesus saith to him: Begone, Satan: for it is written: The Lord thy God
shalt thou adore, and him only shalt thou serve.  Then the devil left him; and
behold angels came and ministered to him.


\bigskip

%\columnbreak

\atitle{2nd Sunday of Lent}

\bibleref{Epistle}{1 Thess.~4:1--7}

Brethren, we pray and beseech you in the Lord Jesus that,
as you have received from us, how you ought to walk and to please God, so also
you would walk, that you may abound the more.  For you know what precepts I
have given to you by the Lord Jesus.  For this is the will of God, your
sanctification: That you should abstain from fornication: That every one of you
should know how to possess his vessel in sanctification and honour, not in the
passion of lust, like the Gentiles that know not God: And that no man overreach
nor circumvent his brother in business: because the Lord is the avenger of all
these things, as we have told you before and have testified.  For God hath not
called us unto uncleanness, but unto sanctification.


\bibleref{Gospel}{Matt.~17:1--9}

At that time Jesus took Peter and James, and John his brother,
and bringeth them up into a high mountain apart: And he was transfigured before
them. And his face did shine as the sun: and his garments became white as snow.
And behold there appeared to them Moses and Elias talking with him.  And Peter
answering, said to Jesus: Lord, it is good for us to be here: if thou wilt, let
us make here three tabernacles, one for thee, and one for Moses, and one for
Elias.  And as he was yet speaking, behold a bright cloud overshadowed them.
And lo a voice out of the cloud, saying: This is my beloved Son, in whom I am
well pleased: hear ye him.  And the disciples hearing fell upon their face, and
were very much afraid.  And Jesus came and touched them: and said to them:
Arise, and fear not.  And they lifting up their eyes, saw no one, but only
Jesus.  And as they came down from the mountain, Jesus charged them, saying:
Tell the vision to no man, till the Son of man be risen from the dead.


%\columnbreak

\bigskip

\atitle{3rd Sunday of Lent}

\bibleref{Epistle}{Eph.~5:1--9}

Brethren, be ye therefore followers of God, as most dear children: And walk in love, as
Christ also hath loved us and hath delivered himself for us, an oblation and a
sacrifice to God for an odour of sweetness.  But fornication and all
uncleanness or covetousness, let it not so much as be named among you, as
becometh saints: Or obscenity or foolish talking or scurrility, which is to no
purpose: but rather giving of thanks.  For know you this and understand: That
no fornicator or unclean or covetous person (which is a serving of idols) hath
inheritance in the kingdom of Christ and of God.  Let no man deceive you with
vain words. For because of these things cometh the anger of God upon the
children of unbelief.  Be ye not therefore partakers with them.  For you were
heretofore darkness, but now light in the Lord.  Walk then as children of the
light.  For the fruit of the light is in all goodness and justice and truth.


\bibleref{Gospel}{Luke 11:14--28}


At that time Jesus was casting out a devil: and the same was dumb. And when he had cast out
the devil, the dumb spoke: and the multitudes, were in admiration at it.  But
some of them said: He casteth out devils by Beelzebub, the prince of devils.
And others tempting, asked of him a sign from heaven.  But he seeing their
thoughts, said to them: Every kingdom divided against itself shall be brought
to desolation; and house upon house shall fall.  And if Satan also be divided
against himself, how shall his kingdom stand? Because you say that through
Beelzebub I cast out devils.  Now if I cast out devils by Beelzebub, by whom do
your children cast them out? Therefore, they shall be your judges.  But if I by
the finger of God cast out devils, doubtless the kingdom of God is come upon
you.  When a strong man armed keepeth his court, those things are in peace
which he possesseth.  But if a stronger than he come upon him and overcome him,
he will take away all his armour wherein he trusted and will distribute his
spoils.  He that is not with me is against me; and he that gathereth not with
me scattereth.  When the unclean spirit is gone out of a man, he walketh
through places without water, seeking rest: and not finding, he saith: I will
return into my house whence I came out.  And when he is come, he findeth it
swept and garnished.  Then he goeth and taketh with him seven other spirits
more wicked than himself: and entering in they dwell there. And the last state
of that man becomes worse than the first.  And it came to pass, as he spoke
these things, a certain woman from the crowd, lifting up her voice, said to
him: Blessed is the womb that bore thee and the paps that gave thee suck.  But
he said: Yea rather, blessed are they who hear the word of God and keep it.


%\bigskip

%\columnbreak

\atitle{4th Sunday of Lent}

\bibleref{Epistle}{Gal.~4:22--31}

Brethren, it is written that Abraham had two sons: the one by a bondwoman and the
other by a free woman.  But he who was of the bondwoman was born according to
the flesh: but he of the free woman was by promise.  Which things are said by
an allegory. For these are the two testaments. The one from Mount Sina,
engendering unto bondage, which is Agar.  For Sina is a mountain in Arabia,
which hath affinity to that Jerusalem which now is: and is in bondage with her
children.  But that Jerusalem which is above is free: which is our mother.  For
it is written: Rejoice, thou barren, that bearest not: break forth and cry thou
that travailest not: for many are the children of the desolate, more than of
her that hath a husband.  Now we, brethren, as Isaac was, are the children of
promise.  But as then he that was born according to the flesh persecuted him
that was after the spirit: so also it is now.  But what saith the scripture?
Cast out the bondwoman and her son: for the son of the bondwoman shall not be
heir with the son of the free woman.  So then, brethren, we are not the
children of the bondwoman but of the free: by the freedom wherewith Christ has
made us free.

%\columnbreak

\bibleref{Gospel}{John 6:1--15}

At that time, Jesus went over the sea of Galilee, which is that of
Tiberias.  And a great multitude followed him, because they saw the miracles
which he did on them that were diseased.  Jesus therefore went up into a
mountain: and there he sat with his disciples.  Now the pasch, the festival day
of the Jews, was near at hand.  When Jesus therefore had lifted up his eyes and
seen that a very great multitude cometh to him, he said to Philip: Whence shall
we buy bread, that these may eat?  And this he said to try him: for he himself
knew what he would do.  Philip answered him: Two hundred pennyworth of bread is
not sufficient for them that every one may take a little.  One of his
disciples, Andrew, the brother of Simon Peter, saith to him: There is a boy
here that hath five barley loaves and two fishes.  But what are these among so
many?  Then Jesus said: Make the men sit down. Now, there was much grass in the
place. The men therefore sat down, in number about five thousand.  And Jesus
took the loaves: and when he had given thanks, he distributed to them that were
set down. In like manner also of the fishes, as much as they would.  And when
they were filled, he said to his disciples: gather up the fragments that
remain, lest they be lost.  They gathered up therefore and filled twelve
baskets with the fragments of the five barley loaves which remained over and
above to them that had eaten.  Now those men, when they had seen what a miracle
Jesus had done, said: This is of a truth the prophet that is to come into the
world.  Jesus therefore, when he knew that they would come to take him by force
and make him king, fled again into the mountains, himself alone.


%\bigskip

\atitle{Passion Sunday}

\bibleref{Epistle}{Heb.~9:11--15}

Brethren, Christ, being come an high Priest of the good things to come, by a greater
and more perfect tabernacle, not made with hand, that is, not of this creation:
Neither by the blood of goats or of calves, but by his own blood, entered once
into the Holies, having obtained eternal redemption.  \challnote{Eternal
redemption\ldots\ By that one sacrifice of his blood, once offered on the
cross, Christ our Lord paid and exhibited, once for all, the general price and
ransom of all mankind: which no other priest could do.} For if the blood of
goats and of oxen, and the ashes of an heifer, being sprinkled, sanctify such
as are defiled, to the cleansing of the flesh: How much more shall the blood of
Christ, who by the Holy Ghost offered himself unspotted unto God, cleanse our
conscience from dead works, to serve the living God?  And therefore he is the
mediator of the new testament: that by means of his death for the redemption of
those transgressions which were under the former testament, they that are
called may receive the promise of eternal inheritance, in Christ Jesus our Lord.


\bibleref{Gospel}{John 8:46--59}

At that time Jesus said to the multitudes of the Jews:
Which of you shall convince me of sin? If I say the truth to you, why do you
not believe me: He that is of God heareth the words of God. Therefore you hear
them not, because you are not of God.  The Jews therefore answered and said to
him: Do not we say well that thou art a Samaritan and hast a devil?  Jesus
answered: I have not a devil: but I honour my Father. And you have dishonoured
me.  But I seek not my own glory: there is one that seeketh and judgeth.  Amen,
amen, I say to you: If any man keep my word, he shall not see death for ever.
The Jews therefore said: Now we know that thou hast a devil.  Abraham is dead,
and the prophets: and thou sayest: If any man keep my word, he shall not taste
death for ever.  Art thou greater than our father Abraham who is dead? And the
prophets are dead. Whom dost thou make thyself?  Jesus answered: If I glorify
myself, my glory is nothing.  It is my Father that glorifieth me, of whom you
say that he is your God.  And you have not known him: but I know him. And if I
shall say that I know him not, I shall be like to you, a liar. But I do know
him and do keep his word.  Abraham your father rejoiced that he might see my
day: he saw it and was glad.  The Jews therefore said to him: Thou art not yet
fifty years old.  And hast thou seen Abraham?  Jesus said to them: Amen, amen,
I say to you, before Abraham was made, \textsc{I am}.  They took up stones
therefore to cast at him. But Jesus hid himself and went out of the temple.


%\bigskip

\atitle{Palm Sunday}

\bibleref{Epistle}{Phil.~2:5--11}

Brethren, let this mind be in you, which was also in Christ Jesus: Who being in the
form of God, thought it not robbery to be equal with God: But emptied himself,
taking the form of a servant, being made in the likeness of men, and in habit
found as a man.
\challnote{Emptied himself, exinanivit\ldots\ made himself as of no account.}  He humbled
himself, becoming obedient unto death, even to the death of the cross.  For
which cause, God also hath exalted him and hath given him a name which is above
all names: That in the name of Jesus every knee should bow, of those that are
in heaven, on earth, and under the earth: And that every tongue should confess
that the Lord Jesus Christ is in the glory of God the Father.

%\columnbreak

\bibleref{Gospel}{Matt.~26:36--27:60}

At that time, Jesus came with them into a country place which is called Gethsemani. And
he said to his disciples: Sit you here, till I go yonder and pray.  And taking
with him Peter and the two sons of Zebedee, he began to grow sorrowful and to
be sad.  Then he saith to them: My soul is sorrowful even unto death. Stay you
here and watch with me.  And going a little further, he fell upon his face,
praying and saying: My Father, if it be possible, let this chalice pass from
me.  Nevertheless, not as I will but as thou wilt.  And he cometh to his
disciples and findeth them asleep. And he saith to Peter: What? Could you not
watch one hour with me?  Watch ye: and pray that ye enter not into temptation.
The spirit indeed is willing, but the flesh is weak.  Again the second time, he
went and prayed, saying: My Father, if this chalice may not pass away, but I
must drink it, thy will be done.  And he cometh again and findeth them
sleeping: for their eyes were heavy.  And leaving them, he went again: and he
prayed the third time, saying the selfsame word.  Then he cometh to his
disciples and said to them: Sleep ye now and take your rest. Behold the hour is
at hand: and the Son of man shall be betrayed into the hands of sinners.  Rise:
let us go. Behold he is at hand that will betray me.  As he yet spoke, behold
Judas, one of the twelve, came, and with him a great multitude with swords and
clubs, sent from the chief priests and the ancients of the people.  And he that
betrayed him gave them a sign, saying: Whomsoever I shall kiss, that is he.
Hold him fast.  And forthwith coming to Jesus, he said: Hail, Rabbi. And he
kissed him.  And Jesus said to him: Friend, whereto art thou come? Then they
came up and laid hands on Jesus and held him.  And behold one of them that were
with Jesus, stretching forth his hand, drew out his sword: and striking the
servant of the high priest, cut off his ear.  Then Jesus saith to him: Put up
again thy sword into its place: for all that take the sword shall perish with
the sword.  Thinkest thou that I cannot ask my Father, and he will give me
presently more than twelve legions of angels?  How then shall the scriptures be
fulfilled, that so it must be done?  In that same hour, Jesus said to the
multitudes: You are come out, as it were to a robber, with swords and clubs to
apprehend me. I sat daily with you, teaching in the temple: and you laid not
hands on me.  Now all this was done that the scriptures of the prophets might
be fulfilled. Then the disciples, all leaving him, fled.  

But they holding Jesus led him to Caiphas the high priest, where the scribes
and the ancients were assembled.  And Peter followed him afar off, even to the
court of the high priest, and going in, he sat with the servants, that he might
see the end.  And the chief priests and the whole council sought false witness
against Jesus, that they might put him to death.  And they found not, whereas
many false witnesses had come in. And last of all there came two false
witnesses: And they said: This man said, I am able to destroy the temple of God
and after three days to rebuild it.  And the high priest rising up, said to
him: Answerest thou nothing to the things which these witness against thee?
But Jesus held his peace. And the high priest said to him: I adjure thee by the
living God, that thou tell us if thou be the Christ the Son of God.  Jesus
saith to him: Thou hast said it. Nevertheless I say to you, hereafter you shall
see the Son of man sitting on the right hand of the power of God and coming in
the clouds of heaven.  Then the high priest rent his garments, saying: He hath
blasphemed: What further need have we of witnesses? Behold, now you have heard
the blasphemy.  What think you? But they answering, said: He is guilty of
death.  Then did they spit in his face and buffeted him. And others struck his
face with the palms of their hands, saying: Prophesy unto us, O Christ. Who is
he that struck thee?  

But Peter sat without in the court. And there came to him a servant maid,
saying: Thou also wast with Jesus the Galilean.  But he denied before them all,
saying: I know not what thou sayest.  And as he went out of the gate, another
maid saw him; and she saith to them that were there: This man also was with
Jesus of Nazareth.  And again he denied with an oath: I know not the man.  And
after a little while, they came that stood by and said to Peter: Surely thou
also art one of them. For even thy speech doth discover thee.  Then he began to
curse and to swear that he knew not the man. And immediately the cock crew.
And Peter remembered the word of Jesus which he had said: Before the cock crow,
thou wilt deny me thrice. And going forth, he wept bitterly.

And when morning was come, all the chief priests and ancients of the people
took counsel against Jesus, that they might put him to death.  And they brought
him bound and delivered him to Pontius Pilate the governor.  

Then Judas, who betrayed him, seeing that he was condemned, repenting himself,
brought back the thirty pieces of silver to the chief priests and ancients,
saying: I have sinned in betraying innocent blood. But they said: What is that
to us? Look thou to it.  And casting down the pieces of silver in the temple,
he departed and went and hanged himself with an halter.  But the chief priests
having taken the pieces of silver, said: It is not lawful to put them into the
corbona, because it is the price of blood.  \challnote{Corbona\ldots\ A place
in the temple where the people put in their gifts or offerings.} And after they
had consulted together, they bought with them the potter's field, to be a
burying place for strangers.  For this cause that field was called Haceldama,
that is, the field of blood, even to this day.  Then was fulfilled that which
was spoken by Jeremias the prophet, saying: And they took the thirty pieces of
silver, the price of him that was prized, whom they prized of the children of
Israel.  And they gave them unto the potter's field, as the Lord appointed to
me.  

And Jesus stood before the governor, and the governor asked him, saying: Art
thou the king of the Jews? Jesus saith to him: Thou sayest it.  And when he was
accused by the chief priests and ancients, he answered nothing.  Then Pilate
saith to him: Dost not thou hear how great testimonies they allege against
thee?  And he answered him to never a word, so that the governor wondered
exceedingly.  Now upon the solemn day the governor was accustomed to release to
the people one prisoner, whom they would.  And he had then a notorious prisoner
that was called Barabbas.  They therefore being gathered together, Pilate said:
Whom will you that I release to You: Barabbas, or Jesus that is called Christ?
For he knew that for envy they had delivered him.  And as he was sitting in the
place of judgment, his wife sent to him, saying: Have thou nothing to do with
that just man; for I have suffered many things this day in a dream because of
him.  But the chief priests and ancients persuaded the people that they should
ask Barabbas and make Jesus away.  And the governor answering, said to them:
Whether will you of the two to be released unto you? But they said: Barabbas.
Pilate saith to them: What shall I do then with Jesus that is called Christ?
They say all: Let him be crucified.  The governor said to them: Why, what evil
hath he done? But they cried out the more, saying: Let him be crucified.  And
Pilate seeing that he prevailed nothing, but that rather a tumult was made,
taking water washed his hands before the people, saying: I am innocent of the
blood of this just man. Look you to it.  And the whole people answering, said:
His blood be upon us and upon our children.  Then he released to them Barabbas:
and having scourged Jesus, delivered him unto them to be crucified.  

Then the soldiers of the governor, taking Jesus into the hall, gathered
together unto him the whole band.  And stripping him, they put a scarlet cloak
about him.  And platting a crown of thorns, they put it upon his head, and a
reed in his right hand. And bowing the knee before him, they mocked him,
saying: Hail, King of the Jews.  And spitting upon him, they took the reed and
struck his head.  And after they had mocked him, they took off the cloak from
him and put on him his own garments and led him away to crucify him.  And going
out, they found a man of Cyrene, named Simon: him they forced to take up his
cross.  And they came to the place that is called Golgotha, which is the place
of Calvary.  And they gave him wine to drink mingled with gall. And when he had
tasted, he would not drink.  And after they had crucified him, they divided his
garments, casting lots; that it might be fulfilled which was spoken by the
prophet, saying: They divided my garments among them; and upon my vesture they
cast lots.  And they sat and watched him.  And they put over his head his cause
written: \textsc{This is Jesus the King of the Jews}.  Then were crucified with
him two thieves: one on the right hand and one on the left.  And they that
passed by blasphemed him, wagging their heads, and saying: Vah, thou that
destroyest the temple of God and in three days dost rebuild it: save thy own
self. If thou be the Son of God, come down from the cross.  In like manner also
the chief priests, with the scribes and ancients, mocking said: He saved
others: himself he cannot save. If he be the king of Israel, let him now come
down from the cross: and we will believe him.  He trusted in God: let him now
deliver him if he will have him.  For he said: I am the Son of God.  And the
selfsame thing the thieves also that were crucified with him reproached him
with.  

Now from the sixth hour, there was darkness over the whole earth, until the
ninth hour.  And about the ninth hour, Jesus cried with a loud voice, saying:
Eli, Eli, lamma sabacthani? That is, My God, My God, why hast thou forsaken me?
And some that stood there and heard said: This man calleth Elias.  And
immediately one of them running took a sponge and filled it with vinegar and
put it on a reed and gave him to drink.  And the others said: Let be. Let us
see whether Elias will come to deliver him.  And Jesus again crying with a loud
voice, yielded up the ghost.  

And behold the veil of the temple was rent in two from the top even to the
bottom: and the earth quaked and the rocks were rent.  And the graves were
opened: and many bodies of the saints that had slept arose, and coming out of
the tombs after his resurrection, came into the holy city and appeared to many.
Now the centurion and they that were with him watching Jesus, having seen the
earthquake and the things that were done, were sore afraid, saying: Indeed this
was the Son of God.  And there were there many women afar off, who had followed
Jesus from Galilee, ministering unto him: Among whom was Mary Magdalen and Mary
the mother of James and Joseph and the mother of the sons of Zebedee.  And when
it was evening, there came a certain rich man of Arimathea, named Joseph, who
also himself was a disciple of Jesus.  He went to Pilate and asked the body of
Jesus. Then Pilate commanded that the body should be delivered.  And Joseph
taking the body wrapped it up in a clean linen cloth: And laid it in his own
new monument, which he had hewed out in a rock. And he rolled a great stone to
the door of the monument and went his way.

%\columnbreak

\sectionmark{Easter}

\atitle{Easter Sunday}

\bibleref{Epistle}{1 Cor.~5:7--8}

Brethren, purge out the old leaven, that you may be a new paste, as you are unleavened.
For Christ our pasch is sacrificed.  Therefore, let us feast, not with the old
leaven, nor with the leaven of malice and wickedness: but with the unleavened
bread of sincerity and truth.


\bibleref{Gospel}{Mark 16:1--7}

At that time, % And when the sabbath was past, 
Mary Magdalen and Mary the mother of James and
Salome bought sweet spices, that coming, they might anoint Jesus.  And very
early in the morning, the first day of the week, they come to the sepulchre,
the sun being now risen.  \challnote{The sun being now risen\ldots\ They set
out before it was light, to go to the sepulchre; but the sun was risen when
they arrived there. Or, figuratively, the sun here spoken of is the sun of
justice, Christ Jesus our Lord, who was risen before their coming.} And they
said one to another: Who shall roll us back the stone from the door of the
sepulchre?  And looking, they saw the stone rolled back. For it was very great.
And entering into the sepulchre, they saw a young man sitting on the right
side, clothed with a white robe: and they were astonished.  Who saith to them:
Be not affrighted, you seek Jesus of Nazareth, who was crucified. He is risen:
he is not here.  Behold the place where they laid him.  But go, tell his
disciples and Peter that he goeth before you into Galilee. There you shall see
him, as he told you.


%\bigskip

\atitle{Low Sunday}

\bibleref{Epistle}{1 John 5:4--10}

Dearly-beloved: whatsoever is born of God overcometh the world. And this is the victory
which overcameth the world: Our faith.  \challnote{Our faith\ldots\ Not a bare,
speculative, or dead faith; but a faith that worketh by charity. Gal.~5.6} Who
is he that overcometh the world, but he that believeth that Jesus is the Son of
God?  This is he that came by water and blood, Jesus Christ: not by water only
but by water and blood. And it is the Spirit which testifieth that Christ is
the truth.  \challnote{Came by water and blood\ldots\ Not only to wash away our
sins by the water of baptism, but by his own blood.} And there are Three who
give testimony in heaven, the Father, the Word, and the Holy Ghost. And these
three are one.  And there are three that give testimony on earth: the spirit
and the water and the blood. And these three are one.  \challnote{The spirit,
and the water, and the blood\ldots\ As the Father, the Word, and the Holy
Ghost, all bear witness to Christ's divinity; so the spirit, which he yielded
up, crying out with a loud voice upon the cross; and the water and blood that
issued from his side, bear witness to his humanity, and are one; that is, all
agree in one testimony.} If we receive the testimony of men, the testimony of
God is greater. For this is the testimony of God, which is greater, because he
hath testified of his Son.  He that believeth in the Son of God hath the
testimony of God in himself. He that believeth not the Son maketh him a liar:
because he believeth not in the testimony which God hath testified of his Son.
\challnote{He that believeth not the Son, etc\ldots\ By refusing to believe the
testimonies given by the three divine persons, that Jesus was the Messias, and
the true Son of God, by whom eternal life is obtained and promised to all that
comply with his doctrine. In him we have also this lively confidence, that we
shall obtain whatever we ask, according to his will, when we ask what is for
our good, with perseverance, and in the manner we ought. And this we know, and
have experience of, by having obtained the petitions that we have made.}


\bibleref{Gospel}{John 20:19--31}

At that time, when it was late the same day, the first of the week, and the doors were
shut, where the disciples were gathered together, for fear of the Jews, Jesus
came and stood in the midst and said to them: Peace be to you.  \challnote{The
doors were shut\ldots\ The same power which could bring Christ's whole body,
entire in all its dimensions, through the doors, can without the least question
make the same body really present in the sacrament; though both the one and the
other be above our comprehension.} And when he had said this, he shewed them
his hands and his side.  The disciples therefore were glad, when they saw the
Lord.  He said therefore to them again: Peace be to you. As the Father hath
sent me, I also send you.  When he had said this, he breathed on them; and he
said to them: Receive ye the Holy Ghost.  Whose sins you shall forgive, they
are forgiven them: and whose sins you shall retain, they are retained.
\challnote{Whose sins, etc\ldots\ See here the commission, stamped by the broad
seal of heaven, by virtue of which the pastors of Christ's church absolve
repenting sinners upon their confession.} Now Thomas, one of the twelve, who is
called Didymus, was not with them when Jesus came.  The other disciples
therefore said to him: We have seen the Lord.  But he said to them: Except I
shall see in his hands the print of the nails and put my finger into the place
of the nails and put my hand into his side, I will not believe.  And after
eight days, again his disciples were within, and Thomas with them. Jesus
cometh, the doors being shut, and stood in the midst and said: Peace be to you.
Then he said to Thomas: Put in thy finger hither and see my hands. And bring
hither the hand and put it into my side.  And be not faithless, but believing.
Thomas answered and said to him: My Lord and my God.  Jesus saith to him:
Because thou hast seen me, Thomas, thou hast believed: blessed are they that
have not seen and have believed.  Many other signs also did Jesus in the sight
of his disciples, which are not written in this book.  But these are written,
that you may believe that Jesus is the Christ, the Son of God: and that
believing, you may have life in his name.

%\bigskip

%\columnbreak

\atitle{2nd Sunday \break after Easter}

\bibleref{Epistle}{1 Peter 2:21--25}

Dearly-beloved: % For unto this are you called: because 
Christ also suffered for us, leaving you
an example that you should follow his steps.  Who did no sin, neither was guile
found in his mouth.  Who, when he was reviled, did not revile: when he
suffered, he threatened not, but delivered himself to him that judged him
unjustly.  Who his own self bore our sins in his body upon the tree: that we,
being dead to sins, should live to justice: by whose stripes you were healed.
For you were as sheep going astray: but you are now converted to the shepherd
and bishop of your souls.


\bibleref{Gospel}{John 10:11--16}

At that time Jesus said to the Pharisees: I am the good shepherd. The good shepherd giveth his life for his sheep.  But
the hireling and he that is not the shepherd, whose own the sheep are not,
seeth the wolf coming and leaveth the sheep and flieth: and the wolf casteth
and scattereth the sheep, and the hireling flieth, because he is a hireling:
and he hath no care for the sheep.  I am the good shepherd: and I know mine,
and mine know me.  As the Father knoweth me, and I know the Father: and I lay
down my life for my sheep.  And other sheep I have that are not of this fold:
them also I must bring. And they shall hear my voice: And there shall be one
fold and one shepherd.


%\bigskip

%\columnbreak

\atitle{3rd Sunday \break after Easter}

\bibleref{Epistle}{1 Peter 2:11--19}

Dearly beloved, I beseech you, as strangers and pilgrims, to refrain yourselves
from carnal desires which war against the soul, having your conversation good
among the Gentiles: that whereas they speak against you as evildoers, they may,
by the good works which they shall behold in you, glorify God in the day of
visitation.  Be ye subject therefore to every human creature for God's sake:
whether it be to the king as excelling, or to governors as sent by him for the
punishment of evildoers and for the praise of the good.  For so is the will of
God, that by doing well you may put to silence the ignorance of foolish men: As
free and not as making liberty a cloak for malice, but as the servants of God.
Honour all men. Love the brotherhood. Fear God. Honour the king.  Servants, be
subject to your masters with all fear, not only to the good and gentle but also
to the froward.  For this is thankworthy: if, for conscience towards God, a man
endure sorrows, suffering wrongfully.


\bibleref{Gospel}{John 16:16--22}

At that time Jesus said to his disciples: 
A little while, and now you shall not see me: and again a little while, and you
shall see me: because I go to the Father.  Then some of his disciples said one
to another: What is this that he saith to us: A little while, and you shall not
see me: and again a little while, and you shall see me, and, Because I go to
the Father?  They said therefore: What is this that he saith, A little while?
We know not what he speaketh.  And Jesus knew that they had a mind to ask him.
And he said to them: Of this do you inquire among yourselves, because I said: A
little while, and you shall not see me; and again a little while, and you shall
see me?  Amen, amen, I say to you, that you shall lament and weep, but the
world shall rejoice: and you shall be made sorrowful, but your sorrow shall be
turned into joy.  A woman, when she is in labour, hath sorrow, because her hour
is come; but when she hath brought forth the child, she remembereth no more the
anguish, for joy that a man is born into the world.  So also you now indeed
have sorrow: but I will see you again and your heart shall rejoice. And your
joy no man shall take from you.


%\bigskip

\atitle{4th Sunday \break after Easter}

\bibleref{Epistle}{James 1:17--21}

Dearly-beloved: every best gift and every perfect gift is from above, coming down from the
Father of lights, with whom there is no change nor shadow of alteration.  For
of his own will hath he begotten us by the word of truth, that we might be some
beginning of his creature.  \challnote{Some beginning\ldots\ That is, a kind of
first fruits of his creatures.} You know, my dearest brethren. And let every
man be swift to hear, but slow to speak and slow to anger.  For the anger of
man worketh not the justice of God.  Wherefore, casting away all uncleanness
and abundance of naughtiness, with meekness receive the ingrafted word, which
is able to save your souls.


\bibleref{Gospel}{John 16:5--14}

At that time Jesus said to his disciples:
%But I told you not these things from the beginning, because I was with you. And
%now 
I go to him that sent me, and none of you asketh me: Whither goest thou?
But because I have spoken these things to you, sorrow hath filled your heart.
But I tell you the truth: it is expedient to you that I go.  For if I go not,
the Paraclete will not come to you: but if I go, I will send him to you.  And
when he is come, he will convince the world of sin and of justice and of
judgment.  \challnote{He will convince the world of sin, etc\ldots\ The Holy
Ghost, by his coming brought over many thousands, first, to a sense of their
sin in not believing in Christ. Secondly, to a conviction of the justice of
Christ, now sitting at the right hand of his Father. And thirdly, to a right
apprehension of the judgment prepared for them that choose to follow Satan, who
is already judged and condemned.} Of sin: because they believed not in me.  And
of justice: because I go to the Father: and you shall see me no longer.  And of
judgment: because the prince of this world is already judged.  I have yet many
things to say to you: but you cannot bear them now.  But when he, the Spirit of
truth, is come, he will teach you all truth. For he shall not speak of himself:
but what things soever he shall hear, he shall speak. And the things that are
to come, he shall shew you.  \challnote{Will teach you all truth\ldots\ See the
annotation on chap. 14. ver. 26.} He shall glorify me: because he shall receive
of mine and shall shew it to you.


%\bigskip

\atitle{5th Sunday \break after Easter}

\bibleref{Epistle}{James 1:22--27}

Dearly-beloved: be ye doers of the word and not hearers only, deceiving your own selves.
For if a man be a hearer of the word and not a doer, he shall be compared to a
man beholding his own countenance in a glass.  For he beheld himself and went
his way and presently forgot what manner of man he was.  But he that hath
looked into the perfect law of liberty and hath continued therein, not becoming
a forgetful hearer but a doer of the work: this man shall be blessed in his
deed.  And if any man think himself to be religious, not bridling his tongue
but deceiving his own heart, this man's religion is vain.  Religion clean and
undefiled before God and the Father is this: to visit the fatherless and widows
in their tribulation and to keep one's self unspotted from this world.


\bibleref{Gospel}{John 16:23--30}

%And in that day you shall not ask me any thing. 
At that time Jesus said to his disciples:
Amen, amen, I say to you: if
you ask the Father any thing in my name, he will give it you.  Hitherto, you
have not asked any thing in my name. Ask, and you shall receive; that your joy
may be full.  These things I have spoken to you in proverbs. The hour cometh
when I will no longer speak to you in proverbs, but will shew you plainly of
the Father.  In that day, you shall ask in my name: and I say not to you that I
will ask the Father for you.  For the Father himself loveth you, because you
have loved me and have believed that I came out from God.  I came forth from
the Father and am come into the world: again I leave the world and I go to the
Father.  His disciples say to him: Behold, now thou speakest plainly and
speakest no proverb.  Now we know that thou knowest all things and thou needest
not that any man should ask thee. By this we believe that thou camest forth
from God.


\bigskip

%\columnbreak

\atitle{Ascension Thursday}

\bibleref{Epistle}{Acts 1:1--11}

The former treatise I made, O Theophilus, of all things which Jesus began to do
and to teach, until the day on which, giving commandments by the Holy Ghost to
the apostles whom he had chosen, he was taken up.  To whom also he shewed
himself alive after his passion, by many proofs, for forty days appearing to
them, and speaking of the kingdom of God.  And eating together with them, he
commanded them, that they should not depart from Jerusalem, but should wait for
the promise of the Father, which you have heard (saith he) by my mouth.  For
John indeed baptized with water: but you shall be baptized with the Holy Ghost,
not many days hence.  They therefore who were come together, asked him, saying:
Lord, wilt thou at this time restore again the kingdom of Israel?  But he said
to them: It is not for you to know the time or moments, which the Father hath
put in his own power: But you shall receive the power of the Holy Ghost coming
upon you, and you shall be witnesses unto me in Jerusalem, and in all Judea,
and Samaria, and even to the uttermost part of the earth.  And when he had said
these things, while they looked on, he was raised up: and a cloud received him
out of their sight.  And while they were beholding him going up to heaven,
behold two men stood by them in white garments.  Who also said: Ye men of
Galilee, why stand you looking up to heaven? This Jesus who is taken up from
you into heaven, shall so come as you have seen him going into heaven.

\bigskip

%\colmnbreak

\bibleref{Gospel}{Mark 16:14--20}

At that time, Jesus appeared to the eleven as they were at table: and he upbraided
them with their incredulity and hardness of heart, because they did not believe
them who had seen him after he was risen again.  And he said to them: Go ye
into the whole world and preach the gospel to every creature.  He that
believeth and is baptized shall be saved: but he that believeth not shall he
condemned.  And these signs shall follow them that believe: In my name they
shall cast out devils. They shall speak with new tongues.  They shall take up
serpents: and if they shall drink any deadly thing, it shall not hurt them.
They shall lay their hand upon the sick: and they shall recover.  And the Lord
Jesus, after he had spoken to them, was taken up into heaven and sitteth on the
right hand of God.  But they going forth preached every where: the Lord working
withal, and confirming the word with signs that followed.


%\bigskip

\atitle{Sunday %within the Octave of 
after the Ascension}

\bibleref{Epistle}{1 Peter 4:7--11}

Dearly-beloved: % the end of all is at hand. 
Be prudent therefore and watch in prayers.  But
before all things have a constant mutual charity among yourselves: for charity
covereth a multitude of sins.  Using hospitality one towards another, without
murmuring, as every man hath received grace, ministering the same one to
another: as good stewards of the manifold grace of God.  If any man speak, let
him speak, as the words of God. If any minister, let him do it, as of the power
which God administereth: that in all things God may be honoured through Jesus
Christ our Lord.%: to whom is glory and empire for ever and ever. Amen.


\bibleref{Gospel}{John 15:26--16:4}

At that time Jesus said to his disciples:
When the Paraclete cometh, whom I will send you from the Father, the Spirit
of truth, who proceedeth from the Father, he shall give testimony of me.
\challnote{Whom I will send\ldots\ This proves, against the modern Greeks, that
the Holy Ghost proceedeth from the Son, as well as from the Father: otherwise
he could not be sent by the Son.} And you shall give testimony, because you are
with me from the beginning.  These things have I
spoken to you that you may not be scandalized.  They will put you out of the
synagogues: yea, the hour cometh, that whosoever killeth you will think that he
doth a service to God.  And these things will they do to you; because they have
not known the Father nor me.  But these things I have told you, that when the
hour shall come, you may remember that I told you of them.

\sectionmark{Pentecost}

\atitle{Pentecost}

\bibleref{Epistle}{Acts 2:1--11}

When the days of the Pentecost were accomplished, they were all together in
one place: And suddenly there came a sound from heaven, as of a mighty wind
coming: and it filled the whole house where they were sitting.  And there
appeared to them parted tongues, as it were of fire: and it sat upon every one
of them.  And they were all filled with the Holy Ghost: and they began to speak
with divers tongues, according as the Holy Ghost gave them to speak.  Now there
were dwelling at Jerusalem, Jews, devout men, out of every nation under heaven.
And when this was noised abroad, the multitude came together, and were
confounded in mind, because that every man heard them speak in his own tongue.
And they were all amazed, and wondered, saying: Behold, are not all these that
speak Galilean?  And how have we heard, every man our own tongue wherein we
were born?  Parthians and Medes and Elamites and inhabitants of Mesopotamia,
Judea, and Cappadocia, Pontus and Asia, Phrygia and Pamphylia, Egypt and the
parts of Libya about Cyrene, and strangers of Rome, Jews also, and proselytes,
Cretes, and Arabians: we have heard them speak in our own tongues the wonderful
works of God.


\bibleref{Gospel}{John 14:23--31}

At that time Jesus said to his disciples:
%Jesus answered and said to him: 
If any one love me, he will keep my word. And
my Father will love him and we will come to him and will make our abode with
him.  He that loveth me not keepeth not my words. And the word which you have
heard is not mine; but the Father's who sent me.  These things have I spoken to
you, abiding with you.  But the Paraclete, the Holy Ghost, whom the Father will
send in my name, he will teach you all things and bring all things to your
mind, whatsoever I shall have said to you.  \challnote{Teach you all
things\ldots\ Here the Holy Ghost is promised to the apostles and their
successors, particularly, in order to teach them all truth, and to preserve
them from error.} Peace I leave with you: my peace I give unto you: not as the
world giveth, do I give unto you. Let not your heart be troubled: nor let it be
afraid.  You have heard that I said to you: I go away, and I come unto you. If
you loved me you would indeed be glad, because I go to the Father: for the
Father is greater than I.  \challnote{For the Father is greater than I\ldots\
It is evident, that Christ our Lord speaks here of himself as he is made man:
for as God he is equal to the Father. (See Phil.~2.) Any difficulty of
understanding the meaning of these words will vanish, when the relative
circumstances of the text here are considered: for Christ being at this time
shortly to suffer death, signified to his apostles his human nature by these
very words: for as God he could not die. And therefore as he was both God and
man, it must follow that according to his humanity he was to die, which the
apostles were soon to see and believe, as he expresses, ver.~29. And now I have
told you before it come to pass, that when it shall come to pass, you may
believe.} And now I have told you before it come to pass, that when it shall
come to pass, you may believe.  I will not now speak many things with you. For
the prince of this world cometh, and in me he hath not any thing.  But that
the world may know that I love the Father, and as the Father hath given me
commandment, so do I. %Arise, let us go hence.


\bigskip

\atitle{Trinity Sunday}

\bibleref{Epistle}{Rom.~11:33--36}

O the depth of the riches of the wisdom and of the knowledge of God! How
incomprehensible are his judgments, and how unsearchable his ways!  For who
hath known the mind of the Lord? Or who hath been his counsellor?  Or who hath
first given to him, and recompense shall be made him?  For of him, and by him,
and in him, are all things: to him be glory for ever. Amen.


\bibleref{Gospel}{Matt.~28:18--20}

At that time Jesus said to his disciples:
%And Jesus coming, spoke to them, saying: 
All power is given to me in heaven and
in earth.  \challnote{All power, etc\ldots\ See here the warrant and commission
of the apostles and their successors, the bishops and pastors of Christ's
church. He received from his Father all power in heaven and in earth: and in
virtue of this power, he sends them (even as his Father sent him, St. John 20.\
21) to teach and disciple, not one, but all nations; and instruct them in all
truths: and that he may assist them effectually in the execution of this
commission, he promises to be with them, not for three or four hundred years
only, but all days, even to the consummation of the world.  How then could the
Catholic Church ever go astray; having always with her pastors, as is here
promised, Christ himself, who is the way, the truth, and the life. St.~John
14.} Going therefore, teach ye all nations: baptizing them in the name of the
Father and of the Son and of the Holy Ghost.  Teaching them to observe all
things whatsoever I have commanded you. And behold I am with you all days, even
to the consummation of the world.


\bigskip

\atitle{1st Sunday \break after Pentecost}

\bibleref{Epistle}{1 John 4:8--21}

Dearly-beloved: %He that loveth not knoweth not God: for 
God is charity.  By this hath the
charity of God appeared towards us, because God hath sent his only begotten Son
into the world, that we may live by him.  In this is charity: not as though we
had loved God, but because he hath first loved us, and sent his Son to be a
propitiation for our sins.  My dearest, if God hath so loved us, we also ought
to love one another.  No man hath seen God at any time. If we love one another,
God abideth in us: and his charity is perfected in us.  In this we know that we
abide in him, and he in us: because he hath given us of his spirit.  And we
have seen and do testify that the Father hath sent his Son to be the Saviour of
the world.  Whosoever shall confess that Jesus is the Son of God, God abideth
in him, and he in God.  And we have known and have believed the charity which
God hath to us. God is charity: and he that abideth in charity abideth in God,
and God in him.  In this is the charity of God perfected with us, that we may
have confidence in the day of judgment: because as he is, we also are in this
world.  Fear is not in charity: but perfect charity casteth out fear, because
fear hath sin. And he that feareth is not perfected in charity.
\challnote{Fear is not in charity, etc\ldots\ Perfect charity, or love,
banisheth human fear, that is, the fear of men; as also all perplexing fear,
which makes men mistrust or despair of God's mercy; and that kind of servile
fear, which makes them fear the punishment of sin more than the offence offered
to God. But it no way excludes the wholesome fear of God's judgments, so often
recomended in holy writ; nor that fear and trembling, with which we are told to
work out our salvation. Phil.\ 2:12.} Let us therefore love God: because God
first hath loved us.  If any man say: I love God, and hateth his brother; he is
a liar.  For he that loveth not his brother whom he seeth, how can he love God
whom he seeth not?  And this commandment we have from God, that he who loveth
God love also his brother.


\bibleref{Gospel}{Luke 6:36--42}

At that time Jesus said to his disciples:
Be ye merciful, as your Father also is merciful.  Judge not: and you
shall not be judged. Condemn not: and you shall not be condemned. Forgive: and
you shall be forgiven.  Give: and it shall be given to you: good measure and
pressed down and shaken together and running over shall they give into your
bosom.  For with the same measure that you shall mete withal, it shall be
measured to you again.  And he spoke also to them a similitude: Can the blind
lead the blind? Do they not both fall into the ditch?  The disciple is not
above his master: but every one shall be perfect, if he be as his master.  And
why seest thou the mote in thy brother's eye: but the beam that is in thy own
eye thou considerest not?  Or how canst thou say to thy brother: Brother, let
me pull the mote out of thy eye, when thou thyself seest not the beam in thy
own eye? Hypocrite, cast first the beam out of thy own eye: and then shalt thou
see clearly to take out the mote from thy brother's eye.


\bigskip

\atitle{Corpus Christi}

\bibleref{Epistle}{1 Cor.~11:23--29}

Brethren, I have received of the Lord that which also I delivered unto you, that the
Lord Jesus, the same night in which he was betrayed, took bread, and giving
thanks, broke and said: Take ye and eat: This is my body, which shall be
delivered for you. This do for the commemoration of me.  In like manner also
the chalice, after he had supped, saying: This chalice is the new testament in
my blood. This do ye, as often as you shall drink, for the commemoration of me.
For as often as you shall eat this bread and drink the chalice, you shall shew
the death of the Lord, until he come.  Therefore, whosoever shall eat this
bread, or drink the chalice of the Lord unworthily, shall be guilty of the body
and of the blood of the Lord.  \challnote{Or drink\ldots\ Here erroneous
translators corrupted the text, by putting and drink (contrary to the original)
instead of or drink.} \challnote{Guilty of the body, etc., not discerning the
body, etc\ldots\ This demonstrates the real presence of the body and blood of
Christ, even to the unworthy communicant; who otherwise could not be guilty of
the body and blood of Christ, or justly condemned for not discerning the Lord's
body.} But let a man prove himself: and so let him eat of that bread and drink
of the chalice.  \challnote{Drink of the chalice\ldots\ This is not said by way
of command, but by way of allowance, viz., where and when it is agreeable to
the practice and discipline of the church.} For he that eateth and drinketh
unworthily eateth and drinketh judgment to himself, not discerning the body of
the Lord.

\bigskip

\bibleref{Gospel}{John 6:56--59}

At that time Jesus said to the multitudes of the Jews:
My flesh is meat indeed: and my blood is drink indeed.  He that eateth my
flesh and drinketh my blood abideth in me: and I in him.  As the living Father
hath sent me and I live by the Father: so he that eateth me, the same also
shall live by me.  This is the bread that came down from heaven. Not as your
fathers did eat manna and are dead. He that eateth this bread shall live for
ever.


%\bigskip

\atitle{2nd Sunday \break after Pentecost}

\bibleref{Epistle}{1 John 3:13--18}

Dearly-beloved: Wonder not if the world hate you.  We know that we have passed from
death to life, because we love the brethren. He that loveth not abideth in
death.  Whosoever hateth his brother is a murderer. And you know that no
murderer hath eternal life abiding in himself.  In this we have known the
charity of God, because he hath laid down his life for us: and we ought to lay
down our lives for the brethren.  He that hath the substance of this world and
shall see his brother in need and shall shut up his bowels from him: how doth
the charity of God abide in him?  My little children, let us not love in word
nor in tongue, but in deed and in truth.

\bigskip

\bibleref{Gospel}{Luke 14:16--24}

At that time Jesus spoke to the Pharisees this parable:
A certain man made a great supper and invited many.  And he
sent his servant at the hour of supper to say to them that were invited, that
they should come: for now all things are ready.  And they began all at once to
make excuse. The first said to him: I have bought a farm and I must needs go
out and see it. I pray thee, hold me excused.  And another said: I have bought
five yoke of oxen and I go to try them. I pray thee, hold me excused.  And
another said: I have married a wife; and therefore I cannot come.  And the
servant returning, told these things to his lord.  Then the master of the
house, being angry, said to his servant: Go out quickly into the streets and
lanes of the city; and bring in hither the poor and the feeble and the blind
and the lame.  And the servant said: Lord, it is done as thou hast commanded;
and yet there is room.  And the Lord said to the servant: Go out into the
highways and hedges, and compel them to come in, that my house may be filled.
But I say unto you that none of those men that were invited shall taste of my
supper.


\bigskip

\atitle{Sacred Heart of Jesus}

\bibleref{Epistle}{Eph.~3:8--12,14--19}

Brethren: To me, the least of all the saints, is given this grace, to preach
among the Gentiles the unsearchable riches of Christ:
And to enlighten all men, that they may see what is the
dispensation of the mystery which hath been hidden from eternity in God
who created all things:
That the manifold wisdom of God may be made known to the
principalities and powers in heavenly places through the church,
According to the eternal purpose which he made in Christ Jesus our
Lord:
In whom we have boldness and access with confidence by the faith
of him.
%Wherefore I pray you not to faint at my tribulations for you,
%which is your glory.
For this cause I bow my knees to the Father of our Lord Jesus
Christ,
Of whom all paternity in heaven and earth is named:
%All paternity... Or, the whole family. God is the Father, both of angels
%and men; whosoever besides is named father, is so named with
%subordination to him.
That he would grant you, according to the riches of his glory, to
be strengthened by his Spirit with might unto the inward man:
That Christ may dwell by faith in your hearts: that, being rooted
and founded in charity,
You may be able to comprehend, with all the saints, what is the
breadth and length and height and depth,
To know also the charity of Christ, which surpasseth all
knowledge: that you may be filled unto all the fulness of God.

\bigskip

\bibleref{Gospel}{John 19:31--37}

At that time: the Jews (because it was the parasceve), that the bodies
might not remain upon the cross on the sabbath day (for that was a great
sabbath day), besought Pilate that their legs might be broken: and that
they might be taken away.
The soldiers therefore came: and they broke the legs of the
first, and of the other that was crucified with him.
But after they were come to Jesus, when they saw that he was
already dead, they did not break his legs.
But one of the soldiers with a spear opened his side: and
immediately there came out blood and water.
And he that saw it hath given testimony: and his testimony is
true. And he knoweth that he saith true: that you also may believe.
For these things were done that the scripture might be fulfilled:
You shall not break a bone of him.
And again another scripture saith: They shall look on him whom
they pierced.


%\bigskip



\atitle{3rd Sunday \break after Pentecost}

\bibleref{Epistle}{1 Peter 5:6--11}

Dearly-beloved: Be you humbled under the mighty hand of God, that he may exalt you in
the time of visitation: Casting all your care upon him, for he hath care of
you.  Be sober and watch: because your adversary the devil, as a roaring lion,
goeth about seeking whom he may devour.  Whom resist ye, strong in faith:
knowing that the same affliction befalls, your brethren who are in the world.
But the God of all grace, who hath called us unto his eternal glory in Christ
Jesus, after you have suffered a little, will himself perfect you and confirm
you and establish you.  To him be glory and empire, for ever and ever. Amen.

%\columnbreak

\bibleref{Gospel}{Luke 15:1--10}

At that time, the publicans and sinners drew near unto him to hear him.  And the
Pharisees and the scribes murmured, saying: This man receiveth sinners and
eateth with them.  And he spoke to them this parable, saying: What man of you
that hath an hundred sheep, and if he shall lose one of them, doth he not leave
the ninety-nine in the desert and go after that which was lost, until he find
it?  And when he hath found it, lay it upon his shoulders, rejoicing?  And
coming home, call together his friends and neighbours, saying to them: Rejoice
with me, because I have found my sheep that was lost?  I say to you that even
so there shall be joy in heaven upon one sinner that doth penance, more than
upon ninety-nine just who need not penance.  Or what woman having ten groats,
if she lose one groat, doth not light a candle and sweep the house and seek
diligently until she find it?  And when she hath found it, call together her
friends and neighbours, saying: Rejoice with me, because I have found the groat
which I had lost.  So I say to you, there shall be joy before the angels of God
upon one sinner doing penance.
\challnote{Before the angels\ldots\ By this it is plain that the spirits in heaven have
a concern for us below, and a joy at our repentance and consequently a
knowledge of it.}


%\bigskip


%\colmnbreak

\atitle{4th Sunday \break after Pentecost}

\bibleref{Epistle}{Rom.~8:18--23}

Brethren, I reckon that the sufferings of this time are not worthy to be
compared with the glory to come that shall be revealed in us.
For the expectation of the creature waiteth for the revelation of
the sons of God.
\challnote{The expectation of the creature, etc\ldots\ He speaks of the corporeal
creation, made for the use and service of man; and, by occasion of his
sin, made subject to vanity, that is, to a perpetual instability,
tending to corruption and other defects; so that by a figure of speech
it is here said to groan and be in labour, and to long for its
deliverance, which is then to come, when sin shall reign no more; and
God shall raise the bodies and unite them to their souls never more to
separate, and to be in everlasting happiness in heaven.}
For the creature was made subject to vanity: not willingly, but by
reason of him that made it subject, in hope.
Because the creature also itself shall be delivered from the
servitude of corruption, into the liberty of the glory of the children
of God.
For we know that every creature groaneth and travaileth in pain,
even till now.
And not only it, but ourselves also, who have the firstfruits of
the Spirit: even we ourselves groan within ourselves, waiting for the
adoption of the sons of God, the redemption of our body.


\bibleref{Gospel}{Luke 5:1--11}

At that time, when the multitudes pressed upon Jesus to
hear the word of God, he stood by the lake of Genesareth,
and saw two ships standing by the lake: but the fishermen were gone
out of them and were washing their nets.
And going into one of the ships that was Simon's, he desired him to
draw back a little from the land. And sitting, he taught the multitudes
out of the ship.
Now when he had ceased to speak, he said to Simon: Launch out into
the deep and let down your nets for a draught.
And Simon answering said to him: Master, we have laboured all the
night and have taken nothing: but at thy word I will let down the net.
And when they had done this, they enclosed a very great multitude
of fishes: and their net broke.
And they beckoned to their partners that were in the other ship,
that they should come and help them. And they came and filled both the
ships, so that they were almost sinking.
Which when Simon Peter saw, he fell down at Jesus' knees, saying:
Depart from me, for I am a sinful man, O Lord.
For he was wholly astonished, and all that were with him, at the
draught of the fishes which they had taken.
And so were also James and John, the sons of Zebedee, who were
Simon's partners. And Jesus saith to Simon: Fear not: from henceforth
thou shalt catch men.
And having brought their ships to land, leaving all things, they
followed him.



%\bigskip


\atitle{5th Sunday \break after Pentecost}

\bibleref{Epistle}{1 Peter 3:8--15}

Dearly-beloved: be ye all of one mind, having compassion one of
another, being lovers of the brotherhood, merciful, modest, humble:
Not rendering evil for evil, nor railing for railing, but
contrariwise, blessing: for unto this are you called, that you may
inherit a blessing.
For he that will love life and see good days, let him refrain his
tongue from evil, and his lips that they speak no guile.
Let him decline from evil and do good: Let him seek after peace
and pursue it:
Because the eyes of the Lord are upon the just, and his ears unto
their prayers but the countenance of the Lord upon them that do evil
things.
And who is he that can hurt you, if you be zealous of good?
But if also you suffer any thing for justice' sake, blessed are
ye. And be not afraid of their fear: and be not troubled.
But sanctify the Lord Christ in your hearts, being ready always to
satisfy every one that asketh you a reason of that hope which is in you.


%\columnbreak

\bibleref{Gospel}{Matt.~5:20--24}

At that time Jesus said to his disciples:
unless your justice abound more than that of
the scribes and Pharisees, you shall not enter into the kingdom of
heaven.
\challnote{The scribes and Pharisees\ldots\ The scribes were the doctors of the law of
Moses: the Pharisees were a precise set of men, making profession of a
more exact observance of the law: and upon that account greatly esteemed
among the people.}
You have heard that it was said to them of old: Thou shalt not
kill. And whosoever shall kill, shall be in danger of the judgment.
\challnote{Shall be in danger of the judgment\ldots\ That is, shall deserve to be
punished by that lesser tribunal among the Jews, called the Judgment,
which took cognizance of such crimes.}
But I say to you, that whosoever is angry with his brother, shall
be in danger of the judgment. And whosoever shall say to his brother,
Raca, shall be in danger of the council. And whosoever shall say, Thou
fool, shall be in danger of hell fire.
\challnote{Raca\ldots\ A word expressing great indignation or contempt. Shall be in
danger of the council\ldots\ That is, shall deserve to be punished by the
highest court of judicature, called the Council, or Sanhedrim,
consisting of seventy-two persons, where the highest causes were tried
and judged, which was at Jerusalem.  Thou fool\ldots\ This was then looked
upon as a heinous injury, when uttered with contempt, spite, or malice:
and therefore is here so severely condemned. Shall be in danger of hell
fire\ldots\  literally, according to the Greek, shall deserve to be cast
into the Gehenna of fire. Which words our Saviour made use of to express
the fire and punishments of hell.}
If therefore thou offer thy gift at the altar, and there thou
remember that thy brother hath anything against thee;
Leave there thy offering before the altar, and go first to be
reconciled to thy brother, and then coming thou shalt offer thy gift.


\bigskip

\atitle{6th Sunday \break after Pentecost}

\bibleref{Epistle}{Rom.~6:3--11}

Brethren, all we who are baptized in Christ Jesus are
baptized in his death?
For we are buried together with him by baptism into death: that, as
Christ is risen from the dead by the glory of the Father, so we also may
walk in newness of life.
For if we have been planted together in the likeness of his death,
we shall be also in the likeness of his resurrection.
Knowing this, that our old man is crucified with him, that the body
of sin may be destroyed, to the end that we may serve sin no longer.
\challnote{Old man---body of sin\ldots\ Our corrupt state, subject to sin and
concupiscence, coming to us from Adam, is called our old man, as our
state, reformed in and by Christ, is called the new man. And the vices
and sins, which then ruled in us are named the body of sin.}
For he that is dead is justified from sin.
Now, if we be dead with Christ, we believe that we shall live also
together with Christ.
Knowing that Christ, rising again from the dead, dieth now no more.
Death shall no more have dominion over him.
For in that he died to sin, he died once: but in that he liveth,
he liveth unto God.
So do you also reckon that you are dead to sin, but alive unto
God, in Christ Jesus our Lord.


\bibleref{Gospel}{Mark 8:1--9}

At that time, when there was great multitude and they had
nothing to eat; calling his disciples together, he saith to them:
I have compassion on the multitude, for behold they have now been
with me three days and have nothing to eat.
And if I shall send them away fasting to their home, they will
faint in the way: for some of them came from afar off.
And his disciples answered him: From whence can any one fill them
here with bread in the wilderness?
And he asked them: How many loaves have ye? Who said: Seven.
And he commanded the people to sit down on the ground. And taking
the seven loaves, giving thanks, he broke and gave to his disciples for
to set before them. And they set them before the people.
And they had a few little fishes: and he blessed them and commanded
them to be set before them.
And they did eat and were filled: and they took up that which was
left of the fragments, seven baskets.
And they that had eaten were about four thousand. And he sent them
away.



\bigskip

%\colmnbreak

\atitle{7th Sunday \break after Pentecost}

\bibleref{Epistle}{Rom.~6:19--23}

Brethren, I speak an human thing, because of the infirmity of your flesh.
For as you have yielded your members to serve uncleanness and iniquity,
unto iniquity: so now yield your members to serve justice, unto
sanctification.
For when you were the servants of sin, you were free men to
justice.
What fruit therefore had you then in those things of which you are
now ashamed? For the end of them is death.
But now being made free from sin and become servants to God, you
have your fruit unto sanctification, and the end life everlasting.
For the wages of sin is death. But the grace of God, life
everlasting in Christ Jesus our Lord.


\bibleref{Gospel}{Matt.7:15--21}

At that time Jesus said to his disciples:
Beware of false prophets, who come to you in the clothing of
sheep, but inwardly they are ravening wolves.
By their fruits you shall know them. Do men gather grapes of
thorns, or figs of thistles?
Even so every good tree bringeth forth good fruit, and the evil
tree bringeth forth evil fruit.
A good tree cannot bring forth evil fruit, neither can an evil
tree bring forth good fruit.
Every tree that bringeth not forth good fruit, shall be cut down,
and shall be cast into the fire.
Wherefore by their fruits you shall know them.
Not every one that saith to me, Lord, Lord, shall enter into the
kingdom of heaven: but he that doth the will of my Father who is in
heaven, he shall enter into the kingdom of heaven.



\bigskip

%\colmnbreak

\atitle{8th Sunday \break after Pentecost}

\bibleref{Epistle}{Rom.~8:12--17}

Brethren, we are debtors, not to the flesh to live
according to the flesh.
For if you live according to the flesh, you shall die: but if by
the Spirit you mortify the deeds of the flesh, you shall live.
For whosoever are led by the Spirit of God, they are the sons of
God.
For you have not received the spirit of bondage again in fear: but
you have received the spirit of adoption of sons, whereby we cry: Abba
(Father).
For the Spirit himself giveth testimony to our spirit that we are
the sons of God.
\challnote{The Spirit himself, etc\ldots\ By the inward motions of divine love, and the
peace of conscience, which the children of God experience, they have a
kind of testimony of God's favour; by which they are much strengthened
in their hope of their justification and salvation; but yet not so as to
pretend to an absolute assurance: which is not usually granted in this
mortal life: during which we are taught to work out our salvation with
fear and trembling. Phil. 2.12. And that he that thinketh himself to
stand, must take heed lest he fall. 1 Cor. 10.12. See also, Rom. 11.20,
21, 22.}
And if sons, heirs also; heirs indeed of God and joint heirs with
Christ. %yet so, if we suffer with him, that we may be also glorified
%with Christ.


\bibleref{Gospel}{Luke 16:1--9}

At that time Jesus spoke to his disciples this parable:
%And he said also to his disciples: 
There was a certain rich man
who had a steward: and the same was accused unto him, that he had wasted
his goods.
And he called him and said to him: How is it that I hear this of
thee? Give an account of thy stewardship: for now thou canst be steward
no longer.
And the steward said within himself: What shall I do, because my
lord taketh away from me the stewardship? To dig I am not able; to beg I
am ashamed.
I know what I will do, that when I shall be removed from the
stewardship, they may receive me into their houses.
Therefore, calling together every one of his lord's debtors, he
said to the first: How much dost thou owe my lord?
But he said: An hundred barrels of oil. And he said to him: Take
thy bill and sit down quickly and write fifty.
Then he said to another: And how much dost thou owe? Who said: An
hundred quarters of wheat. He said to him: Take thy bill and write
eighty.
And the lord commended the unjust steward, forasmuch as he had
done wisely: for the children of this world are wiser in their
generation than the children of light.
And I say to you: Make unto you friends of the mammon of iniquity:
that when you shall fail, they may receive you into everlasting
dwellings.
\challnote{Mammon of iniquity\ldots\ Mammon signifies riches. They are here called the
mammon of iniquity, because oftentimes ill gotten, ill bestowed, or an
occasion of evil; and at the best are but worldly, and false; and not
the true riches of a Christian.  They may receive\ldots\ By this we see,
that the poor servants of God, whom we have relieved by our alms, may
hereafter, by their intercession, bring our souls to heaven.}



\bigskip

\atitle{9th Sunday \break after Pentecost}

\bibleref{Epistle}{1 Cor.~10:6--13}

Brethren, % Now these things were done in a figure of us, that we should not
let us not covet evil things, as they also coveted.
Neither become ye idolaters, as some of them, as it is written:
The people sat down to eat and drink and rose up to play.
Neither let us commit fornication, as some of them that committed
fornication: and there fell in one day three and twenty thousand.
Neither let us tempt Christ, as some of them tempted and perished
by the serpent.
Neither do you murmur, as some of them murmured and were
destroyed by the destroyer.
Now all these things happened to them in figure: and they are
written for our correction, upon whom the ends of the world are come.
\challnote{The ends of the world\ldots\ That is, the last ages.}
Wherefore, he that thinketh himself to stand, let him take heed
lest he fall.
Let no temptation take hold on you, but such as is human.  And
God is faithful, who will not suffer you to be tempted above that which
you are able: but will make also with temptation issue, that you may be
able to bear it.
\challnote{Or\ldots\ no temptation hath taken hold of you\ldots\ or come upon you as yet,
but what is human, or incident to man. Issue\ldots\ or a way to escape.}



\bibleref{Gospel}{Luke 19:41--47}

At that time, when Jesus drew near to Jerusalem, seeing the city, he wept over it, saying:
If thou also hadst known, and that in this thy day, the things
that are to thy peace: but now they are hidden from thy eyes.
For the days shall come upon thee: and thy enemies shall cast a
trench about thee and compass thee round and straiten thee on every
side,
and beat thee flat to the ground, and thy children who are in
thee. And they shall not leave in thee a stone upon a stone: because
thou hast not known the time of thy visitation.
And entering into the temple, he began to cast out them that sold
therein and them that bought.
Saying to them: It is written: My house is the house of prayer.
But you have made it a den of thieves.
And he was teaching daily in the temple. %And the chief priests
%and the scribes and the rulers of the people sought to destroy him.



%\bigskip

\atitle{10th Sunday \break after Pentecost}

\bibleref{Epistle}{1 Cor.~12:2--11}

Brethren, you know that when you were heathens, you went to dumb idols,
according as you were led.
Wherefore, I give you to understand that no man, speaking by the
Spirit of God, saith Anathema to Jesus. And no man can say The Lord
Jesus, but by the Holy Ghost.
Now there are diversities of graces, but the same Spirit.
And there are diversities of ministries but the same Lord.
And there are diversities of operations, but the same God, who
worketh all in all.
And the manifestation of the Spirit is given to every man unto
profit.
To one indeed, by the Spirit, is given the word of wisdom: and to
another, the word of knowledge, according to the same Spirit:
To another, faith in the same spirit: to another, the grace of
healing in one Spirit:
To another the working of miracles: to another, prophecy: to
another, the discerning of spirits: to another, diverse kinds of
tongues: to another, interpretation of speeches.
But all these things, one and the same Spirit worketh, dividing
to every one according as he will.


\bibleref{Gospel}{Luke 18:9--14}

At that time, Jesus spoke this parable to some who trusted in themselves as just and despised others.
%he spoke also this parable:
Two men went up into the temple to pray: the one a Pharisee and
the other a publican.
The Pharisee standing, prayed thus with himself: O God, I give
thee thanks that I am not as the rest of men, extortioners, unjust,
adulterers, as also is this publican.
I fast twice in a week: I give tithes of all that I possess.
And the publican, standing afar off, would not so much as lift up
his eyes towards heaven; but struck his breast, saying: O God, be
merciful to me a sinner.
I say to you, this man went down into his house justified rather
than the other: because every one that exalteth himself shall be
humbled: and he that humbleth himself shall be exalted.


%\bigskip

\atitle{11th Sunday \break after Pentecost}

\bibleref{Epistle}{1 Cor.~15:1--10}

Brethren, I make known unto you, brethren, the gospel which I preached
to you, which also you have received and wherein you stand.
By which also you are saved, if you hold fast after what manner I
preached unto you, unless you have believed in vain.
For I delivered unto you first of all, which I also received: how
that Christ died for our sins, according to the scriptures:
And that he was buried: and that he rose again according to the
scriptures:
And that he was seen by Cephas, and after that by the eleven.
Then was he seen by more than five hundred brethren at once: of
whom many remain until this present, and some are fallen asleep.
After that, he was seen by James: then by all the apostles.
And last of all, he was seen also by me, as by one born out of due
tine.
For I am the least of the apostles, who am not worthy to be called
an apostle, because I persecuted the church of God.
But by the grace of God, I am what I am. And his grace in me hath
not been void.%: but I have laboured more abundantly than all they. Yet
%not I, but the grace of God with me:


\bibleref{Gospel}{Mark 7:31--37}

At that time, Jesus going out of the coasts of Tyre, came by Sidon to the
sea of Galilee, through the midst the of the coasts of Decapolis.
And they bring to him one deaf and dumb: and they besought him
that he would lay his hand upon him.
And taking him from the multitude apart, he put his fingers into
his ears: and spitting, he touched his tongue.
And looking up to heaven, he groaned and said to him: Ephpheta,
which is, Be thou opened.
And immediately his ears were opened and the string of his tongue
was loosed and he spoke right.
And he charged them that they should tell no man. But the more he
charged them, so much the more a great deal did they publish it.
And so much the more did they wonder, saying: He hath done all
things well. He hath made both the deaf to hear and the dumb to speak.


%\bigskip

\atitle{12th Sunday \break after Pentecost}

\bibleref{Epistle}{2 Cor.~3:4--9}

Brethren, such confidence we have, through Christ, towards God.
Not that we are sufficient to think any thing of ourselves, as of
ourselves: but our sufficiency is from God.
Who also hath made us fit ministers of the new testament, not in
the letter but in the spirit. For the letter killeth: but the spirit
quickeneth.
\challnote{The letter\ldots\ Not rightly understood, and taken without the spirit.}
Now if the ministration of death, engraven with letters upon
stones, was glorious (so that the children of Israel could not
steadfastly behold the face of Moses, for the glory of his countenance),
which is made void:
How shall not the ministration of the spirit be rather in glory?
For if the ministration of condemnation be glory, much more the
ministration of justice aboundeth in glory.


\bibleref{Gospel}{Luke 10:23--37}

At that time Jesus said to his disciples:
%And turning to his disciples, he said: 
Blessed are the eyes that
see the things which you see.
For I say to you that many prophets and kings have desired to see
the things that you see and have not seen them; and to hear the things
that you hear and have not heard them.
And behold a certain lawyer stood up, tempting him and saying,
Master, what must I do to possess eternal life?
But he said to him: What is written in the law? How readest thou?
He answering, said: Thou shalt love the Lord thy God with thy
whole heart and with thy whole soul and with all thy strength and with
all thy mind: and thy neighbour as thyself.
And he said to him: Thou hast answered right. This do: and thou
shalt live.
But he willing to justify himself, said to Jesus: And who is my
neighbour?
And Jesus answering, said: A certain man went down from Jerusalem
to Jericho and fell among robbers, who also stripped him and having
wounded him went away, leaving him half dead.
And it chanced, that a certain priest went down the same way: and
seeing him, passed by.
In like manner also a Levite, when he was near the place and saw
him, passed by.
But a certain Samaritan, being on his journey, came near him: and
seeing him, was moved with compassion:
And going up to him, bound up his wounds, pouring in oil and
wine: and setting him upon his own beast, brought him to an inn and took
care of him.
And the next day he took out two pence and gave to the host and
said: Take care of him; and whatsoever thou shalt spend over and above,
I, at my return, will repay thee.
Which of these three, in thy opinion, was neighbour to him that
fell among the robbers?
But he said: He that shewed mercy to him. And Jesus said to him:
Go, and do thou in like manner.




%\bigskip

\atitle{13th Sunday \break after Pentecost}

\bibleref{Epistle}{Gal.~3:16--22}

Brethren, to Abraham were the promises made and to his seed. He saith not:
And to his seeds as of many. But as of one: And to thy seed, which is
Christ.
Now this I say: that the testament which was confirmed by God, the
law which was made after four hundred and thirty years doth not
disannul, to make the promise of no effect.
For if the inheritance be of the law, it is no more of promise.
But God gave it to Abraham by promise.
Why then was the law? It was set because of transgressions, until
the seed should come to whom he made the promise, being ordained by
angels in the hand of a mediator.
\challnote{Because of transgressions\ldots\ To restrain them from sin, by fear and
threats. Ordained by angels\ldots\ The law was delivered by angels, speaking
in the name and person of God to Moses, who was the mediator, on this
occasion, between God and the people.}
Now a mediator is not of one: but God is one.
Was the law then against the promises of God: God forbid!  For if
there had been a law given which could give life, verily justice should
have been by the law.
But the scripture hath concluded all under sin, that the promise,
by the faith of Jesus Christ, might be given to them that believe.
\challnote{Hath concluded all under sin\ldots\ that is, hath declared all to be under
sin, from which they could not be delivered but by faith in Jesus
Christ, the promised seed.}


\bibleref{Gospel}{Luke 17:11--19}

At that time, as Jesus was going to Jerusalem, he passed
through the midst of Samaria and Galilee.
And as he entered into a certain town, there met him ten men that
were lepers, who stood afar off.
And lifted up their voice, saying: Jesus, Master, have mercy on
us.
Whom when he saw, he said: Go, shew yourselves to the priests.
And it came to pass, as they went, they were made clean.
And one of them, when he saw that he was made clean, went back,
with a loud voice glorifying God.
And he fell on his face before his feet, giving thanks.  And this
was a Samaritan.
And Jesus answering, said: Were not ten made clean? And where are
the nine?
There is no one found to return and give glory to God, but this
stranger.
And he said to him: Arise, go thy way; for thy faith hath made
thee whole.

%\columnbreak

%\bigskip

\atitle{14th Sunday \break after Pentecost}

\bibleref{Epistle}{Gal.~5:16--24}

Brethren: Walk in the spirit, and you shall not fulfill the
lusts of the flesh.
For the flesh lusteth against the spirit: and the spirit against
the flesh: For these are contrary one to another: so that you do not the
things that you would.
But if you are led by the spirit, you are not under the law.
Now the works of the flesh are manifest: which are fornication,
uncleanness, immodesty, luxury,
idolatry, witchcrafts, enmities, contentions, emulations, wraths,
quarrels, dissensions, sects,
envies, murders, drunkenness, revellings, and such like.  Of the
which I foretell you, as I have foretold to you, that they who do such
things shall not obtain the kingdom of God.
But the fruit of the Spirit is, charity, joy, peace, patience,
benignity, goodness, longanimity,
mildness, faith, modesty, continency, chastity. Against such there
is no law.
And they that are Christ's have crucified their flesh, with the
vices and concupiscences.


\bibleref{Gospel}{Matt.~6:24--33}

At that time Jesus said to his disciples:
No man can serve two masters. For either he will hate the one, and
love the other: or he will sustain the one, and despise the other. You
cannot serve God and mammon.
\challnote{Mammon\ldots\ That is, riches, worldly interest.}
Therefore I say to you, be not solicitous for your life, what you
shall eat, nor for your body, what you shall put on.  Is not the life
more than the meat: and the body more than the raiment?
Behold the birds of the air, for they neither sow, nor do they
reap, nor gather into barns: and your heavenly Father feedeth them. Are
not you of much more value than they?
And which of you by taking thought, can add to his stature one
cubit?
And for raiment why are you solicitous? Consider the lilies of the
field, how they grow: they labour not, neither do they spin.
But I say to you, that not even Solomon in all his glory was
arrayed as one of these.
And if the grass of the field, which is to day, and to morrow is
cast into the oven, God doth so clothe: how much more you, O ye of
little faith?
Be not solicitous therefore, saying: What shall we eat: or what
shall we drink, or wherewith shall we be clothed?
For after all these things do the heathens seek. For your Father
knoweth that you have need of all these things.
Seek ye therefore first the kingdom of God, and his justice, and
all these things shall be added unto you.


%\bigskip

\atitle{15th Sunday \break after Pentecost}

\bibleref{Epistle}{Gal.~5:25--6:10}

Brethren, if we live in the Spirit, let us also walk in the Spirit.
Let us not be made desirous of vain glory, provoking one another,
envying one another.
Brethren, and if a man be overtaken in any fault, you, who are
spiritual, instruct such a one in the spirit of meekness, considering
thyself, lest thou also be tempted.
Bear ye one another's burdens: and so you shall fulfil the law of
Christ.
For if any man think himself to be some thing, whereas he is
nothing, he deceiveth himself.
But let every one prove his own work: and so he shall have glory in
himself only and not in another.
For every one shall bear his own burden.
And let him that is instructed in the word communicate to him that
instructeth him, in all good things.
Be not deceived: God is not mocked.
For what things a man shall sow, those also shall he reap.  For he
that soweth in his flesh of the flesh also shall reap corruption. But he
that soweth in the spirit of the spirit shall reap life everlasting.
And in doing good, let us not fail. For in due time we shall reap,
not failing.
Therefore, whilst we have time, let us work good to all men, but
especially to those who are of the household of the faith.


\bibleref{Gospel}{Luke 7:11--16}

At that time Jesus went into a city that is
called Naim: and there went with him his disciples and a great
multitude.
And when he came nigh to the gate of the city, behold a dead man
was carried out, the only son of his mother: and she was a widow. And a
great multitude of the city was with her.
Whom when the Lord had seen, being moved with mercy towards her,
he said to her: Weep not.
And he came near and touched the bier. And they that carried it
stood still. And he said: Young man, I say to thee, arise.
And he that was dead sat up and begun to speak. And he gave him to
his mother.
And there came a fear upon them all: and they glorified God
saying: A great prophet is risen up among us: and, God hath visited his
people.


%\bigskip

%\columnbreak

\atitle{16th Sunday \break after Pentecost}

\bibleref{Epistle}{Eph.~3:13--21}

Brethren, I pray you not to faint at my tribulations for you,
which is your glory.
For this cause I bow my knees to the Father of our Lord Jesus
Christ,
of whom all paternity in heaven and earth is named:
\challnote{All paternity\ldots\ Or, the whole family. God is the Father, both of angels
and men; whosoever besides is named father, is so named with
subordination to him.}
That he would grant you, according to the riches of his glory, to
be strengthened by his Spirit with might unto the inward man:
That Christ may dwell by faith in your hearts: that, being rooted
and founded in charity,
you may be able to comprehend, with all the saints, what is the
breadth and length and height and depth,
to know also the charity of Christ, which surpasseth all
knowledge: that you may be filled unto all the fulness of God.
Now to him who is able to do all things more abundantly than we
desire or understand, according to the power that worketh in us:
To him be glory in the church and in Christ Jesus, unto all
generations, world without end. Amen.


\bibleref{Gospel}{Luke 14:1--11}

At that time, when Jesus went into the house of one of the
Pharisees, on the sabbath day, that they watched him.
And behold, there was a certain man before him that had the
dropsy.
And Jesus answering, spoke to the lawyers and Pharisees, saying:
Is it lawful to heal on the sabbath day?
But they held their peace. But he taking him, healed him and sent
him away.
And answering them, he said: Which of you shall have an ass or an
ox fall into a pit and will not immediately draw him out, on the sabbath
day?
And they could not answer him to these things.
And he spoke a parable also to them that were invited, marking how
they chose the first seats at the table, saying to them:
When thou art invited to a wedding, sit not down in the first
place, lest perhaps one more honourable than thou be invited by him:
And he that invited thee and him, come and say to thee: Give this
man place. And then thou begin with shame to take the lowest place.
But when thou art invited, go, sit down in the lowest place; that
when he who invited thee cometh, he may say to thee: Friend, go up
higher. Then shalt thou have glory before them that sit at table with
thee.
Because every one that exalteth himself shall be humbled: and he
that humbleth himself shall be exalted.



\bigskip

%\colmnbreak

\atitle{17th Sunday \break after Pentecost}

\bibleref{Epistle}{Eph.~4:1--6}

Brethren: I, a prisoner in the Lord, beseech you that you walk
worthy of the vocation in which you are called:
With all humility and mildness, with patience, supporting one
another in charity.
Careful to keep the unity of the Spirit in the bond of peace.
One body and one Spirit: as you are called in one hope of your
calling.
One Lord, one faith, one baptism.
One God and Father of all, who is above all, and through all, and
in us all.

%\columnbreak

\bibleref{Gospel}{Matt.~22:34--46}

At that time, the Pharisees, % hearing that he had silenced the Sadducees,
came to Jesus, %together.
and one of them, a doctor of the law, asked him, tempting him:
Master, which is the great commandment in the law?
Jesus said to him: Thou shalt love the Lord thy God with thy
whole heart and with thy whole soul and with thy whole mind.
This is the greatest and the first commandment.
And the second is like to this: Thou shalt love thy neighbour as
thyself.
On these two commandments dependeth the whole law and the
prophets.
And the Pharisees being gathered together, Jesus asked them,
saying: What think you of Christ? Whose son is he? They say to
him: David's.
He saith to them: How then doth David in spirit call him Lord,
saying:
The Lord said to my Lord: Sit on my right hand, until I make thy
enemies thy footstool?
If David then call him Lord, how is he his son?
And no man was able to answer him a word: neither durst any man
from that day forth ask him any more questions.


%\bigskip


\atitle{18th Sunday \break after Pentecost}

\bibleref{Epistle}{1 Cor.~1:4--8}

Brethren, I give thanks to my God always for you, for the grace of God that
is given you in Christ Jesus:
That in all things you are made rich in him, in all utterance and
in all knowledge;
As the testimony of Christ was confirmed in you,
so that nothing is wanting to you in any grace, waiting for the
manifestation of our Lord Jesus Christ.
Who also will confirm you unto the end without crime, in the days
of the coming of our Lord Jesus Christ.


\bibleref{Gospel}{Matt.~9:1--8}

At that time, Jesus entering into a boat, passed over the water and came into
his own city.
And behold they brought to him one sick of the palsy lying in a
bed. And Jesus, seeing their faith, said to the man sick of the palsy:
Be of good heart, son, thy sins are forgiven thee.
And behold some of the scribes said within themselves: He
blasphemeth.
And Jesus seeing their thoughts, said: Why do you think evil in
your hearts?
Whether is easier, to say, Thy sins are forgiven thee: or to say,
Arise, and walk?
But that you may know that the Son of man hath power on earth to
forgive sins, (then said he to the man sick of the palsy,) Arise, take
up thy bed, and go into thy house.
And he arose, and went into his house.
And the multitude seeing it, feared, and glorified God that gave
such power to men.


%\bigskip

\atitle{19th Sunday \break after Pentecost}

\bibleref{Epistle}{Eph.~4:23--28}

Brethren, be renewed in spirit of your mind:
And put on the new man, who according to God is created in justice
and holiness of truth.
Wherefore, putting away lying, speak ye the truth, every man with
his neighbour. For we are members one of another.
Be angry: and sin not. Let not the sun go down upon your anger.
Give not place to the devil.
He that stole, let him now steal no more: but rather let him
labour, working with his hands the thing which is good, that he may have
something to give to him that suffereth need.


\bibleref{Gospel}{Matt.~22:1--14}

At that time, Jesus spoke to the chief priests and the Pharisees in parables, saying:
The kingdom of heaven is likened to a king who made a marriage for
his son.
And he sent his servants to call them that were invited to the
marriage: and they would not come.
Again he sent other servants, saying: Tell them that were invited,
Behold, I have prepared my dinner: my beeves and fatlings are killed,
and all things are ready. Come ye to the marriage.
But they neglected and went their ways, one to his farm and
another to his merchandise.
And the rest laid hands on his servants and, having treated them
contumeliously, put them to death.
But when the king had heard of it, he was angry: and sending his
armies, he destroyed those murderers and burnt their city.
Then he saith to his servants: The marriage indeed is ready; but
they that were invited were not worthy.
Go ye therefore into the highways; and as many as you shall find,
call to the marriage.
And his servants going forth into the ways, gathered together all
that they found, both bad and good: and the marriage was filled with
guests.
And the king went in to see the guests: and he saw there a man
who had not on a wedding garment.
And he saith to him: Friend, how camest thou in hither not having
on a wedding garment? But he was silent.
Then the king said to the waiters: Bind his hands and feet, and
cast him into the exterior darkness. There shall be weeping and gnashing
of teeth.
For many are called, but few are chosen.


%\bigskip

\atitle{20th Sunday \break after Pentecost}

\bibleref{Epistle}{Eph.~5:15--21}

Brethren, see how you walk circumspectly: not as
unwise,
but as wise: redeeming the time, because the days are evil.
Wherefore, become not unwise: but understanding what is the will
of God.
And be not drunk with wine, wherein is luxury: but be ye filled
with the Holy Spirit,
speaking to yourselves in psalms and hymns and spiritual
canticles, singing and making melody in your hearts to the Lord:
Giving thanks always for all things, in the name of our Lord Jesus
Christ, to God and the Father:
being subject one to another, in the fear of Christ.


\bibleref{Gospel}{John 4:46--53}

At that time, % He came again therefore into Cana of Galilee, where he made the
%water wine. And 
there was a certain ruler, whose son was sick at
Capharnaum.
He having heard that Jesus was come from Judea into Galilee, sent
to him and prayed him to come down and heal his son: for he was at the
point of death.
Jesus therefore said to him: Unless you see signs and wonders, you
believe not.
The ruler saith to him: Lord, come down before that my son die.
Jesus saith to him: Go thy way. Thy son liveth. The man believed
the word which Jesus said to him and went his way.
And as he was going down, his servants met him: and they brought
word, saying, that his son lived.
He asked therefore of them the hour wherein he grew better.  And
they said to him: Yesterday at the seventh hour, the fever left him.
The father therefore knew that it was at the same hour that Jesus
said to him: Thy son liveth. And himself believed, and his whole house.


%\bigskip

\atitle{21st Sunday \break after Pentecost}

\bibleref{Epistle}{Eph.~6:10--17}

Brethren, be strengthened in the Lord and in the might of
his power.
Put you on the armour of God, that you may be able to stand
against the deceits of the devil.
For our wrestling is not against flesh and blood; but against
principalities and powers, against the rulers of the world of this
darkness, against the spirits of wickedness in the high places.
\challnote{High places, or heavenly places\ldots\ That is to say, in the air, the
lowest of the celestial regions; in which God permits these wicked
spirits or fallen angels to wander.}
Therefore, take unto you the armour of God, that you may be able
to resist in the evil day and to stand in all things perfect.
Stand therefore, having your loins girt about with truth and
having on the breastplate of justice:
And your feet shod with the preparation of the gospel of peace.
In all things taking the shield of faith, wherewith you may be
able to extinguish all the fiery darts of the most wicked one.
And take unto you the helmet of salvation and the sword of the
Spirit (which is the word of God).


\bibleref{Gospel}{Matt.~18:23--35}

At that time Jesus spoke to his disciples this parable:
The kingdom of heaven likened to a king, who would
take an account of his servants.
And when he had begun to take the account, one as brought to him,
that owed him ten thousand talents.
\challnote{Talents\ldots\ A talent was seven hundred and fifty ounces of silver, which
at the rate of five shillings to the ounce is a hundred and eighty-seven
pounds ten shillings sterling.}
And as he had not wherewith to pay it, his lord commanded that he
should be sold, and his wife and children, and all that he had, and
payment to be made.
But that servant falling down, besought him, saying: Have
patience with me, and I will pay thee all.
And the lord of that servant being moved with pity, let him go
and forgave him the debt.
But when that servant was gone out, he found one of his fellow-
servants that owed him an hundred pence: and laying hold of him, he
throttled him, saying: Pay what thou owest.
\challnote{Pence\ldots\ The Roman penny was the eighth part of an ounce, that is, about
sevenpence half-penny English.}
And his fellow-servant falling down, besought him, saying: Have
patience with me, and I will pay thee all.
And he would not: but went and cast him into prison, till he paid
the debt.
Now his fellow servants seeing what was done, were very much
grieved, and they came, and told their lord all that was done.
Then his lord called him: and said to him: Thou wicked servant, I
forgave thee all the debt, because thou besoughtest me:
Shouldst not thou then have had compassion also on thy fellow
servant, even as I had compassion on thee?
And his lord being angry, delivered him to the torturers until he
paid all the debt.
So also shall my heavenly Father do to you, if you forgive not
every one his brother from your hearts.

%\columnbreak

\bigskip


\atitle{22nd Sunday \break after Pentecost}

\bibleref{Epistle}{Phil.~1:6--11}

Brethren, we are confident in the Lord Jesus that he, who hath begun a good
work in you, will perfect it unto the day of Christ Jesus.
As it is meet for me to think this for you all, for that I have you
in my heart; and that, in my bands and in the defence and confirmation
of the gospel, you all are partakers of my joy.
For God is my witness how I long after you all in the bowels of
Jesus Christ.
And this I pray: That your charity may more and more abound in
knowledge and in all understanding:
That you may approve the better things: that you may be sincere
and without offence unto the day of Christ:
Filled with the fruit of justice, through Jesus Christ, unto the
glory and praise of God.


\bibleref{Gospel}{Matt.~22:15--21}

At that time, the Pharisees went and consulted among themselves how to
ensnare Jesus in his speech.
And they sent to him their disciples with the Herodians, saying:
Master, we know that thou art a true speaker and teachest the way of God
in truth. Neither carest thou for any man: for thou dost not regard the
person of men.
\challnote{The Herodians\ldots\ That is, some that belonged to Herod, and that joined
with him in standing up for the necessity of paying tribute to Caesar,
that is, to the Roman emperor. Some are of opinion that there was a sect
among the Jews called Herodians, from their maintaining that Herod was
the Messias.}
Tell us therefore what dost thou think? Is it lawful to give
tribute to Caesar, or not?
But Jesus knowing their wickedness, said: Why do you tempt me, ye
hypocrites?
Shew me the coin of the tribute. And they offered him a penny.
And Jesus saith to them: Whose image and inscription is this?
They say to him: Caesar's. Then he saith to them: Render
therefore to Caesar the things that are Caesar's; and to God, the things
that are God's.

\bigskip


\atitle{23rd Sunday \break after Pentecost}

\bibleref{Epistle}{Phil.~3:17--4:3}

Brethren, be ye followers of me, and observe them who walk so as
you have our model.
For many walk, of whom I have told you often (and now tell you
weeping) that they are enemies of the cross of Christ:
Whose end is destruction: whose God is their belly: and whose
glory is in their shame: who mind earthly things.
But our conversation is in heaven: from whence also we look for
the Saviour, our Lord Jesus Christ,
who will reform the body of our lowness, made like to the body of
his glory, according to the operation whereby also he is able to subdue
all things unto himself.
Therefore my dearly beloved brethren and most desired, my joy and
my crown: so stand fast in the Lord, my dearly beloved.
I beg of Evodia and I beseech Syntyche to be of one mind in the
Lord.
And I entreat thee also, my sincere companion, help those women who
have laboured with me in the gospel, with Clement and the rest of my
fellow labourers, whose names are in the book of life.


\bibleref{Gospel}{Matt.~9:18--26}

At that time, as Jesus was speaking these things to the multitudes, behold a certain ruler
came up, and adored him, saying: Lord, my daughter is even now dead; but
come, lay thy hand upon her, and she shall live.
And Jesus rising up followed him, with his disciples.
And behold a woman who was troubled with an issue of blood twelve
years, came behind him, and touched the hem of his garment.
For she said within herself: If I shall touch only his garment, I
shall be healed.
But Jesus turning and seeing her, said: Be of good heart,
daughter, thy faith hath made thee whole. And the woman was made whole
from that hour.
And when Jesus was come into the house of the ruler, and saw the
minstrels and the multitude making a rout,
he said: Give place, for the girl is not dead, but sleepeth. And
they laughed him to scorn.
And when the multitude was put forth, he went in, and took her by
the hand. And the maid arose.
And the fame hereof went abroad into all that country.

\bigskip

%\columnbreak

\atitle{24th Sunday \break after Pentecost}

\bibleref{Epistle}{Col.~1:9--14}

Brethren, % Therefore we also, from the day that we heard it, 
we cease not to pray
for you and to beg that you may be filled with the knowledge of his
will, in all wisdom and spiritual understanding:
That you may walk worthy of God, in all things pleasing; being
fruitful in every good work and increasing in the knowledge of God:
Strengthened with all might according to the power of his glory,
in all patience and longsuffering with joy,
giving thanks to God the Father, who hath made us worthy to be
partakers of the lot of the saints in light:
Who hath delivered us from the power of darkness and hath
translated us into the kingdom of the Son of his love,
in whom we have redemption through his blood, the remission of
sins.


\bibleref{Gospel}{Matt.~24:15--35}

At that time Jesus said to his disciples:
When therefore you shall see the abomination of desolation, which
was spoken of by Daniel the prophet, standing in the holy place: he that
readeth let him understand.
Then they that are in Judea, let them flee to the mountains:
And he that is on the housetop, let him not come down to take any
thing out of his house:
And he that is in the field, let him not go back to take his
coat.
And woe to them that are with child and that give suck in those
days.
But pray that your flight be not in the winter or on the sabbath.
For there shall be then great tribulation, such as hath not been
from the beginning of the world until now, neither shall be.
And unless those days had been shortened, no flesh should be
saved: but for the sake of the elect those days shall be shortened.
Then if any man shall say to you, Lo here is Christ, or there: do
not believe him.
For there shall arise false Christs and false prophets and shall
shew great signs and wonders, insomuch as to deceive (if possible) even
the elect.
Behold I have told it to you, beforehand.
If therefore they shall say to you, Behold he is in the desert:
go ye not out. Behold he is in the closets: believe it not.
For as lightning cometh out of the east and appeareth even into
the west: so shall also the coming of the Son of man be.
Wheresoever the body shall be, there shall the eagles also be
gathered together.
\challnote{Wheresoever, etc\ldots\ The coming of Christ shall be sudden, and manifest
to all the world, like lightning: and wheresoever he shall come, thither
shall all mankind be gathered to him, as eagles are gathered about a
dead body.}
And immediately after the tribulation of those days, the sun
shall be darkened and the moon shall not give her light and the stars
shall fall from heaven and the powers of heaven shall be moved.
\challnote{The stars\ldots\ Or flaming meteors resembling stars.}
And then shall appear the sign of the Son of man in heaven.  And
then shall all tribes of the earth mourn: and they shall see the Son of
man coming in the clouds of heaven with much power and majesty.
\challnote{The sign, etc\ldots\ The cross of Christ.}
And he shall send his angels with a trumpet and a great voice:
and they shall gather together his elect from the four winds, from the
farthest parts of the heavens to the utmost bounds of them.
And from the fig tree learn a parable: When the branch thereof is
now tender and the leaves come forth, you know that summer is nigh.
So you also, when you shall see all these things, know ye that it
is nigh, even at the doors.
Amen I say to you that this generation shall not pass till all
these things be done.
Heaven and earth shall pass away: but my words shall not pass away.
\challnote{Shall pass\ldots\ Because they shall be changed at the end of the world into
a new heaven and new earth.}




