\atitle{Psalm 102}

%\vskip-\baselineskip

\begin{psalmmode}
Bless the Lord, O my soul: and let all
    that is within me bless His holy name.

   Bless the Lord, O my soul, and never forget all He hath
    done for thee.

   Who forgiveth all thy iniquities: who healeth all thy
    diseases.

   Who redeemeth thy life from destruction: who crowneth thee
    with mercy and compassion.

   Who satisfieth thy desire with good things: thy youth
    shall be renewed like the eagle's.

   The Lord doth mercies, and judgment for all that suffer
    wrong.

   He hath made his ways known to Moses: his wills to the
    children of Israel.

   The Lord is compassionate and merciful: long suffering and
    plenteous in mercy.

   He will not always be angry: nor will He threaten for
    ever.

  He hath not dealt with us according to our sins: nor
    rewarded us according to our iniquities.

  For according to the height of the heavens above the earth:
    He hath strengthened His mercy towards them that fear Him.

  As far as the east is from the west, so far hath He
    removed our iniquities from us.

  As a father hath compassion on his children, so hath the
    Lord compassion on them that fear him:

  for he knoweth our frame. He remembereth that we are dust:

  man's days are as grass, as the flower of the field so
    shall he flourish.

  For the spirit shall pass in him, and he shall not be: and
    he shall know his place no more.

  But the mercy of the Lord is from eternity and unto
    eternity upon them that fear Him: And His justice unto their
    children's children,

  to such as keep his covenant, and are mindful of His
    commandments to do them.

  The Lord hath prepared His throne in heaven: and His
    kingdom shall rule over all.

  Bless the Lord, all ye His angels: you that are mighty in
    strength, and execute His word, hearkening to the voice of
    His orders.

  Bless the Lord, all ye His hosts: you ministers of His
    that do His will.

  Bless the Lord, all His works: in every place of His
    dominion, O my soul, bless thou the Lord.

\end{psalmmode}

