\documentclass[12pt,a4paper]{memoir}
\usepackage{fontspec}
\setmainfont{Calluna}

\usepackage[autocompile]{gregoriotex}
\setlength{\trimtop}{0pt}
\setlength{\trimedge}{0pt}
\settypeblocksize{240mm}{135mm}{*} % Was 101mm in a5
\setulmargins{*}{*}{1.2}
\setlrmargins{*}{*}{3}
\setheadfoot{\onelineskip}{2\onelineskip}
\setheaderspaces{*}{.8\onelineskip}{*}
\setmarginnotes{7pt}{125pt}{7pt}
\checkandfixthelayout


\tolerance=1000
\pretolerance=800

\title{Chant Book}

\author{Easter Camp}

\begin{document}

\maketitle

\tableofcontents*

\newpage

\section{Introit}

\subsection{Tuesday:}
\marginpar{He gave them the water of wholesome
wisdom to drink, alleluia; and she shall be
made strong in them, and shall not be
moved, alleluia: And she shall exalt them
forever, allelúia, allelúia. Ps. Give glory to
the Lord, and call upon his name: declare
his deeds among the Gentiles.}
\gregorioscore{I-tuesday}

\subsection{Wednesday:}

\marginpar{Come, ye blessed of my Father, receive the
kingdom, alleluia, which was prepared for
you from the foundation of the world,
alleluia, alleluia, alleluia. Ps. Sing ye to the
Lord a new canticle: sing to the Lord, all
the earth.}
\gregorioscore{I-wednesday}

\subsection{Thursday:}

\marginpar{They praised with one accord Thy victorious hand, O Lord, alleluia; for wisdom
opened the mouth of the dumb, and made
the tongues of infants eloquent, alleluia,
alleluia. Ps. Sing ye to the Lord a new canticle; for He hath done wonderful things.}

\gregorioscore{I-thursday}

\subsection{Friday:}

\marginpar{The Lord brought them out in hope, alleluia, and the sea overwhelmed their enemies, alleluia, alleluia, alleluia. Ps. Attend,
O my people, to my law: incline your ears
to the words of my mouth.}
\gregorioscore{I-friday}

\subsection{Saturday:}

\marginpar{The Lord brought forth his people with
joy, alleluia, and his chosen with gladness,
alleluia, alleluia. Ps. Give glory to the Lord,
and call upon his name: declare his deeds
among the Gentiles.}
\gregorioscore{I-saturday}


\newpage

\section{Kyrie}

\marginpar{Lord have mercy, Christ have mercy, Lord have mercy.}
\gregorioscore{ky--kyrie_i--solesmes}

\section{Gloria}

\marginpar{Glory to God in the highest, and on earth peace to men of good will.
We praise you, we bless you, we adore you, we glorify you,
we give you thanks for your great glory, Lord God, heavenly King,
O God, almighty Father.
Lord Jesus Christ, only begotten Son,
Lord God, Lamb of God, Son of the Father,
you take away the sins of the world, have mercy on us;
you take away the sins of the world, receive our prayer;
you are seated at the right hand of the Father, have mercy on us.
For you alone are the Holy One,
you alone are the Lord,
you alone are the Most High, Jesus Christ,
with the Holy Spirit,
in the glory of God the Father.
Amen.}
\gregorioscore{ky--gloria_i--solesmes}

\newpage

\section{Gradual}

\marginpar{This is the day that the Lord hath made. Let us rejoice and be glad in it.}
\gregorioscore{an--haec_dies--solesmes_1961}

\gresetinitiallines{0}

\subsection{Tuesday:}
\marginpar{Let
them say so that have been redeemed by
the Lord, whom he hath redeemed from
the hand of the enemy: and gathered out
of the nations.}
\gregorioscore{G-tuesday}

\subsection{Wednesday:}
\marginpar{The
right hand of the Lord hath wrought
strength: the right hand of the Lord hath
exulted me.}
\gregorioscore{G-wednesday}

\subsection{Thursday:}
\marginpar{The
stone which the builders rejected is become the head of the corner: this is the
work of the Lord, and it is wonderful in
our eyes.}
\gregorioscore{G-thursday}

\eject 

\subsection{Friday:}
\marginpar{Blessed be he that cometh in the name of
the Lord. The Lord is God, and he hath
shone upon us.}
\gregorioscore{G-friday}

%\newpage

\bigskip

\section{Alleluia}

\gresetinitiallines{1}

\gregorioscore{alleluia}

\gresetinitiallines{0}

\subsection{Tuesday:}
\marginpar{The Lord is risen from
the sepulcher, He, who hangeth on the
tree.}
\gregorioscore{A-tuesday}

\subsection{Wednesday:}
\marginpar{The Lord is risen indeed, and hath appeared to Peter.}
\gregorioscore{A-wednesday}

\subsection{Thursday:}
\marginpar{Who created all things, and Who had compassion
upon the human race.}
\gregorioscore{A-thursday}

\subsection{Friday:}
\marginpar{Say ye among the Gentiles, the Lord hath reigned from a tree.}
\gregorioscore{A-friday}

\subsection{Saturday:}
\marginpar{This is the day which the
Lord hath made: let us be glad and rejoice
therein.}
\gregorioscore{A-saturday}

\section{Second Alleluia for Saturday}

\gresetinitiallines{1}

\gregorioscore{alleluia2}

\gresetinitiallines{0}
\marginpar{Praise the Lord, ye children:
praise ye the name of the Lord.}
\gregorioscore{A2-saturday}

\newpage

\section{Sequence}

\gresetinitiallines{1}

\marginpar{Christians! to the Paschal Victim offer your
thankful praises.
The Lamb the sheep redeemeth: Christ, who
only is sinless, reconcileth sinners to the
Father.
Death and life contended in that conflict
stupendous: the Prince of Life, who died,
deathless reigneth.
Speak, Mary, declaring what thou sawest
wayfaring.
"The tomb of Christ who now liveth: and
likewise the glory of the Risen.
Bright Angels attesting, the shroud and napkin resting.
Yea, Christ my hope is arisen: to Galilee He
goeth before you."
We know that Christ is risen, henceforth
ever living: Have mercy, Victor King,
pardon giving. Amen. Alleluia.}
\gregorioscore{se--victimae_paschali--simplex}

\newpage

\section{Credo}

\marginpar{I believe in One God, the Father Almighty, maker of heaven and earth,
of all things visible and invisible.
I believe in one Lord Jesus Christ,
the Only Begotten Son of God,
born of the Father before all ages.
God from God, Light from Light,
true God from true God,
begotten, not made, consubstantial with the Father;
through him all things were made.}

\marginpar{For us men and for our salvation
he came down from heaven,
and by the Holy Spirit was incarnate of the Virgin Mary,
and became man.
For our sake he was crucified under Pontius Pilate,
he suffered death and was buried,
and rose again on the third day
in accordance with the Scriptures.
He ascended into heaven
and is seated at the right hand of the Father.
He will come again in glory
to judge the living and the dead
and his kingdom will have no end.}
\gregorioscore{ky--credo_i--solesmes}

\eject

\marginpar{I believe in the Holy Spirit, the Lord, the giver of life,
who proceeds from the Father and the Son,
who with the Father and the Son is adored and glorified,
who has spoken through the prophets.
I believe in one, holy, catholic and apostolic Church.
I confess one Baptism for the forgiveness of sins
and I look forward to the resurrection of the dead
and the life of the world to come. Amen.}
\gresetinitiallines{0}
\gregorioscore{ky--credo_i--solesmes2}

\newpage

\section{Offertory}

\gresetinitiallines{1}
\subsection{Tuesday:}
\marginpar{And the Lord thundered from heaven, and
the highest gave his voice: Then the fountains of waters appeared, alleluia.}
\gregorioscore{O-tuesday}

\subsection{Wednesday:}
\marginpar{The Lord opened the doors of heaven, and
rained down manna upon them to eat: He
gave them the bread of heaven: man ate
the bread of angels: alleluia.}
\gregorioscore{O-wednesday}

\subsection{Thursday:}
\marginpar{In the day of your solemnity, saith the
Lord, I will bring you into a land that
floweth with milk and honey, alleluia.}
\gregorioscore{O-thursday}

\subsection{Friday:}
\marginpar{This day shall be for a memorial to you:
alleluia: and you shall keep it a feast to the
Lord in your generations with an everlasting observance, alleluia, alleluia, alleluia.}
\gregorioscore{O-friday}

%\newpage

\subsection{Saturday:}
\marginpar{Blessed be he that cometh in the name
Lord. We have blessed you out of the
house of the Lord. The Lord is God, and
he hath shone upon us, alleluia, alleluia.}
\gregorioscore{O-saturday}

\section{Preface}

\subsection{The Solemn Tone:}

\gregorioscore{or--toni_praefationum_(1._tonus_solemnis)--solesmes}

\subsection{Or the Even More Solemn Tone:}

\gregorioscore{or--per_omnia_saecula_saeculorum--solesmes_1961}
\section{Sanctus}
\marginpar{Holy, holy, holy Lord God of Hosts. Heaven and earth are full of your glory. Hosanna in the highest.
Blessed is He who comes in the name of the Lord. Hosannas in the highest.}
\gregorioscore{ky--sanctus_i--solesmes}

\section{Agnus Dei}
\marginpar{Lamb of God,
Who takest away the sins of the world.
Have mercy on us.
Lamb of God,
Who takest away the sins of the world.
Have mercy on us.
Lamb of God, Who takest away the sins of the world.
Grant us peace.}
\gregorioscore{ky--agnus_i--solesmes}

\newpage

\section{Communion}

\subsection{Tuesday:}
\marginpar{If you be risen with Christ, seek the things
that are above; where Christ is sitting at
the right hand of God: alleluia. Mind the
things that are above, alleluia.}
\gregorioscore{C-tuesday}

\subsection{Wednesday:}
\marginpar{Christ rising again from the dead, dieth
now no more, death shall no more have
dominion over him, alleluia, alleluia.}
\gregorioscore{C-wednesday}

\subsection{Thursday:}
\marginpar{Purchased people, declare His virtues, alleluia: Who hath called you out of darkness
into His admirable light, alleluia.}
\gregorioscore{C-thursday}

\subsection{Friday:}
\marginpar{All power is given to me in heaven and in
earth. Going therefore, teach ye all nations;
baptizing them in the name of the Father,
and of the Son, and of the Holy Ghost,
alleluia, alleluia.}
\gregorioscore{C-friday}

%\newpage

\subsection{Saturday:}
\marginpar{For as many of you as have been baptized
in Christ, have put on Christ, alleluia.}
\gregorioscore{co--omnes_qui_in_christo--solesmes}

\section{Ite Missa Est}

\gregorioscore{ky--ite_ia--solesmes}

\end{document}
