\newHymn

%\HymnTitlesc{Litany of Saint Joseph}
\JustHymnNum
\index{Litany of Saint Joseph|upnums}

\begin{multicols}{2}

\lettrine{L}{ord,} have mercy on us.\\
Christ, have mercy on us.\\
\begin{hangparas}{1em}{1}
\parskip0mm
\raggedright
Lord, have mercy on us.

Christ, hear us.

{\itshape Christ, graciously hear us.}

God the Father of heaven,

{\itshape have mercy on us.}

God the Son, Redeemer of the world,

God the Holy Ghost,

Holy Trinity, one God,

%\makebox[\textwidth]{Holy Mary, \hfill%
%             \begin{rotate}{-90}\textit{Pray for us.}\end{rotate}\quad}
Holy Mary, \textit{pray for us.}

Holy Joseph,

Renowned offspring of David,

Light of Patriarchs,

Spouse of the Mother of God,

Chaste guardian of the Virgin,

Foster father of the Son of God,

Diligent protector of Christ,

\sideResponse{Head of the Holy Family,}{pray for us.}

Joseph most just,

Joseph most chaste,

Joseph most prudent,

Joseph most valiant,

Joseph most obedient,

Joseph most faithful,

Mirror of patience,

Lover of poverty,

Model of workers,

Glory of home life,

Guardian of virgins,

Strength of families,

Solace of the afflicted,

Hope of the sick,

Patron of the dying,

Terror of demons,

Protector of Holy Church,

\end{hangparas}

\end{multicols}

Lamb of God, who takest away the sins of the world,\\
\qquad	\textit{spare us O Lord.}\\
Lamb of God, who takest away the sins of the world,\\
\qquad	\textit{graciously hear us, O Lord.}\\
Lamb of God, who takest away the sins of the world,\\
\qquad	\textit{have mercy on us.}

\bigskip

\begin{hangparas}{1em}{-1}
\parskip0mm
\Vbar He made him the lord of His household.
 
 \Rbar And prince over all His possessions.
 
 \end{hangparas}

{\centering Let us pray.\par}

\lettrine{O}{~ God,} who in Thine ineffable providence didst deign to choose Blessed Joseph to be the spouse of Thy most Holy Mother,
grant, we beseech Thee, that as we venerate him as our protector on earth, 
we may be worthy to have him as our intercessor in heaven,
Thou who livest and reignest forever and ever. 
\Rbar Amen.

%O God, who in Thine ineffable providence didst deign to choose Blessed Joseph to be the spouse of Thy most Holy Mother,
%grant, we beseech Thee, that we may merit to have him as our intercessor in heaven,
%whom on earth we venerate as our protector,
%Thou who livest and reignest forever and ever.  Amen.

%O God, who in Thine ineffable providence didst choose Blessed Joseph to be the spouse of Thy most Holy Mother,
%grant that as we venerate him as our protector on earth, 
%we may be worthy to have him as our intercessor in heaven,
%Thou who livest and reignest forever and ever.  Amen.

%O God, in Thine ineffable providence Thou wast pleased to
%choose Blessed Joseph to be the spouse of Thy most holy Mother;
%grant, we beg Thee, that we may be worthy to have him for our
%intercessor in heaven whom on earth we venerate as our Protector: 
% Who livest and reignest,
%world without end.    

