
\newHymn

\HymnTitlesc{Litany of the Sacred Heart}
%\JustHymnNum

\bigskip

\lettrine{L}{ord,} have mercy on us.\\
Christ, have mercy on us.

\pointorig

\begin{hangparas}{1em}{1}
\parskip0mm

Lord, have mercy on us.

Christ, hear us.

{\itshape Christ, graciously hear us.}

God the Father of heaven,

{\itshape have mercy on us.}

God the Son, Redeemer of the world,

God the Holy Ghost,

Holy Trinity, one God,

 Heart of Jesus, Son of the Eternal 
 Father, 

 Heart of Jesus, formed by the Holy Spirit
 in the womb of the Virgin Mother,

\sideResponse{Heart of Jesus, substantially united to the Word of God,}{have mercy on us.}

Heart of Jesus, of Infinite Majesty,

 Heart of Jesus, Sacred Temple of God, 

 Heart of Jesus, Tabernacle of the Most
 High,

%\sideResponse{Heart of Jesus, House of God and Gate of Heaven,}{have mercy on us.}
Heart of Jesus, House of God and Gate of Heaven,
         
 Heart of Jesus, burning furnace of         
 charity,
          
 Heart of Jesus, abode of justice and        
 love,
             
 Heart of Jesus, full of goodness and
 love,
             
 Heart of Jesus, abyss of all virtues,
 
 Heart of Jesus, most worthy of all         
 praise, 

 Heart of Jesus, king and center of all     
 hearts,

 Heart of Jesus, in whom are all treasures  
 of wisdom and knowledge,

 Heart of Jesus, in whom dwells the         
 fullness of divinity,

 Heart of Jesus, in whom the Father was     
 well pleased,
     
 Heart of Jesus, of whose fullness we have  
 all received,
     
 Heart of Jesus, desire of the everlasting  
 hills,
            
Heart of Jesus, patient and most merciful,    

Heart of Jesus, enriching all who invoke   
 Thee,             

 Heart of Jesus, fountain of life and       
 holiness,
         
 Heart of Jesus, propitiation for our       
 sins, 

 Heart of Jesus, loaded down with           
 opprobrium,

\sideResponse{Heart of Jesus, bruised for our offences,}{have mercy on us.}        


 Heart of Jesus, obedient to death, 

 Heart of Jesus, pierced with a lance,

 Heart of Jesus, source of all
 consolation, 

 Heart of Jesus, our life and              
 resurrection, 

 Heart of Jesus, our peace and our
 reconciliation,

 Heart of Jesus, victim for our sins,

 Heart of Jesus, salvation of those who
 trust in Thee, 

 Heart of Jesus, hope of those who die in
 Thee,

 Heart of Jesus, delight of all the
 Saints,
 
 \end{hangparas}
\filbreak
 
Lamb of God, who takest away the sins of the world,\\
\textit{spare us, O Lord.}\\
Lamb of God, who takest away the sins of the world,\\
\textit{graciously hear us, O Lord.}\\
Lamb of God, who takest away the sins of the world,\\
\textit{have mercy on us.}

\begin{hangparas}{1em}{-1} 
\parskip0mm
\Vbar Jesus, meek and humble of heart.

\Rbar Make our hearts like to Thine.
 \end{hangparas}

{\centering Let us pray.\par}

\lettrine{A}{lmighty} and eternal God, look upon the Heart of Thy most beloved Son and upon the
 praises and satisfaction which He offers Thee in the name of sinners; and to those
 who implore Thy mercy, in Thy great goodness, grant forgiveness in the name of the
 same Jesus Christ, Thy Son, who livest and reignest with Thee forever
 and ever. \Rbar Amen.


