\newHymn

\FirstLine{I bind unto myself today}

\settowidth{\versewidth}{The Three in One, and One in Three}

%\firstlindex{Christ be with me, Christ within me}
\begin{verse}[\versewidth]
\HymnTitleInVerse{St.~Patrick's Breastplate}
\initialV{I}{ bind} unto myself today\\*
The strong Name of the Trinity,\\
By invocation of the same,\\*
The Three in One, and One in Three.

\flagverse{2}I bind this day to me for ever,\\*
By power of faith, Christ's Incarnation;\\
His baptism in Jordan river;\\*
His death on cross for my salvation;\\
His bursting from the spicèd tomb;\\*
His riding up the heavenly way;\\
His coming at the day of doom:\\*
I bind unto myself today.

\flagverse{3}I bind unto myself the power\\*
Of the great love of cherubim;\\
The sweet `Well done' in judgment hour;\\*
The service of the seraphim;\\
Confessors' faith, apostles' word,\\*
The patriarchs' prayers, the prophets' scrolls;\\
All good deeds done unto the Lord,\\*
And purity of virgin souls.

\flagverse{4}I bind unto myself today\\*
The virtues of the starlit heaven\\
The glorious sun's life-giving ray,\\*
The whiteness of the moon at even,\\
The flashing of the lightning free,\\*
The whirling wind's tempestuous shocks,\\
The stable earth, the deep salt sea,\\*
Around the old eternal rocks.

\flagverse{5}I bind unto myself today\\*
The power of God to hold and lead,\\
His eye to watch, His might to stay,\\*
His ear to hearken, to my need;\\
The wisdom of my God to teach,\\*
His hand to guide, His shield to ward;\\
The word of God to give me speech,\\*
His heavenly host to be my guard.

\flagverse{6}Against the demon snares of sin,\\*
The vice that gives temptation force,\\
The natural lusts that war within,\\*
The hostile men that mar my course;\\
Or few or many, far or nigh,\\*
In every place and in all hours,\\
Against their fierce hostility\\*
I bind to me these holy powers.

\flagverse{7}Against all Satan's spells and wiles,\\*
Against false words of heresy,\\
Against the knowledge that defiles,\\*
Against the heart's idolatry,\\
Against the wizard's evil craft,\\*
Against the death wound and the burning,\\
The choking wave, the poisoned shaft,\\*
Protect me, Christ, till Thy returning.


%\end{verse}

\newHymn
%\FirstLine{Christ be with me, Christ within me}
\firstlindex{Christ be with me, Christ within me}
%\vskip-2\baselineskip

%\begin{verse}[\versewidth]
%\flagverse{6}\vin \initialV
\vin \FirstVerse{C}{hrist} be with me, Christ within me,\\*
\vin Christ behind me, Christ before me,\\
\vin Christ beside me, Christ to win me,\\*
\vin Christ to comfort and restore me.

\vin Christ beneath me, Christ above me,\\*
\vin Christ in quiet, Christ in danger,\\
\vin Christ in hearts of all that love me,\\*
\vin Christ in mouth of friend and stranger.
%\end{verse}


%\settowidth{\versewidth}{The Three in One, and One in Three}
%\vskip-2\baselineskip

%\begin{verse}[\versewidth]
\flagverse{9}I bind unto myself today\\*
The strong Name of the Trinity,\\
By invocation of the same,\\*
The Three in One, and One in Three.\\
Of whom all nature hath creation,\\*
Eternal Father, Spirit, Word:\\
Praise to the Lord of my salvation,\\*
Salvation is of Christ the Lord.

\end{verse}

\Hpoet{St.~Patrick}{372--466}
\Htrans{Cecil Frances Alexander}{1818--95}


