\newHymn
\FirstLine{O come, O come Emmanuel}

\begin{verse}[\versewidth]

\FirstVerse{O}{ come,} O come Emmanuel,\\*
And ransom captive Israel,\\*
That mourns in lonely exile here\\*
Until the Son of God appear.
\pointorig

\flagverse{Refrain:}
Rejoice! Rejoice! Emmanuel\\*
Shall come to thee, O Israel.


\flagverse{2} O come, Desire of nations, bind\\*
    All peoples in one heart and mind;\\*
    Bid envy, strife and quarrels cease;\\*
    And fill the world with heaven's peace.
 

\flagverse{3} O come, Thou Day-Spring, come and cheer\\*
Our spirits by Thine advent here;\\*
Disperse the gloomy clouds of night\\*
And death's dark shadows put to flight!

\flagverse{4} O come, Thou Key of David, come,\\*
And open wide our heavenly home;\\*
Make safe the way that leads on high,\\*
And close the path to misery. 

\flagverse{5} O come, Thou Rod of Jesse, free\\*
Thine own from Satan's tyranny;\\*
From depths of hell Thy people save,\\*
And give them victory o'er the grave.

\flagverse{6} O come, O come, Thou Lord of Might,\\*
Who to Thy tribes on Sinai's height\\*
In ancient times didst give the law\\*
In cloud, and majesty, and awe.


\flagverse{7} O come, Thou Wisdom from on high,\\*
    And order all things, far and nigh;\\*
    To us the path of knowledge show,\\*
    And cause us in her ways to go.

%These verses occurred in Henry Sloane Coffin and Ambrose White Vernon, eds., Hymns of the Kingdom of God. Revised (New York:
%The A.S. Barnes Company, 1916), Hymn #37. Verse one was the translation by Rev. John Mason Neale.

%For more information about Henry Sloane Coffin, see Pastor, educator, ecumenist: Henry Sloan Coffin (1877-1954), a
%"Presbyterian Heritage" article by James H. Smylie, June 6/13, 2005, at The Presbyterian Outlook. Coffin's noted work Some
%Christian Convictions: A Practical Restatement in Terms of Present-Day Thinking is reproduced at Project Gutenberg. Links open
%in new windows at exterior sites.


\end{verse}
%\attrib{John Mason Neale, 1818--66\\verses 2 and 7 by others}
\Hpoet{John Mason Neale}{1818--66}
%%\Hpoet{Henry Sloane Coffin}{1877--1954}
\Hnote{verses 2 and 7 by others}
