\newHymn
\JustHymnNum
%\HymnTitleit{Rorate caeli desuper}
\FirstLine{Rorate caeli desuper}
\settowidth{\versewidth}{own dew, ye heavens, from above, and let
 the clouds jump up and down}
\gregorioscore{gabc/rorate.tex}

\Hlnote{Drop down dew, ye heavens, from above,\\
and let the clouds rain
down the Just One.}


\begin{verse}[\versewidth]

\annotinverse{Be not angry, O Lord,\\
and remember no longer our iniquity :\\
behold the city of Thy sanctuary\\ is become a desert, \\
Sion is made a desert.\\
Jerusalem is desolate,\\
the house of our holiness and of Thy glory, where our fathers praised Thee.}

\flagverse{1}Ne irascáris Dómine,\\
ne ultra memíneris iniquitátis:\\
Ecce cívitas Sancti facta est desérta:\\
Sion desérta facta est:\\
Jerúsalem desoláta est:\\
Domus sanctificatiónis tuae et glóriae tuae,\\ ubi laudavérunt te patres nostri.

%\flagverse{Ant}Rorate caeli desuper, et nubes pluant iustum.

\annotinverse{We have sinned,\\ and we are become as one unclean,\\
and we have all fallen as a leaf;\\
and our iniquities, like the wind,\\ have
taken us away \\
Thou hast hid Thy face from us,\\
and hast crushed us by the hand of our iniquity.
}

\flagverse{2}Peccávimus, et facti sumus \\
tamquam immúndus nos,\\
et cecídimus\\
quasi fólium univérsi:\\
et iniquitátes nostrae\\ quasi ventus
abstulérunt nos:\\
abscondísti fáciem tuam a nobis,\\
et allisísti nos in manu iniquitátis nostrae.

%\flagverse{Ant}Rorate caeli desuper, et nubes pluant iustum.

\annotinverse{See, O Lord, the affliction of Thy people,\\
and send Him whom Thou hast promised.\\
Send forth the Lamb, the ruler of the
earth,\\
from the Rock of the desert\\ to the mount of the daughter of
Sion,\\
that He Himself may take off\\ the yoke of our
captivity.}

\flagverse{3}Vide Dómine afflictiónem pópuli tui,\\
et mitte quem missúrus es:\\
emítte Agnum dominatórem terrae,\\
de Petra desérti ad montem
fíliae Sion:\\
ut áuferat ipse jugum captivitátis nostrae.


\annotinverse{Be comforted, be comforted, My people;\\
thy salvation shall speedily
come.\\
Why wilt thou waste away in sadness?\\ why hath sorrow
seized thee?\\
I will save thee; fear not:\\
for I am the Lord thy God,\\ the Holy One of Israel, thy Redeemer.}

\flagverse{4}Consolámini, consolámini,\\ pópule meus:\\
cito véniet salus tua:\\
quare moeróre consúmeris,\\ quia innovávit te dolor?\\
Salvábo te,
noli timére,\\
ego enim sum Dóminus Deus tuus,\\ Sanctus Israel, Redémptor tuus.



%\begin{verse}[\versewidth]

%\flagverse{Ant}Rorate caeli desuper, et nubes pluant iustum.

\end{verse}


