\newHymn
\FirstLine{My song is love unknown}

\begin{verse}[\versewidth]

\FirstVerse{M}{y song} is love unknown,\\
my Savior’s love to me,\\
love to the loveless shown,\\
that they might lovely be.\\
O who am I, that for my sake\\
my Lord should take frail flesh and die?

\flagverse{2}He came from his blest throne,\\
salvation to bestow;\\
but men cared not, and none\\
the longed-for Christ would know.\\
But oh, my Friend, my Friend indeed,\\
who at my need his life did spend!

\flagverse{3}Sometimes they strew his way,\\
and his sweet praises sing;\\
resounding all the day\\
hosannas to their King.\\
Then ``Crucify!'' is all their breath,\\
and for his death they thirst and cry.

\flagverse{4}Why, what hath my Lord done?\\
What makes this rage and spite?\\
He made the lame to run,\\
he gave the blind their sight.\\
Sweet injuries! Yet all his deeds\\
their hatred feeds; they 'gainst him rise.

\flagverse{5}They rise, and needs will have\\
my dear Lord sent away;\\
a murderer they save,\\
the Prince of Life they slay.\\
Yet willing he to suff'ring goes,\\
that he his foes from thence might free.

\flagverse{6}In life, no house, no home\\
my Lord on earth might have;\\
in death, no friendly tomb\\
but what a stranger gave.\\
What may I say? Heav'n was his home,\\
but mine the tomb wherein he lay.

\flagverse{7}Here might I stay and sing,\\
no story so divine;\\
never was love, dear King,\\
never was grief like thine.\\
This is my Friend, in whose sweet praise\\
I all my days could gladly spend.

\end{verse}

\Hpoet{Samuel Crossman}{1623--84}

